---
title: "PCA (cognition) stats"
output: html_notebook
---
# import functions
```{r}
library(lmerTest)
library(emmeans)
library(lme4)
library(tidyverse)
library(broom)
library(ggpubr)
library(ggprism)
library(nplyr)
library(effects)
library(corrplot)
library(ppcor)
library(ordinal)
library(dplyr)
library(MuMIn)
library(modelbased)
library(multcomp)
```
# Load data
```{r}
df_dim <- readRDS("df_dim_28July26.rds")

cols <- c("participant", "gender", "condition", "test_no", "day", "order", "dimension", "channel", "night")
df_dim <- df_dim %>% mutate_at(cols, factor) 
```
## Changes in PCA scores over the week (Fig 5)
#1. lme
```{r}
df_dim <- df_dim %>% 
  group_by(dimension) %>% 
  nest() 

df_dim1 <- pluck(df_dim$data[[1]])
df_dim2 <- pluck(df_dim$data[[2]])
df_dim3 <- pluck(df_dim$data[[3]])
df_dim4 <- pluck(df_dim$data[[4]])

df_dim1 <- df_dim1 %>% 
  mutate(dimvalue_z = scale(dimvalue)) %>% 
  mutate(base_dimvalue_z = scale(base_dimvalue))

df_dim2 <- df_dim2 %>% 
  mutate(dimvalue_z = scale(dimvalue)) %>% 
  mutate(base_dimvalue_z = scale(base_dimvalue))

df_dim3 <- df_dim3 %>% 
  mutate(dimvalue_z = scale(dimvalue)) %>% 
  mutate(base_dimvalue_z = scale(base_dimvalue))

df_dim4 <- df_dim4 %>% 
  mutate(dimvalue_z = scale(dimvalue)) %>% 
  mutate(base_dimvalue_z = scale(base_dimvalue))

fit.dim1<- lmer(dimvalue_z ~ condition:day + day + test_no + order + base_dimvalue_z + (1|participant), data = df_dim1)
stats_dim1 <- anova(fit.dim1)

fit.dim2<- lmer(dimvalue_z ~ condition:day + day + test_no + order + base_dimvalue_z + (1|participant), data = df_dim2)
stats_dim2 <- anova(fit.dim2)

fit.dim3<- lmer(dimvalue_z ~ condition:day + day + test_no + order + base_dimvalue_z + (1|participant), data = df_dim3)
stats_dim3 <- anova(fit.dim3)

fit.dim4<- lmer(dimvalue_z ~ condition:day + day + test_no + order + base_dimvalue_z + (1|participant), data = df_dim4)
stats_dim4 <- anova(fit.dim4)

# estimated means
dim1_esmmeans <- estimate_means(fit.dim1 , by = c("day", "condition"))
dim2_esmmeans <- estimate_means(fit.dim2 , by = c("day", "condition"))
dim3_esmmeans <- estimate_means(fit.dim3 , by = c("day", "condition"))
dim4_esmmeans <- estimate_means(fit.dim4 , by = c("day", "condition"))
```
#2. posthoc
```{r}
# comparing between conditions for each day (in paper)
emm_options(pbkrtest.limit = 9880,
            lmerTest.limit = 9880)


pairs(emmeans(fit.dim1, ~day:condition, by="day", p.adjust = "tukey"))

pairs(emmeans(fit.dim2, ~day:condition, by="day", p.adjust = "tukey"))

pairs(emmeans(fit.dim3, ~day:condition, by="day", p.adjust = "tukey"))

pairs(emmeans(fit.dim4, ~day:condition, by="day", p.adjust = "tukey"))

```
#3b. Plot 
```{r}
plot.dim1 <- ggplot(dim1_esmmeans,  aes(x = day, y = Mean, linetype=condition, shape=condition, group=condition)) + 
  scale_shape_manual(values = c(16,21)) +
  geom_point(position = position_dodge(width=0.2), size=2) +
  geom_line(aes(group=condition), linewidth=0.2) +
  geom_errorbar(aes(x=day, y=Mean, ymin=Mean-SE, ymax=Mean+SE), linetype=1, width=0.4, position = position_dodge(0.2), lwd=0.3) +
  geom_point(aes(shape=condition),fill="white", size=2, position = position_dodge(0.2)) +
  theme_prism(base_size =10, base_fontface="plain", base_line_size=0.2) +
  xlab("Day") + ylab("Z-score") +
  scale_y_continuous(limits = c(-0.65, 0.7), breaks = seq(-0.65, 0.7,0.15), expand = c(0, NA))+
  ggtitle("PC1: effort") +
  theme(legend.position="bottom") +
  scale_x_discrete(labels=c("B", "1", "2", "3", "4", "5", "6")) 
plot.dim1

plot.dim2 <- ggplot(dim2_esmmeans,  aes(x = day, y = Mean, linetype=condition, shape=condition, group=condition)) + 
  scale_shape_manual(values = c(16,21)) +
  geom_point(position = position_dodge(width=0.2), size=2) +
  geom_line(aes(group=condition), linewidth=0.2) +
  geom_errorbar(aes(x=day, y=Mean, ymin=Mean-SE, ymax=Mean+SE), linetype=1, width=0.4, position = position_dodge(0.2), lwd=0.3) +
  geom_point(aes(shape=condition),fill="white", size=2, position = position_dodge(0.2)) +
  theme_prism(base_size =10, base_fontface="plain", base_line_size=0.2) +
  xlab("Day") + ylab("Z-score") +
  scale_y_continuous(limits = c(-0.25, 0.25), breaks = seq(-0.25, 0.25,0.1), expand = c(0, NA))+
  ggtitle("PC2: Response time") +
  theme(legend.position="bottom") +
  scale_x_discrete(labels=c("B", "1", "2", "3", "4", "5", "6")) 
plot.dim2

plot.dim3 <- ggplot(dim3_esmmeans,  aes(x = day, y = Mean, linetype=condition, shape=condition, group=condition)) + 
  scale_shape_manual(values = c(16,21)) +
  geom_point(position = position_dodge(width=0.2), size=2) +
  geom_line(aes(group=condition), linewidth=0.2) +
  geom_errorbar(aes(x=day, y=Mean, ymin=Mean-SE, ymax=Mean+SE), linetype=1, width=0.4, position = position_dodge(0.2), lwd=0.3) +
  geom_point(aes(shape=condition),fill="white", size=2, position = position_dodge(0.2)) +
  theme_prism(base_size =10, base_fontface="plain", base_line_size=0.2) +
  xlab("Day") + ylab("Z-score") +
  scale_y_continuous(limits = c(-0.25, 0.25), breaks = seq(-0.25, 0.25,0.1), expand = c(0, NA))+
  ggtitle("PC3: Response consistency") +
  theme(legend.position="bottom") +
  scale_x_discrete(labels=c("B", "1", "2", "3", "4", "5", "6")) 
plot.dim3

plot.dim4 <- ggplot(dim4_esmmeans,  aes(x = day, y = Mean, linetype=condition, shape=condition, group=condition)) + 
  scale_shape_manual(values = c(16,21)) +
  geom_point(position = position_dodge(width=0.2), size=2) +
  geom_line(aes(group=condition), linewidth=0.2) +
  geom_errorbar(aes(x=day, y=Mean, ymin=Mean-SE, ymax=Mean+SE), linetype=1, width=0.4, position = position_dodge(0.2), lwd=0.3) +
  geom_point(aes(shape=condition),fill="white", size=2, position = position_dodge(0.2)) +
  theme_prism(base_size =10, base_fontface="plain", base_line_size=0.2) +
  xlab("Day") + ylab("Z-score") +
  scale_y_continuous(limits = c(-0.65, 0.7), breaks = seq(-0.65, 0.7,0.15), expand = c(0, NA))+
  ggtitle("PC4: Attentional lapses") +
  theme(legend.position="bottom") +
  scale_x_discrete(labels=c("B", "1", "2", "3", "4", "5", "6")) 
plot.dim4

ggsave("figure/fig5/plot_dim1.svg", plot=plot.dim1, width=4, height=4)
ggsave("figure/fig5/plot_dim2.svg", plot=plot.dim2, width=4, height=4)
ggsave("figure/fig5/plot_dim3.svg", plot=plot.dim3, width=4, height=4)
ggsave("figure/fig5/plot_dim4.svg", plot=plot.dim4, width=4, height=4)

rm(list = ls()[-match(c("df_dim", "df_dim1", "df_dim2", "df_dim3", "df_dim4"), ls())])
```
#3b. Plot with violin and raw points
```{r}
plot_outcome <- function(esmmeans_data, raw_data, title, y_min, y_max, y_break) {
  
   ggplot(esmmeans_data, aes(x = day, y = Mean, group = condition, shape = condition, colour = state)) +
    scale_shape_manual(values = c(16, 21)) +
    geom_violin(data = subset(raw_data, condition == "SE"), aes(x = day, y = dimvalue_z, group = interaction(day, condition)), inherit.aes = FALSE, position = position_nudge(-0.1),width = 0.4,alpha = 0.1,linewidth = 0.1) +
    geom_violin(data = subset(raw_data, condition == "SR"), aes(x = day, y = dimvalue_z, group = interaction(day, condition)), inherit.aes = FALSE, position = position_nudge(0.1),width = 0.4,alpha = 0.1,linewidth = 0.1) +
   geom_point(data = subset(raw_data, condition == "SE"),
               aes(x = day, y = dimvalue_z, group = interaction(day, condition)), shape = 16, inherit.aes = FALSE, position = position_nudge(x = -0.1), alpha = 0.3, size = 0.3, stroke=0.1) +
    geom_point(data = subset(raw_data, condition == "SR"), aes(x = day, y = dimvalue_z, group = interaction(day, condition)), shape = 21, fill = "white", inherit.aes = FALSE, position = position_nudge(x = 0.1), alpha = 0.3, size = 0.3, stroke=0.1) +
       geom_line(data = subset(esmmeans_data, condition == "SE"),
          aes(x = day, y = Mean, group = condition),
          linewidth = 0.2, position = position_nudge(-0.1), colour = "black") +
    geom_line(data = subset(esmmeans_data, condition == "SR"),
          aes(x = day, y = Mean, group = condition),
          linewidth = 0.2, position = position_nudge(0.1), colour = "black") +
     geom_errorbar(data = subset(esmmeans_data, condition == "SE"),
                  aes(x=day, y=Mean, ymin=Mean-SE, ymax=Mean+SE), linetype=1, width=0.3, position = position_nudge(-0.1), lwd=0.3, colour="black") +
    geom_errorbar(data = subset(esmmeans_data, condition == "SR"),
                  aes(x=day, y=Mean, ymin=Mean-SE, ymax=Mean+SE), linetype=1, width=0.3, position = position_nudge(0.1), lwd=0.3, colour="black") +
    geom_point(data = subset(esmmeans_data, condition == "SE"),
               aes(shape = condition),
               position = position_nudge(-0.1),size = 1, stroke =0.3, colour="black") +
    geom_point(data = subset(esmmeans_data, condition == "SR"),
               aes(shape = condition),
               fill = "white", shape =21,
               position = position_nudge(0.1),size = 1, stroke =0.3, colour="black") +
  theme_prism(base_size = 8, base_fontface="plain", base_line_size=0.1) +
    labs(x = "Day", y = "Z-scored") +
    theme(legend.position="none") +
    ggtitle(title) +
    scale_y_continuous(limits = c(y_min, y_max), breaks = seq(y_min, y_max, y_break), expand = c(0, NA)) +
    scale_x_discrete(labels = c("B", "1", "2", "3", "4", "5", "6", "7")) +
    theme_prism(base_size = 9, base_fontface = "plain", base_line_size = 0.2) +
    theme(legend.position="none") 
}

plot_dim1 <- plot_outcome(dim1_esmmeans, df_dim1, "PC 1: effort",-3, 5, 0.5)
plot_dim2 <- plot_outcome(dim2_esmmeans, df_dim2, "PC 2: response time",-3, 5, 0.5)
plot_dim3 <- plot_outcome(dim3_esmmeans, df_dim3, "PC 3: response consistency",-4.5, 4, 0.5)
plot_dim4 <- plot_outcome(dim4_esmmeans, df_dim4, "PC 4: attentional lapses",-4.5, 4, 0.5)

ggsave("figure/fig5/plot_dim1.svg", plot=plot_dim1, width=4, height=4)
ggsave("figure/fig5/plot_dim2.svg", plot=plot_dim2, width=4, height=4)
ggsave("figure/fig5/plot_dim3.svg", plot=plot_dim3, width=4, height=4)
ggsave("figure/fig5/plot_dim4.svg", plot=plot_dim4, width=4, height=4)

rm(list = ls()[-match(c("df_dim", "df_dim1", "df_dim2", "df_dim3", "df_dim4"), ls())])
```

## Baseline: associations with all periodic and aperiodic components (Table S7)
#1. lmes
# Dimension 1
```{r}
df_dim <- unnest(df_dim)

df_baseline <- df_dim %>% 
  filter(dimension=="Dim1") %>% # choose dimension
  filter(day=="2") %>% #baseline
  relocate(channel, .after = 8) 

df_baseline_norm <- df_baseline %>% 
  mutate(across(9:last_col(), scale, .names = "{.col}_z"))

# duration
fit.duration_phasic <- lmer(dimvalue_z ~   test_no  + order + phasic_perc_z + NREM_perc_z + (1|participant), data=df_baseline_norm)
fit.duration_phasic_summary <- as.data.frame(coef(summary(fit.duration_phasic))) 
phasic_coeff <- fit.duration_phasic_summary[7,] 
phasic_confint <- as.data.frame(t(confint(fit.duration_phasic)[9,]))
phasic_coeff <- cbind(phasic_coeff,phasic_confint)

fit.duration_tonic <- lmer(dimvalue_z ~   test_no  + order + tonic_perc_z + NREM_perc_z + (1|participant), data=df_baseline_norm)
fit.duration_tonic_summary <- as.data.frame(coef(summary(fit.duration_tonic))) 
tonic_coeff <- fit.duration_tonic_summary[7,] 
tonic_confint <- as.data.frame(t(confint(fit.duration_tonic)[9,]))
tonic_coeff <- cbind(tonic_coeff,tonic_confint)

#fit.duration_NREM <- lmer(dimvalue_z ~   test_no  + order + NREM_perc_z + (1|participant), data=df_baseline_norm)
#fit.duration_NREM_summary <- as.data.frame(coef(summary(fit.duration_NREM))) 
#NREM_coeff <- fit.duration_NREM_summary[7,] 
#NREM_confint <- as.data.frame(t(confint(fit.duration_NREM)[9,]))
#NREM_coeff <- cbind(NREM_coeff,NREM_confint)

fit.duration_REM <- lmer(dimvalue_z ~   test_no  + order + REM_perc_z + NREM_perc_z + (1|participant), data=df_baseline_norm)
fit.duration_REM_summary <- as.data.frame(coef(summary(fit.duration_REM))) 
REM_coeff <- fit.duration_REM_summary[7,] 
NREM_coeff <- fit.duration_REM_summary[8,] 

REM_confint <- as.data.frame(t(confint(fit.duration_REM)[9,]))
REM_coeff <- cbind(REM_coeff,REM_confint)
NREM_confint <- as.data.frame(t(confint(fit.duration_REM)[10,]))
NREM_coeff <- cbind(NREM_coeff,NREM_confint)

# oscillations ----
#phasic ----
fit.IAPF_phasic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + IAPF_phasic_z + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.IAPF_phasic_summary <- as.data.frame(coef(summary(fit.IAPF_phasic))) 
IAPF_phasic_coeff <- fit.IAPF_phasic_summary[11,]
IAPF_phasic_confint <- as.data.frame(t(confint(fit.IAPF_phasic)[13,]))
IAPF_phasic_coeff <- cbind(IAPF_phasic_coeff,IAPF_phasic_confint)

fit.densityalpha_phasic  <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + densityalpha_phasic_z + NREM_perc_z + swa_NREM_z +  (1|participant), data=df_baseline_norm)
fit.densityalpha_phasic_summary <- as.data.frame(coef(summary(fit.densityalpha_phasic))) 
densityalpha_phasic_coeff <- fit.densityalpha_phasic_summary[11,]
densityalpha_phasic_confint <- as.data.frame(t(confint(fit.densityalpha_phasic)[13,]))
densityalpha_phasic_coeff <- cbind(densityalpha_phasic_coeff,densityalpha_phasic_confint)

fit.snralpha_phasic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + snralpha_phasic_z  + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.snralpha_phasic_summary <- as.data.frame(coef(summary(fit.snralpha_phasic))) 
snralpha_phasic_coeff <- fit.snralpha_phasic_summary[11,]
snralpha_phasic_confint <- as.data.frame(t(confint(fit.snralpha_phasic)[13,]))
snralpha_phasic_coeff <- cbind(snralpha_phasic_coeff,snralpha_phasic_confint)

fit.ITPF_phasic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + ITPF_phasic_z +  NREM_perc_z + swa_NREM_z +(1|participant), data=df_baseline_norm)
fit.ITPF_phasic_summary <- as.data.frame(coef(summary(fit.ITPF_phasic))) 
ITPF_phasic_coeff <- fit.ITPF_phasic_summary[11,]
ITPF_phasic_confint <- as.data.frame(t(confint(fit.ITPF_phasic)[13,]))
ITPF_phasic_coeff <- cbind(ITPF_phasic_coeff,ITPF_phasic_confint)

fit.densitytheta_phasic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + densitytheta_phasic_z + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.densitytheta_phasic_summary <- as.data.frame(coef(summary(fit.densitytheta_phasic))) 
densitytheta_phasic_coeff <- fit.densitytheta_phasic_summary[11,]
densitytheta_phasic_confint <- as.data.frame(t(confint(fit.densitytheta_phasic)[13,]))
densitytheta_phasic_coeff <- cbind(densitytheta_phasic_coeff,densitytheta_phasic_confint)

fit.snrtheta_phasic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + snrtheta_phasic_z + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.snrtheta_phasic_summary <- as.data.frame(coef(summary(fit.snrtheta_phasic))) 
snrtheta_phasic_coeff <- fit.snrtheta_phasic_summary[11,]
snrtheta_phasic_confint <- as.data.frame(t(confint(fit.snrtheta_phasic)[13,]))
snrtheta_phasic_coeff <- cbind(snrtheta_phasic_coeff,snrtheta_phasic_confint)

#tonic ----
fit.IAPF_tonic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + IAPF_tonic_z + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.IAPF_tonic_summary <- as.data.frame(coef(summary(fit.IAPF_tonic))) 
IAPF_tonic_coeff <- fit.IAPF_tonic_summary[11,]
IAPF_tonic_confint <- as.data.frame(t(confint(fit.IAPF_tonic)[13,]))
IAPF_tonic_coeff <- cbind(IAPF_tonic_coeff,IAPF_tonic_confint)

fit.densityalpha_tonic  <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + densityalpha_tonic_z +  NREM_perc_z + swa_NREM_z +(1|participant), data=df_baseline_norm)
fit.densityalpha_tonic_summary <- as.data.frame(coef(summary(fit.densityalpha_tonic))) 
densityalpha_tonic_coeff <- fit.densityalpha_tonic_summary[11,]
densityalpha_tonic_confint <- as.data.frame(t(confint(fit.densityalpha_tonic)[13,]))
densityalpha_tonic_coeff <- cbind(densityalpha_tonic_coeff,densityalpha_tonic_confint)

fit.snralpha_tonic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + snralpha_tonic_z  + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.snralpha_tonic_summary <- as.data.frame(coef(summary(fit.snralpha_tonic))) 
snralpha_tonic_coeff <- fit.snralpha_tonic_summary[11,]
snralpha_tonic_confint <- as.data.frame(t(confint(fit.snralpha_tonic)[13,]))
snralpha_tonic_coeff <- cbind(snralpha_tonic_coeff,snralpha_tonic_confint)

fit.ITPF_tonic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + ITPF_tonic_z +  NREM_perc_z + swa_NREM_z +(1|participant), data=df_baseline_norm)
fit.ITPF_tonic_summary <- as.data.frame(coef(summary(fit.ITPF_tonic))) 
ITPF_tonic_coeff <- fit.ITPF_tonic_summary[11,]
ITPF_tonic_confint <- as.data.frame(t(confint(fit.ITPF_tonic)[13,]))
ITPF_tonic_coeff <- cbind(ITPF_tonic_coeff,ITPF_tonic_confint)

fit.densitytheta_tonic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + densitytheta_tonic_z +  NREM_perc_z + swa_NREM_z +(1|participant), data=df_baseline_norm)
fit.densitytheta_tonic_summary <- as.data.frame(coef(summary(fit.densitytheta_tonic))) 
densitytheta_tonic_coeff <- fit.densitytheta_tonic_summary[11,]
densitytheta_tonic_confint <- as.data.frame(t(confint(fit.densitytheta_tonic)[13,]))
densitytheta_tonic_coeff <- cbind(densitytheta_tonic_coeff,densitytheta_tonic_confint)

fit.snrtheta_tonic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + snrtheta_tonic_z +  NREM_perc_z + swa_NREM_z +(1|participant), data=df_baseline_norm)
fit.snrtheta_tonic_summary <- as.data.frame(coef(summary(fit.snrtheta_tonic))) 
snrtheta_tonic_coeff <- fit.snrtheta_tonic_summary[11,]
snrtheta_tonic_confint <- as.data.frame(t(confint(fit.snrtheta_tonic)[13,]))
snrtheta_tonic_coeff <- cbind(snrtheta_tonic_coeff,snrtheta_tonic_confint)

# aperiodic ----
#phasic
fit.exp30to45_phasic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + exp30to45_phasic_z +  NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.exp30to45_phasic_summary <- as.data.frame(coef(summary(fit.exp30to45_phasic))) 
exp30to45_phasic_coeff <- fit.exp30to45_phasic_summary[11,]
exp30to45_phasic_confint <- as.data.frame(t(confint(fit.exp30to45_phasic)[13,]))
exp30to45_phasic_coeff <- cbind(exp30to45_phasic_coeff,exp30to45_phasic_confint)

# tonic
fit.exp30to45_tonic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + exp30to45_tonic_z + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.exp30to45_tonic_summary <- as.data.frame(coef(summary(fit.exp30to45_tonic))) 
exp30to45_tonic_coeff <- fit.exp30to45_tonic_summary[11,]
exp30to45_tonic_confint <- as.data.frame(t(confint(fit.exp30to45_tonic)[13,]))
exp30to45_tonic_coeff <- cbind(exp30to45_tonic_coeff,exp30to45_tonic_confint)

# Create table for Dim 1 ----
results_dimension <-  rbind(phasic_coeff, tonic_coeff, REM_coeff, NREM_coeff, IAPF_phasic_coeff, IAPF_tonic_coeff, densityalpha_phasic_coeff, densityalpha_tonic_coeff, snralpha_phasic_coeff, snralpha_tonic_coeff, ITPF_phasic_coeff, ITPF_tonic_coeff, densitytheta_phasic_coeff, densitytheta_tonic_coeff,snrtheta_phasic_coeff, snrtheta_tonic_coeff, exp30to45_phasic_coeff,exp30to45_tonic_coeff) 
colnames(results_dimension)[5] <- "pvalue"
colnames(results_dimension)[6] <- "confint_start"
colnames(results_dimension)[7] <- "confint_end"

dimension1 <- results_dimension %>%
  mutate(across(1:7, as.numeric)) %>% 
  mutate(across(where(is.numeric), ~ format(round(.x, 4), nsmall = 4)))

dimension1$confint <- paste(dimension1$confint_start, dimension1$confint_end, sep=",")

dimension1 <- dimension1 %>% 
  rownames_to_column("row_names") 
 dimension1$row_names <- gsub("scale\\(([^)]+)\\)", "\\1",  dimension1$row_names)
 dimension1$dimension <- rep("Dimension 1", 18)
```
# Dimension 2
```{r}
rm(list = ls()[-match(c("df_dim", "df_dim1", "df_dim2", "df_dim3", "df_dim4", "dimension1"), ls())])

df_dim <- unnest(df_dim)

df_baseline_norm <- df_dim %>% 
  filter(dimension=="Dim2") %>% # choose dimension
  filter(day=="2") %>% #baseline
  relocate(channel, .after = 8) %>% 
 mutate(across(9:last_col(), scale, .names = "{.col}_z"))

# duration
fit.duration_phasic <- lmer(dimvalue_z ~   test_no  + order + phasic_perc_z + NREM_perc_z + (1|participant), data=df_baseline_norm)
fit.duration_phasic_summary <- as.data.frame(coef(summary(fit.duration_phasic))) 
phasic_coeff <- fit.duration_phasic_summary[7,] 
phasic_confint <- as.data.frame(t(confint(fit.duration_phasic)[9,]))
phasic_coeff <- cbind(phasic_coeff,phasic_confint)

fit.duration_tonic <- lmer(dimvalue_z ~   test_no  + order + tonic_perc_z + NREM_perc_z + (1|participant), data=df_baseline_norm)
fit.duration_tonic_summary <- as.data.frame(coef(summary(fit.duration_tonic))) 
tonic_coeff <- fit.duration_tonic_summary[7,] 
tonic_confint <- as.data.frame(t(confint(fit.duration_tonic)[9,]))
tonic_coeff <- cbind(tonic_coeff,tonic_confint)

#fit.duration_NREM <- lmer(dimvalue_z ~   test_no  + order + NREM_perc_z + (1|participant), data=df_baseline_norm)
#fit.duration_NREM_summary <- as.data.frame(coef(summary(fit.duration_NREM))) 
#NREM_coeff <- fit.duration_NREM_summary[7,] 
#NREM_confint <- as.data.frame(t(confint(fit.duration_NREM)[9,]))
#NREM_coeff <- cbind(NREM_coeff,NREM_confint)

fit.duration_REM <- lmer(dimvalue_z ~   test_no  + order + REM_perc_z + NREM_perc_z + (1|participant), data=df_baseline_norm)
fit.duration_REM_summary <- as.data.frame(coef(summary(fit.duration_REM))) 
REM_coeff <- fit.duration_REM_summary[7,] 
NREM_coeff <- fit.duration_REM_summary[8,] 

REM_confint <- as.data.frame(t(confint(fit.duration_REM)[9,]))
REM_coeff <- cbind(REM_coeff,REM_confint)
NREM_confint <- as.data.frame(t(confint(fit.duration_REM)[10,]))
NREM_coeff <- cbind(NREM_coeff,NREM_confint)

# oscillations ----
#phasic ----
fit.IAPF_phasic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + IAPF_phasic_z + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.IAPF_phasic_summary <- as.data.frame(coef(summary(fit.IAPF_phasic))) 
IAPF_phasic_coeff <- fit.IAPF_phasic_summary[11,]
IAPF_phasic_confint <- as.data.frame(t(confint(fit.IAPF_phasic)[13,]))
IAPF_phasic_coeff <- cbind(IAPF_phasic_coeff,IAPF_phasic_confint)

fit.densityalpha_phasic  <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + densityalpha_phasic_z + NREM_perc_z + swa_NREM_z +  (1|participant), data=df_baseline_norm)
fit.densityalpha_phasic_summary <- as.data.frame(coef(summary(fit.densityalpha_phasic))) 
densityalpha_phasic_coeff <- fit.densityalpha_phasic_summary[11,]
densityalpha_phasic_confint <- as.data.frame(t(confint(fit.densityalpha_phasic)[13,]))
densityalpha_phasic_coeff <- cbind(densityalpha_phasic_coeff,densityalpha_phasic_confint)

fit.snralpha_phasic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + snralpha_phasic_z  + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.snralpha_phasic_summary <- as.data.frame(coef(summary(fit.snralpha_phasic))) 
snralpha_phasic_coeff <- fit.snralpha_phasic_summary[11,]
snralpha_phasic_confint <- as.data.frame(t(confint(fit.snralpha_phasic)[13,]))
snralpha_phasic_coeff <- cbind(snralpha_phasic_coeff,snralpha_phasic_confint)

fit.ITPF_phasic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + ITPF_phasic_z +  NREM_perc_z + swa_NREM_z +(1|participant), data=df_baseline_norm)
fit.ITPF_phasic_summary <- as.data.frame(coef(summary(fit.ITPF_phasic))) 
ITPF_phasic_coeff <- fit.ITPF_phasic_summary[11,]
ITPF_phasic_confint <- as.data.frame(t(confint(fit.ITPF_phasic)[13,]))
ITPF_phasic_coeff <- cbind(ITPF_phasic_coeff,ITPF_phasic_confint)

fit.densitytheta_phasic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + densitytheta_phasic_z + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.densitytheta_phasic_summary <- as.data.frame(coef(summary(fit.densitytheta_phasic))) 
densitytheta_phasic_coeff <- fit.densitytheta_phasic_summary[11,]
densitytheta_phasic_confint <- as.data.frame(t(confint(fit.densitytheta_phasic)[13,]))
densitytheta_phasic_coeff <- cbind(densitytheta_phasic_coeff,densitytheta_phasic_confint)

fit.snrtheta_phasic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + snrtheta_phasic_z + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.snrtheta_phasic_summary <- as.data.frame(coef(summary(fit.snrtheta_phasic))) 
snrtheta_phasic_coeff <- fit.snrtheta_phasic_summary[11,]
snrtheta_phasic_confint <- as.data.frame(t(confint(fit.snrtheta_phasic)[13,]))
snrtheta_phasic_coeff <- cbind(snrtheta_phasic_coeff,snrtheta_phasic_confint)

#tonic ----
fit.IAPF_tonic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + IAPF_tonic_z + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.IAPF_tonic_summary <- as.data.frame(coef(summary(fit.IAPF_tonic))) 
IAPF_tonic_coeff <- fit.IAPF_tonic_summary[11,]
IAPF_tonic_confint <- as.data.frame(t(confint(fit.IAPF_tonic)[13,]))
IAPF_tonic_coeff <- cbind(IAPF_tonic_coeff,IAPF_tonic_confint)

fit.densityalpha_tonic  <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + densityalpha_tonic_z +  NREM_perc_z + swa_NREM_z +(1|participant), data=df_baseline_norm)
fit.densityalpha_tonic_summary <- as.data.frame(coef(summary(fit.densityalpha_tonic))) 
densityalpha_tonic_coeff <- fit.densityalpha_tonic_summary[11,]
densityalpha_tonic_confint <- as.data.frame(t(confint(fit.densityalpha_tonic)[13,]))
densityalpha_tonic_coeff <- cbind(densityalpha_tonic_coeff,densityalpha_tonic_confint)

fit.snralpha_tonic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + snralpha_tonic_z  + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.snralpha_tonic_summary <- as.data.frame(coef(summary(fit.snralpha_tonic))) 
snralpha_tonic_coeff <- fit.snralpha_tonic_summary[11,]
snralpha_tonic_confint <- as.data.frame(t(confint(fit.snralpha_tonic)[13,]))
snralpha_tonic_coeff <- cbind(snralpha_tonic_coeff,snralpha_tonic_confint)

fit.ITPF_tonic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + ITPF_tonic_z +  NREM_perc_z + swa_NREM_z +(1|participant), data=df_baseline_norm)
fit.ITPF_tonic_summary <- as.data.frame(coef(summary(fit.ITPF_tonic))) 
ITPF_tonic_coeff <- fit.ITPF_tonic_summary[11,]
ITPF_tonic_confint <- as.data.frame(t(confint(fit.ITPF_tonic)[13,]))
ITPF_tonic_coeff <- cbind(ITPF_tonic_coeff,ITPF_tonic_confint)

fit.densitytheta_tonic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + densitytheta_tonic_z +  NREM_perc_z + swa_NREM_z +(1|participant), data=df_baseline_norm)
fit.densitytheta_tonic_summary <- as.data.frame(coef(summary(fit.densitytheta_tonic))) 
densitytheta_tonic_coeff <- fit.densitytheta_tonic_summary[11,]
densitytheta_tonic_confint <- as.data.frame(t(confint(fit.densitytheta_tonic)[13,]))
densitytheta_tonic_coeff <- cbind(densitytheta_tonic_coeff,densitytheta_tonic_confint)

fit.snrtheta_tonic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + snrtheta_tonic_z +  NREM_perc_z + swa_NREM_z +(1|participant), data=df_baseline_norm)
fit.snrtheta_tonic_summary <- as.data.frame(coef(summary(fit.snrtheta_tonic))) 
snrtheta_tonic_coeff <- fit.snrtheta_tonic_summary[11,]
snrtheta_tonic_confint <- as.data.frame(t(confint(fit.snrtheta_tonic)[13,]))
snrtheta_tonic_coeff <- cbind(snrtheta_tonic_coeff,snrtheta_tonic_confint)

# aperiodic ----
#phasic
fit.exp30to45_phasic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + exp30to45_phasic_z +  NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.exp30to45_phasic_summary <- as.data.frame(coef(summary(fit.exp30to45_phasic))) 
exp30to45_phasic_coeff <- fit.exp30to45_phasic_summary[11,]
exp30to45_phasic_confint <- as.data.frame(t(confint(fit.exp30to45_phasic)[13,]))
exp30to45_phasic_coeff <- cbind(exp30to45_phasic_coeff,exp30to45_phasic_confint)

# tonic
fit.exp30to45_tonic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + exp30to45_tonic_z + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.exp30to45_tonic_summary <- as.data.frame(coef(summary(fit.exp30to45_tonic))) 
exp30to45_tonic_coeff <- fit.exp30to45_tonic_summary[11,]
exp30to45_tonic_confint <- as.data.frame(t(confint(fit.exp30to45_tonic)[13,]))
exp30to45_tonic_coeff <- cbind(exp30to45_tonic_coeff,exp30to45_tonic_confint)

# Create table for Dim 2 ----
results_dimension <-  rbind(phasic_coeff, tonic_coeff, REM_coeff, NREM_coeff, IAPF_phasic_coeff, IAPF_tonic_coeff, densityalpha_phasic_coeff, densityalpha_tonic_coeff, snralpha_phasic_coeff, snralpha_tonic_coeff, ITPF_phasic_coeff, ITPF_tonic_coeff, densitytheta_phasic_coeff, densitytheta_tonic_coeff,snrtheta_phasic_coeff, snrtheta_tonic_coeff, exp30to45_phasic_coeff,exp30to45_tonic_coeff) 
colnames(results_dimension)[5] <- "pvalue"
colnames(results_dimension)[6] <- "confint_start"
colnames(results_dimension)[7] <- "confint_end"

dimension2 <- results_dimension %>%
  mutate(across(1:7, as.numeric)) %>% 
  mutate(across(where(is.numeric), ~ format(round(.x, 4), nsmall = 4)))

dimension2$confint <- paste(dimension2$confint_start, dimension2$confint_end, sep=",")

dimension2 <- dimension2 %>% 
  rownames_to_column("row_names") 
 dimension2$row_names <- gsub("scale\\(([^)]+)\\)", "\\1",  dimension2$row_names)
 dimension2$dimension <- rep("Dimension 2", 18)
```
# Dimension 3
```{r}
rm(list = ls()[-match(c("df_dim", "df_dim1", "df_dim2", "df_dim3", "df_dim4", "dimension1", "dimension2"), ls())])

df_dim <- unnest(df_dim)

df_baseline_norm <- df_dim %>% 
  filter(dimension=="Dim3") %>% # choose dimension
  filter(day=="2") %>% #baseline
  relocate(channel, .after = 8) %>% 
 mutate(across(9:last_col(), scale, .names = "{.col}_z"))

# duration
fit.duration_phasic <- lmer(dimvalue_z ~   test_no  + order + phasic_perc_z + NREM_perc_z + (1|participant), data=df_baseline_norm)
fit.duration_phasic_summary <- as.data.frame(coef(summary(fit.duration_phasic))) 
phasic_coeff <- fit.duration_phasic_summary[7,] 
phasic_confint <- as.data.frame(t(confint(fit.duration_phasic)[9,]))
phasic_coeff <- cbind(phasic_coeff,phasic_confint)

fit.duration_tonic <- lmer(dimvalue_z ~   test_no  + order + tonic_perc_z + NREM_perc_z + (1|participant), data=df_baseline_norm)
fit.duration_tonic_summary <- as.data.frame(coef(summary(fit.duration_tonic))) 
tonic_coeff <- fit.duration_tonic_summary[7,] 
tonic_confint <- as.data.frame(t(confint(fit.duration_tonic)[9,]))
tonic_coeff <- cbind(tonic_coeff,tonic_confint)

#fit.duration_NREM <- lmer(dimvalue_z ~   test_no  + order + NREM_perc_z + (1|participant), data=df_baseline_norm)
#fit.duration_NREM_summary <- as.data.frame(coef(summary(fit.duration_NREM))) 
#NREM_coeff <- fit.duration_NREM_summary[7,] 
#NREM_confint <- as.data.frame(t(confint(fit.duration_NREM)[9,]))
#NREM_coeff <- cbind(NREM_coeff,NREM_confint)

fit.duration_REM <- lmer(dimvalue_z ~   test_no  + order + REM_perc_z + NREM_perc_z + (1|participant), data=df_baseline_norm)
fit.duration_REM_summary <- as.data.frame(coef(summary(fit.duration_REM))) 
REM_coeff <- fit.duration_REM_summary[7,] 
NREM_coeff <- fit.duration_REM_summary[8,] 

REM_confint <- as.data.frame(t(confint(fit.duration_REM)[9,]))
REM_coeff <- cbind(REM_coeff,REM_confint)
NREM_confint <- as.data.frame(t(confint(fit.duration_REM)[10,]))
NREM_coeff <- cbind(NREM_coeff,NREM_confint)

# oscillations ----
#phasic ----
fit.IAPF_phasic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + IAPF_phasic_z + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.IAPF_phasic_summary <- as.data.frame(coef(summary(fit.IAPF_phasic))) 
IAPF_phasic_coeff <- fit.IAPF_phasic_summary[11,]
IAPF_phasic_confint <- as.data.frame(t(confint(fit.IAPF_phasic)[13,]))
IAPF_phasic_coeff <- cbind(IAPF_phasic_coeff,IAPF_phasic_confint)

fit.densityalpha_phasic  <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + densityalpha_phasic_z + NREM_perc_z + swa_NREM_z +  (1|participant), data=df_baseline_norm)
fit.densityalpha_phasic_summary <- as.data.frame(coef(summary(fit.densityalpha_phasic))) 
densityalpha_phasic_coeff <- fit.densityalpha_phasic_summary[11,]
densityalpha_phasic_confint <- as.data.frame(t(confint(fit.densityalpha_phasic)[13,]))
densityalpha_phasic_coeff <- cbind(densityalpha_phasic_coeff,densityalpha_phasic_confint)

fit.snralpha_phasic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + snralpha_phasic_z  + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.snralpha_phasic_summary <- as.data.frame(coef(summary(fit.snralpha_phasic))) 
snralpha_phasic_coeff <- fit.snralpha_phasic_summary[11,]
snralpha_phasic_confint <- as.data.frame(t(confint(fit.snralpha_phasic)[13,]))
snralpha_phasic_coeff <- cbind(snralpha_phasic_coeff,snralpha_phasic_confint)

fit.ITPF_phasic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + ITPF_phasic_z +  NREM_perc_z + swa_NREM_z +(1|participant), data=df_baseline_norm)
fit.ITPF_phasic_summary <- as.data.frame(coef(summary(fit.ITPF_phasic))) 
ITPF_phasic_coeff <- fit.ITPF_phasic_summary[11,]
ITPF_phasic_confint <- as.data.frame(t(confint(fit.ITPF_phasic)[13,]))
ITPF_phasic_coeff <- cbind(ITPF_phasic_coeff,ITPF_phasic_confint)

fit.densitytheta_phasic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + densitytheta_phasic_z + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.densitytheta_phasic_summary <- as.data.frame(coef(summary(fit.densitytheta_phasic))) 
densitytheta_phasic_coeff <- fit.densitytheta_phasic_summary[11,]
densitytheta_phasic_confint <- as.data.frame(t(confint(fit.densitytheta_phasic)[13,]))
densitytheta_phasic_coeff <- cbind(densitytheta_phasic_coeff,densitytheta_phasic_confint)

fit.snrtheta_phasic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + snrtheta_phasic_z + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.snrtheta_phasic_summary <- as.data.frame(coef(summary(fit.snrtheta_phasic))) 
snrtheta_phasic_coeff <- fit.snrtheta_phasic_summary[11,]
snrtheta_phasic_confint <- as.data.frame(t(confint(fit.snrtheta_phasic)[13,]))
snrtheta_phasic_coeff <- cbind(snrtheta_phasic_coeff,snrtheta_phasic_confint)

#tonic ----
fit.IAPF_tonic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + IAPF_tonic_z + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.IAPF_tonic_summary <- as.data.frame(coef(summary(fit.IAPF_tonic))) 
IAPF_tonic_coeff <- fit.IAPF_tonic_summary[11,]
IAPF_tonic_confint <- as.data.frame(t(confint(fit.IAPF_tonic)[13,]))
IAPF_tonic_coeff <- cbind(IAPF_tonic_coeff,IAPF_tonic_confint)

fit.densityalpha_tonic  <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + densityalpha_tonic_z +  NREM_perc_z + swa_NREM_z +(1|participant), data=df_baseline_norm)
fit.densityalpha_tonic_summary <- as.data.frame(coef(summary(fit.densityalpha_tonic))) 
densityalpha_tonic_coeff <- fit.densityalpha_tonic_summary[11,]
densityalpha_tonic_confint <- as.data.frame(t(confint(fit.densityalpha_tonic)[13,]))
densityalpha_tonic_coeff <- cbind(densityalpha_tonic_coeff,densityalpha_tonic_confint)

fit.snralpha_tonic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + snralpha_tonic_z  + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.snralpha_tonic_summary <- as.data.frame(coef(summary(fit.snralpha_tonic))) 
snralpha_tonic_coeff <- fit.snralpha_tonic_summary[11,]
snralpha_tonic_confint <- as.data.frame(t(confint(fit.snralpha_tonic)[13,]))
snralpha_tonic_coeff <- cbind(snralpha_tonic_coeff,snralpha_tonic_confint)

fit.ITPF_tonic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + ITPF_tonic_z +  NREM_perc_z + swa_NREM_z +(1|participant), data=df_baseline_norm)
fit.ITPF_tonic_summary <- as.data.frame(coef(summary(fit.ITPF_tonic))) 
ITPF_tonic_coeff <- fit.ITPF_tonic_summary[11,]
ITPF_tonic_confint <- as.data.frame(t(confint(fit.ITPF_tonic)[13,]))
ITPF_tonic_coeff <- cbind(ITPF_tonic_coeff,ITPF_tonic_confint)

fit.densitytheta_tonic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + densitytheta_tonic_z +  NREM_perc_z + swa_NREM_z +(1|participant), data=df_baseline_norm)
fit.densitytheta_tonic_summary <- as.data.frame(coef(summary(fit.densitytheta_tonic))) 
densitytheta_tonic_coeff <- fit.densitytheta_tonic_summary[11,]
densitytheta_tonic_confint <- as.data.frame(t(confint(fit.densitytheta_tonic)[13,]))
densitytheta_tonic_coeff <- cbind(densitytheta_tonic_coeff,densitytheta_tonic_confint)

fit.snrtheta_tonic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + snrtheta_tonic_z +  NREM_perc_z + swa_NREM_z +(1|participant), data=df_baseline_norm)
fit.snrtheta_tonic_summary <- as.data.frame(coef(summary(fit.snrtheta_tonic))) 
snrtheta_tonic_coeff <- fit.snrtheta_tonic_summary[11,]
snrtheta_tonic_confint <- as.data.frame(t(confint(fit.snrtheta_tonic)[13,]))
snrtheta_tonic_coeff <- cbind(snrtheta_tonic_coeff,snrtheta_tonic_confint)

# aperiodic ----
#phasic
fit.exp30to45_phasic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + exp30to45_phasic_z +  NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.exp30to45_phasic_summary <- as.data.frame(coef(summary(fit.exp30to45_phasic))) 
exp30to45_phasic_coeff <- fit.exp30to45_phasic_summary[11,]
exp30to45_phasic_confint <- as.data.frame(t(confint(fit.exp30to45_phasic)[13,]))
exp30to45_phasic_coeff <- cbind(exp30to45_phasic_coeff,exp30to45_phasic_confint)

# tonic
fit.exp30to45_tonic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + exp30to45_tonic_z + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.exp30to45_tonic_summary <- as.data.frame(coef(summary(fit.exp30to45_tonic))) 
exp30to45_tonic_coeff <- fit.exp30to45_tonic_summary[11,]
exp30to45_tonic_confint <- as.data.frame(t(confint(fit.exp30to45_tonic)[13,]))
exp30to45_tonic_coeff <- cbind(exp30to45_tonic_coeff,exp30to45_tonic_confint)

# Create table for Dim 3 ----
results_dimension <-   rbind(phasic_coeff, tonic_coeff, REM_coeff, NREM_coeff, IAPF_phasic_coeff, IAPF_tonic_coeff, densityalpha_phasic_coeff, densityalpha_tonic_coeff, snralpha_phasic_coeff, snralpha_tonic_coeff, ITPF_phasic_coeff, ITPF_tonic_coeff, densitytheta_phasic_coeff, densitytheta_tonic_coeff,snrtheta_phasic_coeff, snrtheta_tonic_coeff, exp30to45_phasic_coeff,exp30to45_tonic_coeff)  
colnames(results_dimension)[5] <- "pvalue"
colnames(results_dimension)[6] <- "confint_start"
colnames(results_dimension)[7] <- "confint_end"

dimension3 <- results_dimension %>%
  mutate(across(1:7, as.numeric)) %>% 
  mutate(across(where(is.numeric), ~ format(round(.x, 4), nsmall = 4)))

dimension3$confint <- paste(dimension3$confint_start, dimension3$confint_end, sep=",")

dimension3 <- dimension3 %>% 
  rownames_to_column("row_names") 
 dimension3$row_names <- gsub("scale\\(([^)]+)\\)", "\\1",  dimension3$row_names)
 dimension3$dimension <- rep("Dimension 3", 18)
```
# Dimension 4
```{r}
rm(list = ls()[-match(c("df_dim", "df_dim1", "df_dim2", "df_dim3", "df_dim4", "dimension1", "dimension2", "dimension3"), ls())])

df_dim <- unnest(df_dim)

df_baseline_norm <- df_dim %>% 
  filter(dimension=="Dim4") %>% # choose dimension
  filter(day=="2") %>% #baseline
  relocate(channel, .after = 8) %>% 
  mutate(across(9:last_col(), scale, .names = "{.col}_z"))

# duration
fit.duration_phasic <- lmer(dimvalue_z ~   test_no  + order + phasic_perc_z + NREM_perc_z + (1|participant), data=df_baseline_norm)
fit.duration_phasic_summary <- as.data.frame(coef(summary(fit.duration_phasic))) 
phasic_coeff <- fit.duration_phasic_summary[7,] 
phasic_confint <- as.data.frame(t(confint(fit.duration_phasic)[9,]))
phasic_coeff <- cbind(phasic_coeff,phasic_confint)

fit.duration_tonic <- lmer(dimvalue_z ~   test_no  + order + tonic_perc_z + NREM_perc_z + (1|participant), data=df_baseline_norm)
fit.duration_tonic_summary <- as.data.frame(coef(summary(fit.duration_tonic))) 
tonic_coeff <- fit.duration_tonic_summary[7,] 
tonic_confint <- as.data.frame(t(confint(fit.duration_tonic)[9,]))
tonic_coeff <- cbind(tonic_coeff,tonic_confint)

#fit.duration_NREM <- lmer(dimvalue_z ~   test_no  + order + NREM_perc_z + (1|participant), data=df_baseline_norm)
#fit.duration_NREM_summary <- as.data.frame(coef(summary(fit.duration_NREM))) 
#NREM_coeff <- fit.duration_NREM_summary[7,] 
#NREM_confint <- as.data.frame(t(confint(fit.duration_NREM)[9,]))
#NREM_coeff <- cbind(NREM_coeff,NREM_confint)

fit.duration_REM <- lmer(dimvalue_z ~   test_no  + order + REM_perc_z + NREM_perc_z + (1|participant), data=df_baseline_norm)
fit.duration_REM_summary <- as.data.frame(coef(summary(fit.duration_REM))) 
REM_coeff <- fit.duration_REM_summary[7,] 
NREM_coeff <- fit.duration_REM_summary[8,] 

REM_confint <- as.data.frame(t(confint(fit.duration_REM)[9,]))
REM_coeff <- cbind(REM_coeff,REM_confint)
NREM_confint <- as.data.frame(t(confint(fit.duration_REM)[10,]))
NREM_coeff <- cbind(NREM_coeff,NREM_confint)

# oscillations ----
#phasic ----
fit.IAPF_phasic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + IAPF_phasic_z + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.IAPF_phasic_summary <- as.data.frame(coef(summary(fit.IAPF_phasic))) 
IAPF_phasic_coeff <- fit.IAPF_phasic_summary[11,]
IAPF_phasic_confint <- as.data.frame(t(confint(fit.IAPF_phasic)[13,]))
IAPF_phasic_coeff <- cbind(IAPF_phasic_coeff,IAPF_phasic_confint)

fit.densityalpha_phasic  <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + densityalpha_phasic_z + NREM_perc_z + swa_NREM_z +  (1|participant), data=df_baseline_norm)
fit.densityalpha_phasic_summary <- as.data.frame(coef(summary(fit.densityalpha_phasic))) 
densityalpha_phasic_coeff <- fit.densityalpha_phasic_summary[11,]
densityalpha_phasic_confint <- as.data.frame(t(confint(fit.densityalpha_phasic)[13,]))
densityalpha_phasic_coeff <- cbind(densityalpha_phasic_coeff,densityalpha_phasic_confint)

fit.snralpha_phasic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + snralpha_phasic_z  + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.snralpha_phasic_summary <- as.data.frame(coef(summary(fit.snralpha_phasic))) 
snralpha_phasic_coeff <- fit.snralpha_phasic_summary[11,]
snralpha_phasic_confint <- as.data.frame(t(confint(fit.snralpha_phasic)[13,]))
snralpha_phasic_coeff <- cbind(snralpha_phasic_coeff,snralpha_phasic_confint)

fit.ITPF_phasic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + ITPF_phasic_z +  NREM_perc_z + swa_NREM_z +(1|participant), data=df_baseline_norm)
fit.ITPF_phasic_summary <- as.data.frame(coef(summary(fit.ITPF_phasic))) 
ITPF_phasic_coeff <- fit.ITPF_phasic_summary[11,]
ITPF_phasic_confint <- as.data.frame(t(confint(fit.ITPF_phasic)[13,]))
ITPF_phasic_coeff <- cbind(ITPF_phasic_coeff,ITPF_phasic_confint)

fit.densitytheta_phasic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + densitytheta_phasic_z + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.densitytheta_phasic_summary <- as.data.frame(coef(summary(fit.densitytheta_phasic))) 
densitytheta_phasic_coeff <- fit.densitytheta_phasic_summary[11,]
densitytheta_phasic_confint <- as.data.frame(t(confint(fit.densitytheta_phasic)[13,]))
densitytheta_phasic_coeff <- cbind(densitytheta_phasic_coeff,densitytheta_phasic_confint)

fit.snrtheta_phasic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + snrtheta_phasic_z + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.snrtheta_phasic_summary <- as.data.frame(coef(summary(fit.snrtheta_phasic))) 
snrtheta_phasic_coeff <- fit.snrtheta_phasic_summary[11,]
snrtheta_phasic_confint <- as.data.frame(t(confint(fit.snrtheta_phasic)[13,]))
snrtheta_phasic_coeff <- cbind(snrtheta_phasic_coeff,snrtheta_phasic_confint)

#tonic ----
fit.IAPF_tonic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + IAPF_tonic_z + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.IAPF_tonic_summary <- as.data.frame(coef(summary(fit.IAPF_tonic))) 
IAPF_tonic_coeff <- fit.IAPF_tonic_summary[11,]
IAPF_tonic_confint <- as.data.frame(t(confint(fit.IAPF_tonic)[13,]))
IAPF_tonic_coeff <- cbind(IAPF_tonic_coeff,IAPF_tonic_confint)

fit.densityalpha_tonic  <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + densityalpha_tonic_z +  NREM_perc_z + swa_NREM_z +(1|participant), data=df_baseline_norm)
fit.densityalpha_tonic_summary <- as.data.frame(coef(summary(fit.densityalpha_tonic))) 
densityalpha_tonic_coeff <- fit.densityalpha_tonic_summary[11,]
densityalpha_tonic_confint <- as.data.frame(t(confint(fit.densityalpha_tonic)[13,]))
densityalpha_tonic_coeff <- cbind(densityalpha_tonic_coeff,densityalpha_tonic_confint)

fit.snralpha_tonic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + snralpha_tonic_z  + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.snralpha_tonic_summary <- as.data.frame(coef(summary(fit.snralpha_tonic))) 
snralpha_tonic_coeff <- fit.snralpha_tonic_summary[11,]
snralpha_tonic_confint <- as.data.frame(t(confint(fit.snralpha_tonic)[13,]))
snralpha_tonic_coeff <- cbind(snralpha_tonic_coeff,snralpha_tonic_confint)

fit.ITPF_tonic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + ITPF_tonic_z +  NREM_perc_z + swa_NREM_z +(1|participant), data=df_baseline_norm)
fit.ITPF_tonic_summary <- as.data.frame(coef(summary(fit.ITPF_tonic))) 
ITPF_tonic_coeff <- fit.ITPF_tonic_summary[11,]
ITPF_tonic_confint <- as.data.frame(t(confint(fit.ITPF_tonic)[13,]))
ITPF_tonic_coeff <- cbind(ITPF_tonic_coeff,ITPF_tonic_confint)

fit.densitytheta_tonic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + densitytheta_tonic_z +  NREM_perc_z + swa_NREM_z +(1|participant), data=df_baseline_norm)
fit.densitytheta_tonic_summary <- as.data.frame(coef(summary(fit.densitytheta_tonic))) 
densitytheta_tonic_coeff <- fit.densitytheta_tonic_summary[11,]
densitytheta_tonic_confint <- as.data.frame(t(confint(fit.densitytheta_tonic)[13,]))
densitytheta_tonic_coeff <- cbind(densitytheta_tonic_coeff,densitytheta_tonic_confint)

fit.snrtheta_tonic <- lmer(dimvalue_z ~   test_no + tst_min_z + order + channel + snrtheta_tonic_z +  NREM_perc_z + swa_NREM_z +(1|participant), data=df_baseline_norm)
fit.snrtheta_tonic_summary <- as.data.frame(coef(summary(fit.snrtheta_tonic))) 
snrtheta_tonic_coeff <- fit.snrtheta_tonic_summary[11,]
snrtheta_tonic_confint <- as.data.frame(t(confint(fit.snrtheta_tonic)[13,]))
snrtheta_tonic_coeff <- cbind(snrtheta_tonic_coeff,snrtheta_tonic_confint)

# aperiodic ----
#phasic
fit.exp30to45_phasic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + exp30to45_phasic_z +  NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.exp30to45_phasic_summary <- as.data.frame(coef(summary(fit.exp30to45_phasic))) 
exp30to45_phasic_coeff <- fit.exp30to45_phasic_summary[11,]
exp30to45_phasic_confint <- as.data.frame(t(confint(fit.exp30to45_phasic)[13,]))
exp30to45_phasic_coeff <- cbind(exp30to45_phasic_coeff,exp30to45_phasic_confint)

# tonic
fit.exp30to45_tonic <- lmer(dimvalue_z ~  test_no + tst_min_z + order + channel + exp30to45_tonic_z + NREM_perc_z + swa_NREM_z + (1|participant), data=df_baseline_norm)
fit.exp30to45_tonic_summary <- as.data.frame(coef(summary(fit.exp30to45_tonic))) 
exp30to45_tonic_coeff <- fit.exp30to45_tonic_summary[11,]
exp30to45_tonic_confint <- as.data.frame(t(confint(fit.exp30to45_tonic)[13,]))
exp30to45_tonic_coeff <- cbind(exp30to45_tonic_coeff,exp30to45_tonic_confint)

# Create table for Dim 4 ----
results_dimension <-   rbind(phasic_coeff, tonic_coeff, REM_coeff, NREM_coeff, IAPF_phasic_coeff, IAPF_tonic_coeff, densityalpha_phasic_coeff, densityalpha_tonic_coeff, snralpha_phasic_coeff, snralpha_tonic_coeff, ITPF_phasic_coeff, ITPF_tonic_coeff, densitytheta_phasic_coeff, densitytheta_tonic_coeff,snrtheta_phasic_coeff, snrtheta_tonic_coeff, exp30to45_phasic_coeff,exp30to45_tonic_coeff) 
colnames(results_dimension)[5] <- "pvalue"
colnames(results_dimension)[6] <- "confint_start"
colnames(results_dimension)[7] <- "confint_end"

dimension4 <- results_dimension %>%
  mutate(across(1:7, as.numeric)) %>% 
  mutate(across(where(is.numeric), ~ format(round(.x, 4), nsmall = 4)))

dimension4$confint <- paste(dimension1$confint_start, dimension1$confint_end, sep=",")

dimension4 <- dimension4 %>% 
  rownames_to_column("row_names") 
 dimension4$row_names <- gsub("scale\\(([^)]+)\\)", "\\1",  dimension4$row_names)
 dimension4$dimension <- rep("Dimension 4", 18)
```
#2. combine all dimension results into one and create table
```{r}
my_order <- c("NREM_perc_z", "REM_perc_z", "phasic_perc_z", "tonic_perc_z", "IAPF_phasic_z", "densityalpha_phasic_z", "snralpha_phasic_z", "ITPF_phasic_z", "densitytheta_phasic_z", "snrtheta_phasic_z", "IAPF_tonic_z", "densityalpha_tonic_z", "snralpha_tonic_z", "ITPF_tonic_z", "densitytheta_tonic_z", "snrtheta_tonic_z", "exp30to45_phasic_z", "exp30to45_tonic_z")

dimension_results_adj <- rbind(dimension1, dimension2, dimension3, dimension4) %>% 
  mutate(adj_pvalue = p.adjust(pvalue, method="fdr"))  %>%
  relocate(adj_pvalue, .after = pvalue)  %>%
  mutate(across(2:9, as.numeric)) %>% 
  mutate(across(2:9, ~ format(round(.x, 4), nsmall = 4)))  %>%
  mutate(row_names = factor(row_names, levels=my_order)) %>% 
  arrange(row_names)
dimension_results_adj$dimension <- as.factor(dimension_results_adj$dimension)

# Generate table 
library(knitr)
library(kableExtra)

dim1_table <- dimension_results_adj %>% 
  filter(dimension == "Dimension 1") %>% 
  dplyr::select(!c(5,8,9,11)) %>% 
  kable("html", digits=4, caption = "Dimension 1 for baseline") %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) 

dim2_table <- dimension_results_adj %>% 
  filter(dimension == "Dimension 2") %>% 
  dplyr::select(!c(5,8,9,11)) %>% 
  kable("html", digits=4, caption = "Dimension 2 for baseline") %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) 

dim3_table <- dimension_results_adj %>% 
  filter(dimension == "Dimension 3") %>% 
  dplyr::select(!c(5,8,9,11)) %>% 
  kable("html", digits=4, caption = "Dimension 3 for baseline") %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) 

dim4_table <- dimension_results_adj %>% 
  filter(dimension == "Dimension 4") %>% 
  dplyr::select(!c(5,8,9,11)) %>% 
  kable("html", digits=4, caption = "Dimension 4 for baseline") %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) 
  
```

## Week: (Fig5)
#Load data
```{r}
# clear global env
rm(list = ls())

df_dim_week <- readRDS("df_dim_week_28July26.rds")

cols <- c("participant", "gender", "condition", "test_no", "day", "order", "dimension", "channel", "night")
df_dim_week <- df_dim_week %>% mutate_at(cols, factor) 
```
#1. lmes
# Dimension 1 
```{r}
df_dim_norm <- df_dim_week %>% filter(dimension=="Dim1") %>%  
  relocate(channel, .after = 8)  %>% 
  dplyr::select(-channel_baseline)
df_dim_norm <- df_dim_norm %>% 
 mutate(across(10:last_col(), scale, .names = "{.col}_z"))

#duration
fit.duration_NREM <- lmer(dimvalue_z ~ NREM_perc_z + NREM_perc_baseline_z + REM_perc_z + REM_perc_baseline_z + base_dimvalue_z + condition:night + night + test_no  + order + (1|participant), data=df_dim_norm)
fit.duration_NREM_summary <- as.data.frame(coef(summary(fit.duration_NREM))) 
NREM_coeff <- fit.duration_NREM_summary[c(2),]  
REM_coeff <- fit.duration_NREM_summary[c(4),] 

fit.duration_phasic <- lmer(dimvalue_z ~ phasic_perc_z + phasic_perc_baseline_z + NREM_perc_z + NREM_perc_baseline_z + base_dimvalue_z + condition:night + night + test_no  + order + (1|participant), data=df_dim_norm)
fit.duration_phasic_summary <- as.data.frame(coef(summary(fit.duration_phasic))) 
phasic_coeff <- fit.duration_phasic_summary[c(2),] 

fit.duration_tonic <- lmer(dimvalue_z ~ tonic_perc_z + tonic_perc_baseline_z +NREM_perc_z + NREM_perc_baseline_z + base_dimvalue_z + condition:night + night+test_no  + order + (1|participant), data=df_dim_norm)
fit.duration_tonic_summary <- as.data.frame(coef(summary(fit.duration_tonic))) 
tonic_coeff <- fit.duration_tonic_summary[c(2),] 

# oscillations
fit.IAPF_phasic <- lmer(dimvalue_z ~ IAPF_phasic_z + IAPF_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.IAPF_phasic_summary <- as.data.frame(coef(summary(fit.IAPF_phasic))) 
IAPF_phasic_coeff <- fit.IAPF_phasic_summary[c(2),]

fit.densityalpha_phasic <- lmer(dimvalue_z ~ densityalpha_phasic_z + densityalpha_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.densityalpha_phasic_summary <- as.data.frame(coef(summary(fit.densityalpha_phasic))) 
densityalpha_phasic_coeff <- fit.densityalpha_phasic_summary[c(2),]

fit.densitytheta_phasic <- lmer(dimvalue_z ~ densitytheta_phasic_z + densitytheta_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.densitytheta_phasic_summary <- as.data.frame(coef(summary(fit.densitytheta_phasic))) 
densitytheta_phasic_coeff <- fit.densitytheta_phasic_summary[c(2),]

fit.snralpha_phasic <- lmer(dimvalue_z ~ snralpha_phasic_z + snralpha_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.snralpha_phasic_summary <- as.data.frame(coef(summary(fit.snralpha_phasic))) 
snralpha_phasic_coeff <- fit.snralpha_phasic_summary[c(2),]

fit.snrtheta_phasic <- lmer(dimvalue_z ~ snrtheta_phasic_z + snrtheta_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.snrtheta_phasic_summary <- as.data.frame(coef(summary(fit.snrtheta_phasic))) 
snrtheta_phasic_coeff <- fit.snrtheta_phasic_summary[c(2),]

fit.IAPF_tonic <- lmer(dimvalue_z ~ IAPF_tonic_z + IAPF_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z +  condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.IAPF_tonic_summary <- as.data.frame(coef(summary(fit.IAPF_tonic))) 
IAPF_tonic_coeff <- fit.IAPF_tonic_summary[c(2),]

fit.densityalpha_tonic <- lmer(dimvalue_z ~ densityalpha_tonic_z + densityalpha_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.densityalpha_tonic_summary <- as.data.frame(coef(summary(fit.densityalpha_tonic))) 
densityalpha_tonic_coeff <- fit.densityalpha_tonic_summary[c(2),]

fit.densitytheta_tonic <- lmer(dimvalue_z ~ densitytheta_tonic_z + densitytheta_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.densitytheta_tonic_summary <- as.data.frame(coef(summary(fit.densitytheta_tonic))) 
densitytheta_tonic_coeff <- fit.densitytheta_tonic_summary[c(2),]
densitytheta_tonic_coeff <- fit.densitytheta_tonic_summary[c(2),]

fit.snralpha_tonic <- lmer(dimvalue_z ~ snralpha_tonic_z + snralpha_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.snralpha_tonic_summary <- as.data.frame(coef(summary(fit.snralpha_tonic))) 
snralpha_tonic_coeff <- fit.snralpha_tonic_summary[c(2),]
snralpha_tonic_coeff <- fit.snralpha_tonic_summary[c(2),]

fit.snrtheta_tonic <- lmer(dimvalue_z ~ snrtheta_tonic_z +-snrtheta_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z +  condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.snrtheta_tonic_summary <- as.data.frame(coef(summary(fit.snrtheta_tonic))) 
snrtheta_tonic_coeff <- fit.snrtheta_tonic_summary[c(2),]

# aperiodic ----
fit.exp30to45_phasic <- lmer(dimvalue_z ~ exp30to45_phasic_z + exp30to45_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.exp30to45_phasic_summary <- as.data.frame(coef(summary(fit.exp30to45_phasic))) 
exp30to45_phasic_coeff <- fit.exp30to45_phasic_summary[c(2),]

fit.exp30to45_tonic <- lmer(dimvalue_z ~ exp30to45_tonic_z + exp30to45_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.exp30to45_tonic_summary <- as.data.frame(coef(summary(fit.exp30to45_tonic))) 
exp30to45_tonic_coeff <- fit.exp30to45_tonic_summary[c(2),]

results_week_dim1 <- rbind(NREM_coeff, REM_coeff, phasic_coeff, tonic_coeff, IAPF_phasic_coeff, IAPF_tonic_coeff, densityalpha_phasic_coeff,  densityalpha_tonic_coeff, snralpha_phasic_coeff, snralpha_tonic_coeff, densitytheta_phasic_coeff, densitytheta_tonic_coeff, exp30to45_phasic_coeff,exp30to45_tonic_coeff) 
colnames(results_week_dim1)[5] <- "pvalue"
results_week_dim1 <- results_week_dim1 %>%
  mutate(across(where(is.numeric), ~ format(round(.x, 4), nsmall = 4)))

results_week_dim1 <- results_week_dim1 %>% 
  rownames_to_column("row_names") #%>% 
results_week_dim1$row_names <- gsub("scale\\(([^)]+)\\)", "\\1",  results_week_dim1$row_names)

results_week_dim1$dimension <- rep("Dim 1", 14)
```
#Dimension 1 - unified model for phasic vs tonic significance
```{r}
rm(list = ls()[-match(c("df_dim_week", "results_week_dim1", "df_dim_norm"), ls())])

# duration ----
fit.duration <- lmer(dimvalue_z ~ NREM_perc_z + NREM_perc_baseline_z + phasic_perc_z + phasic_perc_baseline_z + tonic_perc_z + tonic_perc_baseline_z + base_dimvalue_z + condition:night + night + test_no  + order + (1|participant), data=df_dim_norm)
fit.duration_summary <- as.data.frame(coef(summary(fit.duration))) 
duration_coeff <- fit.duration_summary[c(2,4,6),] 

# Formally test if stages differ from each other
duration_comparison <- glht(fit.duration,
                   linfct = c(
                     "phasic_perc_z - tonic_perc_z = 0",
                     "phasic_perc_z - NREM_perc_z = 0",
                     "tonic_perc_z - NREM_perc_z = 0"
                   ))
s<-summary(duration_comparison,
        test = adjusted("bonferroni"))

 glht_duration <- data.frame(
    estimate   = s$test$coefficients,
    SE         = s$test$sigma,
    z          = s$test$tstat,
    p          = s$test$pvalues)

# oscillations ----
# alpha
fit.IAPF <- lmer(dimvalue_z ~ IAPF_phasic_z + IAPF_phasic_baseline_z + IAPF_tonic_z + IAPF_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.IAPF_summary <- as.data.frame(coef(summary(fit.IAPF))) 
IAPF_coeff <- fit.IAPF_summary[c(2,4),]

fit.densityalpha <- lmer(dimvalue_z ~ densityalpha_phasic_z + densityalpha_phasic_baseline_z + densityalpha_tonic_z + densityalpha_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.densityalpha_summary <- as.data.frame(coef(summary(fit.densityalpha))) 
densityalpha_coeff <- fit.densityalpha_summary[c(2,4),]

fit.snralpha <- lmer(dimvalue_z ~ snralpha_phasic_z + snralpha_phasic_baseline_z + snralpha_tonic_z + snralpha_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.snralpha_summary <- as.data.frame(coef(summary(fit.snralpha))) 
snralpha_coeff <- fit.snralpha_summary[c(2,4),]

#theta 
fit.densitytheta <- lmer(dimvalue_z ~ densitytheta_phasic_z + densitytheta_phasic_baseline_z + densitytheta_tonic_z + densitytheta_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.densitytheta_summary <- as.data.frame(coef(summary(fit.densitytheta))) 
densitytheta_coeff <- fit.densitytheta_summary[c(2,4),]

# aperiodic ----
fit.exp30to45 <- lmer(dimvalue_z ~ exp30to45_phasic_z + exp30to45_phasic_baseline_z + exp30to45_tonic_z + exp30to45_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.exp30to45_summary <- as.data.frame(coef(summary(fit.exp30to45))) 
exp30to45_coeff <- fit.exp30to45_summary[c(2,4),]

# run glht ----
run_glht <- function(model, contrasts) {
   comp <- glht(model, linfct = contrasts)
   s    <- summary(comp)
   
    tab <- data.frame(
    estimate   = s$test$coefficients,
    SE         = s$test$sigma,
    z          = s$test$tstat,
    p          = s$test$pvalues
  )
  
}

# IAPF
glht_IAPF <- run_glht(
  model     = fit.IAPF,
  contrasts = "IAPF_phasic_z - IAPF_tonic_z = 0"
)

# density alpha
glht_densityalpha <- run_glht(
  model     = fit.densityalpha,
  contrasts = "densityalpha_phasic_z - densityalpha_tonic_z = 0"
)

# snr alpha
glht_snralpha <- run_glht(
  model     = fit.snralpha,
  contrasts = "snralpha_phasic_z - snralpha_tonic_z = 0"
)

# density theta
glht_densitytheta <- run_glht(
  model     = fit.densitytheta,
  contrasts = "densitytheta_phasic_z - densitytheta_tonic_z = 0"
)

# exp30-45Hz
glht_exp30to45 <- run_glht(
  model     = fit.exp30to45,
  contrasts = "exp30to45_phasic_z - exp30to45_tonic_z =0"
)

final_glht_dim1 <- rbind(
  glht_duration,
  glht_IAPF,
  glht_densityalpha,
  glht_snralpha,
  glht_densitytheta,
  glht_exp30to45
) %>%  mutate(adj_pvalue = p.adjust(p, method="fdr")) 

```
# Dimension 2
```{r}
rm(list = ls()[-match(c("df_dim_week", "results_week_dim1", "final_glht_dim1"), ls())])

df_dim_norm <- df_dim_week %>% filter(dimension=="Dim2") %>%  
  relocate(channel, .after = 8)  %>% 
  dplyr::select(-channel_baseline)
df_dim_norm <- df_dim_norm %>% 
 mutate(across(10:last_col(), scale, .names = "{.col}_z"))

#duration
fit.duration_NREM <- lmer(dimvalue_z ~ NREM_perc_z + NREM_perc_baseline_z + REM_perc_z + REM_perc_baseline_z + base_dimvalue_z + condition:night + night + test_no  + order + (1|participant), data=df_dim_norm)
fit.duration_NREM_summary <- as.data.frame(coef(summary(fit.duration_NREM))) 
NREM_coeff <- fit.duration_NREM_summary[c(2),]  
REM_coeff <- fit.duration_NREM_summary[c(4),] 

fit.duration_phasic <- lmer(dimvalue_z ~ phasic_perc_z + phasic_perc_baseline_z + NREM_perc_z + NREM_perc_baseline_z + base_dimvalue_z + condition:night + night + test_no  + order + (1|participant), data=df_dim_norm)
fit.duration_phasic_summary <- as.data.frame(coef(summary(fit.duration_phasic))) 
phasic_coeff <- fit.duration_phasic_summary[c(2),] 

fit.duration_tonic <- lmer(dimvalue_z ~ tonic_perc_z + tonic_perc_baseline_z +NREM_perc_z + NREM_perc_baseline_z + base_dimvalue_z + condition:night + night+test_no  + order + (1|participant), data=df_dim_norm)
fit.duration_tonic_summary <- as.data.frame(coef(summary(fit.duration_tonic))) 
tonic_coeff <- fit.duration_tonic_summary[c(2),] 

# oscillations
fit.IAPF_phasic <- lmer(dimvalue_z ~ IAPF_phasic_z + IAPF_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.IAPF_phasic_summary <- as.data.frame(coef(summary(fit.IAPF_phasic))) 
IAPF_phasic_coeff <- fit.IAPF_phasic_summary[c(2),]

fit.densityalpha_phasic <- lmer(dimvalue_z ~ densityalpha_phasic_z + densityalpha_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.densityalpha_phasic_summary <- as.data.frame(coef(summary(fit.densityalpha_phasic))) 
densityalpha_phasic_coeff <- fit.densityalpha_phasic_summary[c(2),]

fit.densitytheta_phasic <- lmer(dimvalue_z ~ densitytheta_phasic_z + densitytheta_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.densitytheta_phasic_summary <- as.data.frame(coef(summary(fit.densitytheta_phasic))) 
densitytheta_phasic_coeff <- fit.densitytheta_phasic_summary[c(2),]

fit.snralpha_phasic <- lmer(dimvalue_z ~ snralpha_phasic_z + snralpha_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.snralpha_phasic_summary <- as.data.frame(coef(summary(fit.snralpha_phasic))) 
snralpha_phasic_coeff <- fit.snralpha_phasic_summary[c(2),]

fit.snrtheta_phasic <- lmer(dimvalue_z ~ snrtheta_phasic_z + snrtheta_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.snrtheta_phasic_summary <- as.data.frame(coef(summary(fit.snrtheta_phasic))) 
snrtheta_phasic_coeff <- fit.snrtheta_phasic_summary[c(2),]

fit.IAPF_tonic <- lmer(dimvalue_z ~ IAPF_tonic_z + IAPF_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z +  condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.IAPF_tonic_summary <- as.data.frame(coef(summary(fit.IAPF_tonic))) 
IAPF_tonic_coeff <- fit.IAPF_tonic_summary[c(2),]

fit.densityalpha_tonic <- lmer(dimvalue_z ~ densityalpha_tonic_z + densityalpha_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.densityalpha_tonic_summary <- as.data.frame(coef(summary(fit.densityalpha_tonic))) 
densityalpha_tonic_coeff <- fit.densityalpha_tonic_summary[c(2),]

fit.densitytheta_tonic <- lmer(dimvalue_z ~ densitytheta_tonic_z + densitytheta_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.densitytheta_tonic_summary <- as.data.frame(coef(summary(fit.densitytheta_tonic))) 
densitytheta_tonic_coeff <- fit.densitytheta_tonic_summary[c(2),]
densitytheta_tonic_coeff <- fit.densitytheta_tonic_summary[c(2),]

fit.snralpha_tonic <- lmer(dimvalue_z ~ snralpha_tonic_z + snralpha_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.snralpha_tonic_summary <- as.data.frame(coef(summary(fit.snralpha_tonic))) 
snralpha_tonic_coeff <- fit.snralpha_tonic_summary[c(2),]
snralpha_tonic_coeff <- fit.snralpha_tonic_summary[c(2),]

fit.snrtheta_tonic <- lmer(dimvalue_z ~ snrtheta_tonic_z +-snrtheta_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z +  condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.snrtheta_tonic_summary <- as.data.frame(coef(summary(fit.snrtheta_tonic))) 
snrtheta_tonic_coeff <- fit.snrtheta_tonic_summary[c(2),]

# aperiodic ----
fit.exp30to45_phasic <- lmer(dimvalue_z ~ exp30to45_phasic_z + exp30to45_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.exp30to45_phasic_summary <- as.data.frame(coef(summary(fit.exp30to45_phasic))) 
exp30to45_phasic_coeff <- fit.exp30to45_phasic_summary[c(2),]

fit.exp30to45_tonic <- lmer(dimvalue_z ~ exp30to45_tonic_z + exp30to45_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.exp30to45_tonic_summary <- as.data.frame(coef(summary(fit.exp30to45_tonic))) 
exp30to45_tonic_coeff <- fit.exp30to45_tonic_summary[c(2),]

results_week_dim2 <- rbind(NREM_coeff, REM_coeff, phasic_coeff, tonic_coeff, IAPF_phasic_coeff, IAPF_tonic_coeff, densityalpha_phasic_coeff,  densityalpha_tonic_coeff, snralpha_phasic_coeff, snralpha_tonic_coeff, densitytheta_phasic_coeff, densitytheta_tonic_coeff, exp30to45_phasic_coeff,exp30to45_tonic_coeff) 
colnames(results_week_dim2)[5] <- "pvalue"
results_week_dim2 <- results_week_dim2 %>%
  mutate(across(where(is.numeric), ~ format(round(.x, 4), nsmall = 4)))

results_week_dim2 <- results_week_dim2 %>% 
  rownames_to_column("row_names") #%>% 
results_week_dim2$row_names <- gsub("scale\\(([^)]+)\\)", "\\1",  results_week_dim2$row_names)

results_week_dim2$dimension <- rep("Dim 2", 14)
```
#2 Dimension 2 - unified model for phasic vs tonic significance
```{r}
rm(list = ls()[-match(c("df_dim_week", "results_week_dim1", "final_glht_dim1", "results_week_dim2", "df_dim_norm"), ls())])

# duration ----
fit.duration <- lmer(dimvalue_z ~ NREM_perc_z + NREM_perc_baseline_z + phasic_perc_z + phasic_perc_baseline_z + tonic_perc_z + tonic_perc_baseline_z + base_dimvalue_z + condition:night + night + test_no  + order + (1|participant), data=df_dim_norm)
fit.duration_summary <- as.data.frame(coef(summary(fit.duration))) 
duration_coeff <- fit.duration_summary[c(2,4,6),] 

# Formally test if stages differ from each other
duration_comparison <- glht(fit.duration,
                   linfct = c(
                     "phasic_perc_z - tonic_perc_z = 0",
                     "phasic_perc_z - NREM_perc_z = 0",
                     "tonic_perc_z - NREM_perc_z = 0"
                   ))
s<-summary(duration_comparison,
        test = adjusted("bonferroni"))

 glht_duration <- data.frame(
    estimate   = s$test$coefficients,
    SE         = s$test$sigma,
    z          = s$test$tstat,
    p          = s$test$pvalues)

# oscillations ----
# alpha
fit.IAPF <- lmer(dimvalue_z ~ IAPF_phasic_z + IAPF_phasic_baseline_z + IAPF_tonic_z + IAPF_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.IAPF_summary <- as.data.frame(coef(summary(fit.IAPF))) 
IAPF_coeff <- fit.IAPF_summary[c(2,4),]

fit.densityalpha <- lmer(dimvalue_z ~ densityalpha_phasic_z + densityalpha_phasic_baseline_z + densityalpha_tonic_z + densityalpha_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.densityalpha_summary <- as.data.frame(coef(summary(fit.densityalpha))) 
densityalpha_coeff <- fit.densityalpha_summary[c(2,4),]

fit.snralpha <- lmer(dimvalue_z ~ snralpha_phasic_z + snralpha_phasic_baseline_z + snralpha_tonic_z + snralpha_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.snralpha_summary <- as.data.frame(coef(summary(fit.snralpha))) 
snralpha_coeff <- fit.snralpha_summary[c(2,4),]

#theta 
fit.densitytheta <- lmer(dimvalue_z ~ densitytheta_phasic_z + densitytheta_phasic_baseline_z + densitytheta_tonic_z + densitytheta_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.densitytheta_summary <- as.data.frame(coef(summary(fit.densitytheta))) 
densitytheta_coeff <- fit.densitytheta_summary[c(2,4),]

# aperiodic ----
fit.exp30to45 <- lmer(dimvalue_z ~ exp30to45_phasic_z + exp30to45_phasic_baseline_z + exp30to45_tonic_z + exp30to45_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.exp30to45_summary <- as.data.frame(coef(summary(fit.exp30to45))) 
exp30to45_coeff <- fit.exp30to45_summary[c(2,4),]


# run glht ----
run_glht <- function(model, contrasts) {
   comp <- glht(model, linfct = contrasts)
   s    <- summary(comp)
   
    tab <- data.frame(
    estimate   = s$test$coefficients,
    SE         = s$test$sigma,
    z          = s$test$tstat,
    p          = s$test$pvalues
  )
  
}

# IAPF
glht_IAPF <- run_glht(
  model     = fit.IAPF,
  contrasts = "IAPF_phasic_z - IAPF_tonic_z = 0"
)

# density alpha
glht_densityalpha <- run_glht(
  model     = fit.densityalpha,
  contrasts = "densityalpha_phasic_z - densityalpha_tonic_z = 0"
)

# snr alpha
glht_snralpha <- run_glht(
  model     = fit.snralpha,
  contrasts = "snralpha_phasic_z - snralpha_tonic_z = 0"
)

# density theta
glht_densitytheta <- run_glht(
  model     = fit.densitytheta,
  contrasts = "densitytheta_phasic_z - densitytheta_tonic_z = 0"
)

# exp30-45Hz
glht_exp30to45 <- run_glht(
  model     = fit.exp30to45,
  contrasts = "exp30to45_phasic_z - exp30to45_tonic_z =0"
)

final_glht_dim2 <- rbind(
  glht_duration,
  glht_IAPF,
  glht_densityalpha,
  glht_snralpha,
  glht_densitytheta,
  glht_exp30to45
)%>%  mutate(adj_pvalue = p.adjust(p, method="fdr")) 

```
# Dimension 3 
```{r}
rm(list = ls()[-match(c("df_dim_week", "results_week_dim1", "final_glht_dim1", "results_week_dim2", "final_glht_dim2"), ls())])

df_dim_norm <- df_dim_week %>% filter(dimension=="Dim3") %>%  
  relocate(channel, .after = 8)  %>% 
  dplyr::select(-channel_baseline)
df_dim_norm <- df_dim_norm %>% 
 mutate(across(10:last_col(), scale, .names = "{.col}_z"))

#duration
fit.duration_NREM <- lmer(dimvalue_z ~ NREM_perc_z + NREM_perc_baseline_z + REM_perc_z + REM_perc_baseline_z + base_dimvalue_z + condition:night + night + test_no  + order + (1|participant), data=df_dim_norm)
fit.duration_NREM_summary <- as.data.frame(coef(summary(fit.duration_NREM))) 
NREM_coeff <- fit.duration_NREM_summary[c(2),]  
REM_coeff <- fit.duration_NREM_summary[c(4),] 

fit.duration_phasic <- lmer(dimvalue_z ~ phasic_perc_z + phasic_perc_baseline_z + NREM_perc_z + NREM_perc_baseline_z + base_dimvalue_z + condition:night + night + test_no  + order + (1|participant), data=df_dim_norm)
fit.duration_phasic_summary <- as.data.frame(coef(summary(fit.duration_phasic))) 
phasic_coeff <- fit.duration_phasic_summary[c(2),] 

fit.duration_tonic <- lmer(dimvalue_z ~ tonic_perc_z + tonic_perc_baseline_z +NREM_perc_z + NREM_perc_baseline_z + base_dimvalue_z + condition:night + night+test_no  + order + (1|participant), data=df_dim_norm)
fit.duration_tonic_summary <- as.data.frame(coef(summary(fit.duration_tonic))) 
tonic_coeff <- fit.duration_tonic_summary[c(2),] 

# oscillations
fit.IAPF_phasic <- lmer(dimvalue_z ~ IAPF_phasic_z + IAPF_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.IAPF_phasic_summary <- as.data.frame(coef(summary(fit.IAPF_phasic))) 
IAPF_phasic_coeff <- fit.IAPF_phasic_summary[c(2),]

fit.densityalpha_phasic <- lmer(dimvalue_z ~ densityalpha_phasic_z + densityalpha_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.densityalpha_phasic_summary <- as.data.frame(coef(summary(fit.densityalpha_phasic))) 
densityalpha_phasic_coeff <- fit.densityalpha_phasic_summary[c(2),]

fit.densitytheta_phasic <- lmer(dimvalue_z ~ densitytheta_phasic_z + densitytheta_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.densitytheta_phasic_summary <- as.data.frame(coef(summary(fit.densitytheta_phasic))) 
densitytheta_phasic_coeff <- fit.densitytheta_phasic_summary[c(2),]

fit.snralpha_phasic <- lmer(dimvalue_z ~ snralpha_phasic_z + snralpha_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.snralpha_phasic_summary <- as.data.frame(coef(summary(fit.snralpha_phasic))) 
snralpha_phasic_coeff <- fit.snralpha_phasic_summary[c(2),]

fit.snrtheta_phasic <- lmer(dimvalue_z ~ snrtheta_phasic_z + snrtheta_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.snrtheta_phasic_summary <- as.data.frame(coef(summary(fit.snrtheta_phasic))) 
snrtheta_phasic_coeff <- fit.snrtheta_phasic_summary[c(2),]

fit.IAPF_tonic <- lmer(dimvalue_z ~ IAPF_tonic_z + IAPF_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z +  condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.IAPF_tonic_summary <- as.data.frame(coef(summary(fit.IAPF_tonic))) 
IAPF_tonic_coeff <- fit.IAPF_tonic_summary[c(2),]

fit.densityalpha_tonic <- lmer(dimvalue_z ~ densityalpha_tonic_z + densityalpha_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.densityalpha_tonic_summary <- as.data.frame(coef(summary(fit.densityalpha_tonic))) 
densityalpha_tonic_coeff <- fit.densityalpha_tonic_summary[c(2),]

fit.densitytheta_tonic <- lmer(dimvalue_z ~ densitytheta_tonic_z + densitytheta_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.densitytheta_tonic_summary <- as.data.frame(coef(summary(fit.densitytheta_tonic))) 
densitytheta_tonic_coeff <- fit.densitytheta_tonic_summary[c(2),]
densitytheta_tonic_coeff <- fit.densitytheta_tonic_summary[c(2),]

fit.snralpha_tonic <- lmer(dimvalue_z ~ snralpha_tonic_z + snralpha_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.snralpha_tonic_summary <- as.data.frame(coef(summary(fit.snralpha_tonic))) 
snralpha_tonic_coeff <- fit.snralpha_tonic_summary[c(2),]
snralpha_tonic_coeff <- fit.snralpha_tonic_summary[c(2),]

fit.snrtheta_tonic <- lmer(dimvalue_z ~ snrtheta_tonic_z +-snrtheta_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z +  condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.snrtheta_tonic_summary <- as.data.frame(coef(summary(fit.snrtheta_tonic))) 
snrtheta_tonic_coeff <- fit.snrtheta_tonic_summary[c(2),]

# aperiodic ----
fit.exp30to45_phasic <- lmer(dimvalue_z ~ exp30to45_phasic_z + exp30to45_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.exp30to45_phasic_summary <- as.data.frame(coef(summary(fit.exp30to45_phasic))) 
exp30to45_phasic_coeff <- fit.exp30to45_phasic_summary[c(2),]

fit.exp30to45_tonic <- lmer(dimvalue_z ~ exp30to45_tonic_z + exp30to45_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.exp30to45_tonic_summary <- as.data.frame(coef(summary(fit.exp30to45_tonic))) 
exp30to45_tonic_coeff <- fit.exp30to45_tonic_summary[c(2),]

results_week_dim3 <- rbind(NREM_coeff, REM_coeff, phasic_coeff, tonic_coeff, IAPF_phasic_coeff, IAPF_tonic_coeff, densityalpha_phasic_coeff,  densityalpha_tonic_coeff, snralpha_phasic_coeff, snralpha_tonic_coeff, densitytheta_phasic_coeff, densitytheta_tonic_coeff, exp30to45_phasic_coeff,exp30to45_tonic_coeff) 
colnames(results_week_dim3)[5] <- "pvalue"
results_week_dim3 <- results_week_dim3 %>%
  mutate(across(where(is.numeric), ~ format(round(.x, 4), nsmall = 4)))

results_week_dim3 <- results_week_dim3 %>% 
  rownames_to_column("row_names") #%>% 
results_week_dim3$row_names <- gsub("scale\\(([^)]+)\\)", "\\1",  results_week_dim3$row_names)

results_week_dim3$dimension <- rep("Dim 3", 14)
```
# Dimension 3 - unified model for phasic vs tonic significance
```{r}
rm(list = ls()[-match(c("df_dim_week", "results_week_dim1", "results_week_dim2", "results_week_dim3", "final_glht_dim1", "final_glht_dim2", "df_dim_norm"), ls())])

# duration ----
fit.duration <- lmer(dimvalue_z ~ NREM_perc_z + NREM_perc_baseline_z + phasic_perc_z + phasic_perc_baseline_z + tonic_perc_z + tonic_perc_baseline_z + base_dimvalue_z + condition:night + night + test_no  + order + (1|participant), data=df_dim_norm)
fit.duration_summary <- as.data.frame(coef(summary(fit.duration))) 
duration_coeff <- fit.duration_summary[c(2,4,6),] 

# Formally test if stages differ from each other
duration_comparison <- glht(fit.duration,
                   linfct = c(
                     "phasic_perc_z - tonic_perc_z = 0",
                     "phasic_perc_z - NREM_perc_z = 0",
                     "tonic_perc_z - NREM_perc_z = 0"
                   ))
s<-summary(duration_comparison,
        test = adjusted("bonferroni"))

 glht_duration <- data.frame(
    estimate   = s$test$coefficients,
    SE         = s$test$sigma,
    z          = s$test$tstat,
    p          = s$test$pvalues)

# oscillations ----
# alpha
fit.IAPF <- lmer(dimvalue_z ~ IAPF_phasic_z + IAPF_phasic_baseline_z + IAPF_tonic_z + IAPF_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.IAPF_summary <- as.data.frame(coef(summary(fit.IAPF))) 
IAPF_coeff <- fit.IAPF_summary[c(2,4),]

fit.densityalpha <- lmer(dimvalue_z ~ densityalpha_phasic_z + densityalpha_phasic_baseline_z + densityalpha_tonic_z + densityalpha_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.densityalpha_summary <- as.data.frame(coef(summary(fit.densityalpha))) 
densityalpha_coeff <- fit.densityalpha_summary[c(2,4),]

fit.snralpha <- lmer(dimvalue_z ~ snralpha_phasic_z + snralpha_phasic_baseline_z + snralpha_tonic_z + snralpha_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.snralpha_summary <- as.data.frame(coef(summary(fit.snralpha))) 
snralpha_coeff <- fit.snralpha_summary[c(2,4),]

#theta 
fit.densitytheta <- lmer(dimvalue_z ~ densitytheta_phasic_z + densitytheta_phasic_baseline_z + densitytheta_tonic_z + densitytheta_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.densitytheta_summary <- as.data.frame(coef(summary(fit.densitytheta))) 
densitytheta_coeff <- fit.densitytheta_summary[c(2,4),]

# aperiodic ----
fit.exp30to45 <- lmer(dimvalue_z ~ exp30to45_phasic_z + exp30to45_phasic_baseline_z + exp30to45_tonic_z + exp30to45_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.exp30to45_summary <- as.data.frame(coef(summary(fit.exp30to45))) 
exp30to45_coeff <- fit.exp30to45_summary[c(2,4),]


# run glht ----
run_glht <- function(model, contrasts) {
   comp <- glht(model, linfct = contrasts)
   s    <- summary(comp)
   
    tab <- data.frame(
    estimate   = s$test$coefficients,
    SE         = s$test$sigma,
    z          = s$test$tstat,
    p          = s$test$pvalues
  )
  
}

# IAPF
glht_IAPF <- run_glht(
  model     = fit.IAPF,
  contrasts = "IAPF_phasic_z - IAPF_tonic_z = 0"
)

# density alpha
glht_densityalpha <- run_glht(
  model     = fit.densityalpha,
  contrasts = "densityalpha_phasic_z - densityalpha_tonic_z = 0"
)

# snr alpha
glht_snralpha <- run_glht(
  model     = fit.snralpha,
  contrasts = "snralpha_phasic_z - snralpha_tonic_z = 0"
)

# density theta
glht_densitytheta <- run_glht(
  model     = fit.densitytheta,
  contrasts = "densitytheta_phasic_z - densitytheta_tonic_z = 0"
)

# exp30-45Hz
glht_exp30to45 <- run_glht(
  model     = fit.exp30to45,
  contrasts = "exp30to45_phasic_z - exp30to45_tonic_z =0"
)

final_glht_dim3 <- rbind(
  glht_duration,
  glht_IAPF,
  glht_densityalpha,
  glht_snralpha,
  glht_densitytheta,
  glht_exp30to45
)%>%  mutate(adj_pvalue = p.adjust(p, method="fdr")) 

```
# Dimension 4
```{r}
rm(list = ls()[-match(c("df_dim_week", "results_week_dim1", "results_week_dim2", "results_week_dim3", "final_glht_dim1", "final_glht_dim2", "final_glht_dim3"), ls())])

df_dim_norm <- df_dim_week %>% filter(dimension=="Dim4") %>% #change dim1-4 with each round 
  relocate(channel, .after = 8)  %>% 
  dplyr::select(-channel_baseline)
df_dim_norm <- df_dim_norm %>% 
mutate(across(10:last_col(), scale, .names = "{.col}_z"))

#duration
fit.duration_NREM <- lmer(dimvalue_z ~ NREM_perc_z + NREM_perc_baseline_z + REM_perc_z + REM_perc_baseline_z + base_dimvalue_z + condition:night + night + test_no  + order + (1|participant), data=df_dim_norm)
fit.duration_NREM_summary <- as.data.frame(coef(summary(fit.duration_NREM))) 
NREM_coeff <- fit.duration_NREM_summary[c(2),]  
REM_coeff <- fit.duration_NREM_summary[c(4),] 

fit.duration_phasic <- lmer(dimvalue_z ~ phasic_perc_z + phasic_perc_baseline_z + NREM_perc_z + NREM_perc_baseline_z + base_dimvalue_z + condition:night + night + test_no  + order + (1|participant), data=df_dim_norm)
fit.duration_phasic_summary <- as.data.frame(coef(summary(fit.duration_phasic))) 
phasic_coeff <- fit.duration_phasic_summary[c(2),] 

fit.duration_tonic <- lmer(dimvalue_z ~ tonic_perc_z + tonic_perc_baseline_z +NREM_perc_z + NREM_perc_baseline_z + base_dimvalue_z + condition:night + night+test_no  + order + (1|participant), data=df_dim_norm)
fit.duration_tonic_summary <- as.data.frame(coef(summary(fit.duration_tonic))) 
tonic_coeff <- fit.duration_tonic_summary[c(2),] 

# oscillations
fit.IAPF_phasic <- lmer(dimvalue_z ~ IAPF_phasic_z + IAPF_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.IAPF_phasic_summary <- as.data.frame(coef(summary(fit.IAPF_phasic))) 
IAPF_phasic_coeff <- fit.IAPF_phasic_summary[c(2),]

fit.densityalpha_phasic <- lmer(dimvalue_z ~ densityalpha_phasic_z + densityalpha_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.densityalpha_phasic_summary <- as.data.frame(coef(summary(fit.densityalpha_phasic))) 
densityalpha_phasic_coeff <- fit.densityalpha_phasic_summary[c(2),]

fit.densitytheta_phasic <- lmer(dimvalue_z ~ densitytheta_phasic_z + densitytheta_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.densitytheta_phasic_summary <- as.data.frame(coef(summary(fit.densitytheta_phasic))) 
densitytheta_phasic_coeff <- fit.densitytheta_phasic_summary[c(2),]

fit.snralpha_phasic <- lmer(dimvalue_z ~ snralpha_phasic_z + snralpha_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.snralpha_phasic_summary <- as.data.frame(coef(summary(fit.snralpha_phasic))) 
snralpha_phasic_coeff <- fit.snralpha_phasic_summary[c(2),]

fit.snrtheta_phasic <- lmer(dimvalue_z ~ snrtheta_phasic_z + snrtheta_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.snrtheta_phasic_summary <- as.data.frame(coef(summary(fit.snrtheta_phasic))) 
snrtheta_phasic_coeff <- fit.snrtheta_phasic_summary[c(2),]

fit.IAPF_tonic <- lmer(dimvalue_z ~ IAPF_tonic_z + IAPF_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z +  condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.IAPF_tonic_summary <- as.data.frame(coef(summary(fit.IAPF_tonic))) 
IAPF_tonic_coeff <- fit.IAPF_tonic_summary[c(2),]

fit.densityalpha_tonic <- lmer(dimvalue_z ~ densityalpha_tonic_z + densityalpha_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.densityalpha_tonic_summary <- as.data.frame(coef(summary(fit.densityalpha_tonic))) 
densityalpha_tonic_coeff <- fit.densityalpha_tonic_summary[c(2),]

fit.densitytheta_tonic <- lmer(dimvalue_z ~ densitytheta_tonic_z + densitytheta_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.densitytheta_tonic_summary <- as.data.frame(coef(summary(fit.densitytheta_tonic))) 
densitytheta_tonic_coeff <- fit.densitytheta_tonic_summary[c(2),]
densitytheta_tonic_coeff <- fit.densitytheta_tonic_summary[c(2),]

fit.snralpha_tonic <- lmer(dimvalue_z ~ snralpha_tonic_z + snralpha_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.snralpha_tonic_summary <- as.data.frame(coef(summary(fit.snralpha_tonic))) 
snralpha_tonic_coeff <- fit.snralpha_tonic_summary[c(2),]
snralpha_tonic_coeff <- fit.snralpha_tonic_summary[c(2),]

fit.snrtheta_tonic <- lmer(dimvalue_z ~ snrtheta_tonic_z +-snrtheta_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z +  condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.snrtheta_tonic_summary <- as.data.frame(coef(summary(fit.snrtheta_tonic))) 
snrtheta_tonic_coeff <- fit.snrtheta_tonic_summary[c(2),]

# aperiodic ----
fit.exp30to45_phasic <- lmer(dimvalue_z ~ exp30to45_phasic_z + exp30to45_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.exp30to45_phasic_summary <- as.data.frame(coef(summary(fit.exp30to45_phasic))) 
exp30to45_phasic_coeff <- fit.exp30to45_phasic_summary[c(2),]

fit.exp30to45_tonic <- lmer(dimvalue_z ~ exp30to45_tonic_z + exp30to45_tonic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
fit.exp30to45_tonic_summary <- as.data.frame(coef(summary(fit.exp30to45_tonic))) 
exp30to45_tonic_coeff <- fit.exp30to45_tonic_summary[c(2),]

results_week_dim4 <- rbind(NREM_coeff, REM_coeff, phasic_coeff, tonic_coeff, IAPF_phasic_coeff, IAPF_tonic_coeff, densityalpha_phasic_coeff,  densityalpha_tonic_coeff, snralpha_phasic_coeff, snralpha_tonic_coeff, densitytheta_phasic_coeff, densitytheta_tonic_coeff, exp30to45_phasic_coeff,exp30to45_tonic_coeff) 
colnames(results_week_dim4)[5] <- "pvalue"
results_week_dim4 <- results_week_dim4 %>%
  mutate(across(where(is.numeric), ~ format(round(.x, 4), nsmall = 4)))

results_week_dim4 <- results_week_dim4 %>% 
  rownames_to_column("row_names") #%>% 
results_week_dim4$row_names <- gsub("scale\\(([^)]+)\\)", "\\1",  results_week_dim4$row_names)

results_week_dim4$dimension <- rep("Dim 4", 14)

```
# Dimension 4 - unified model for phasic vs tonic significance
```{r}
rm(list = ls()[-match(c("df_dim_week", "results_week_dim1", "results_week_dim2","results_week_dim3", "results_week_dim4", "final_glht_dim1", "final_glht_dim2", "final_glht_dim3", "df_dim_norm"), ls())])

# duration ----
fit.duration <- lmer(dimvalue_z ~ NREM_perc_z + NREM_perc_baseline_z + phasic_perc_z + phasic_perc_baseline_z + tonic_perc_z + tonic_perc_baseline_z + base_dimvalue_z + condition:night + night + test_no  + order + (1|participant), data=df_dim_norm)
fit.duration_summary <- as.data.frame(coef(summary(fit.duration))) 
duration_coeff <- fit.duration_summary[c(2,4,6),] 

# Formally test if stages differ from each other
duration_comparison <- glht(fit.duration,
                   linfct = c(
                     "phasic_perc_z - tonic_perc_z = 0",
                     "phasic_perc_z - NREM_perc_z = 0",
                     "tonic_perc_z - NREM_perc_z = 0"
                   ))
s<-summary(duration_comparison,
        test = adjusted("bonferroni"))

 glht_duration <- data.frame(
    estimate   = s$test$coefficients,
    SE         = s$test$sigma,
    z          = s$test$tstat,
    p          = s$test$pvalues)

# oscillations ----
# alpha
fit.IAPF <- lmer(dimvalue_z ~ IAPF_phasic_z + IAPF_phasic_baseline_z + IAPF_tonic_z + IAPF_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.IAPF_summary <- as.data.frame(coef(summary(fit.IAPF))) 
IAPF_coeff <- fit.IAPF_summary[c(2,4),]

fit.densityalpha <- lmer(dimvalue_z ~ densityalpha_phasic_z + densityalpha_phasic_baseline_z + densityalpha_tonic_z + densityalpha_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.densityalpha_summary <- as.data.frame(coef(summary(fit.densityalpha))) 
densityalpha_coeff <- fit.densityalpha_summary[c(2,4),]

fit.snralpha <- lmer(dimvalue_z ~ snralpha_phasic_z + snralpha_phasic_baseline_z + snralpha_tonic_z + snralpha_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.snralpha_summary <- as.data.frame(coef(summary(fit.snralpha))) 
snralpha_coeff <- fit.snralpha_summary[c(2,4),]

#theta 
fit.densitytheta <- lmer(dimvalue_z ~ densitytheta_phasic_z + densitytheta_phasic_baseline_z + densitytheta_tonic_z + densitytheta_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.densitytheta_summary <- as.data.frame(coef(summary(fit.densitytheta))) 
densitytheta_coeff <- fit.densitytheta_summary[c(2,4),]

# aperiodic ----
fit.exp30to45 <- lmer(dimvalue_z ~ exp30to45_phasic_z + exp30to45_phasic_baseline_z + exp30to45_tonic_z + exp30to45_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
fit.exp30to45_summary <- as.data.frame(coef(summary(fit.exp30to45))) 
exp30to45_coeff <- fit.exp30to45_summary[c(2,4),]


# run glht ----
run_glht <- function(model, contrasts) {
   comp <- glht(model, linfct = contrasts)
   s    <- summary(comp)
   
    tab <- data.frame(
    estimate   = s$test$coefficients,
    SE         = s$test$sigma,
    z          = s$test$tstat,
    p          = s$test$pvalues
  )
  
}

# IAPF
glht_IAPF <- run_glht(
  model     = fit.IAPF,
  contrasts = "IAPF_phasic_z - IAPF_tonic_z = 0"
)

# density alpha
glht_densityalpha <- run_glht(
  model     = fit.densityalpha,
  contrasts = "densityalpha_phasic_z - densityalpha_tonic_z = 0"
)

# snr alpha
glht_snralpha <- run_glht(
  model     = fit.snralpha,
  contrasts = "snralpha_phasic_z - snralpha_tonic_z = 0"
)

# density theta
glht_densitytheta <- run_glht(
  model     = fit.densitytheta,
  contrasts = "densitytheta_phasic_z - densitytheta_tonic_z = 0"
)

# exp30-45Hz
glht_exp30to45 <- run_glht(
  model     = fit.exp30to45,
  contrasts = "exp30to45_phasic_z - exp30to45_tonic_z =0"
)

final_glht_dim4 <- rbind(
  glht_duration,
  glht_IAPF,
  glht_densityalpha,
  glht_snralpha,
  glht_densitytheta,
  glht_exp30to45
)%>%  mutate(adj_pvalue = p.adjust(p, method="fdr"))


```
#3. Plot
```{r}
# Plot masked results 
results_week_dim_masked <- rbind(results_week_dim1, results_week_dim2,results_week_dim3,results_week_dim4) %>%
  mutate(adj_pvalue = p.adjust(pvalue, method="fdr"))  %>%
    mutate(Estimate = ifelse(abs(adj_pvalue) < 0.05, Estimate, NaN)) 

results_week_dim_masked$sig <- ifelse(
  results_week_dim_masked$adj_pvalue < 0.001, "***", 
  ifelse(results_week_dim_masked$adj_pvalue < 0.01, "**",
    ifelse(results_week_dim_masked$adj_pvalue < 0.05, "*", NA)))

my_order <- c( "NREM_perc_z", "REM_perc_z", "phasic_perc_z","tonic_perc_z", "IAPF_phasic_z","IAPF_tonic_z", "densityalpha_phasic_z", "densityalpha_tonic_z", "snralpha_phasic_z","snralpha_tonic_z", "densitytheta_phasic_z", "densitytheta_tonic_z",   "exp30to45_phasic_z","exp30to45_tonic_z")

results_week_dim_masked <- results_week_dim_masked %>% 
  mutate(row_names = factor(row_names, levels=my_order)) %>% 
  arrange(row_names) 
results_week_dim_masked <- results_week_dim_masked %>% 
   mutate(dimension = fct_relevel(dimension, 
           "Dimension 1", "Dimension 2", "Dimension 3", "Dimension 4"))

results_week_dim_masked <- results_week_dim_masked %>%  mutate(across(2:6, as.numeric)) %>% add_column(y = 0) 

PCA_weekcorrelation <- ggplot(results_week_dim_masked, aes(x = row_names, y= y, fill = Estimate)) +
  geom_tile(colour="black") +
 scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0) +
    facet_wrap(~dimension, nrow=4) +
 # coord_fixed() +
 # geom_text(aes(label= paste(round(Estimate, 2), sig, sep ="\n")), size=3) + # for unmasked results
  geom_text(data = subset(results_week_dim_masked, !is.na(Estimate) & !is.na(sig)),
            aes(label= paste(round(Estimate, 2), sig, sep ="\n")), size=3) +
  theme_prism(base_size = 9, base_fontface="plain", base_line_size=0.2) +
   scale_x_discrete(labels=c('NREM\npercentage','REM\npercentage','phasic\npercentage','tonic\npercentage','phasic\nalpha\npeak\nfrequency','tonic\nalpha\npeak\nfrequency', 'phasic\nalpha\ndensity', 'tonic\nalpha\ndensity', 'phasic\nalpha\namplitude','tonic\nalpha\namplitude', 'phasic\ntheta\ndensity', 'tonic\ntheta\ndensity',  'phasic\nslope\n30-45Hz','tonic\nslope\n30-45Hz')) +
  theme(axis.title.x=element_blank()) 
PCA_weekcorrelation
#ggsave("figure/fig5/PCA_corr.svg", plot=PCA_weekcorrelation, width=11, height=4)

# glht results , fdr corrected
glht_combined <- rbind(final_glht_dim1, final_glht_dim2, final_glht_dim3, final_glht_dim4) %>% 
  mutate(adj_pvalue = p.adjust(p, method = "fdr"))

n_dim1 <- nrow(final_glht_dim1)
n_dim2 <- nrow(final_glht_dim2)
n_dim3 <- nrow(final_glht_dim3)
n_dim4 <- nrow(final_glht_dim4)

# Create kable
glht_combined %>%
  kable(format  = "html", 
        digits  = 4, 
        caption = "Phasic vs Tonic Coefficient Comparison — PCA") %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  pack_rows("Dimension 1", 1, n_dim1) %>%
  pack_rows("Dimension 2", n_dim1 + 1, n_dim1 + n_dim2) %>%
  pack_rows("Dimension 3", n_dim1 + n_dim2 + 1, n_dim1 + n_dim2 + n_dim3) %>%
  pack_rows("Dimension 4", n_dim1 + n_dim2 + n_dim3 + 1, n_dim1 + n_dim2 + n_dim3 + n_dim4)

```
#Investigate strongest correlation in each Dimension
# Dim 1
```{r}
rm(list = setdiff(ls(), "df_dim_week"))

df_dim_norm <- df_dim_week %>% filter(dimension=="Dim1") %>%  
  relocate(channel, .after = 8)  %>% 
  dplyr::select(-channel_baseline)
df_dim_norm <- df_dim_norm %>% 
 mutate(across(10:last_col(), scale, .names = "{.col}_z"))

library(effects) # plot partial regression
library(performance) # calc marginal(fixed-effects var) and conditional (fixed + random variance) R2
# Calculate Cohen D = estimate for fixed effect / (sqrt of sum of variances of random effects)

#Dim1 ----
df_dim <- df_dim_norm %>% filter(dimension=="Dim1") 

fit.exp30to45_dim1 <- lmer(dimvalue_z ~ exp30to45_tonic_z + exp30to45_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim)
effects.fitexp30to45_dim1 <- effect("exp30to45_tonic_z", fit.exp30to45_dim1, partial.residuals=T)
r.squaredGLMM(fit.exp30to45_dim1)

fit.densitytheta_phasic <- lmer(dimvalue_z ~ densitytheta_phasic_z + densitytheta_phasic_baseline_z + base_dimvalue_z + NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z  + channel + order + (1|participant), data=df_dim_norm)
effects.fitthetadensity_dim1 <- effect("densitytheta_phasic_z", fit.densitytheta_phasic, partial.residuals=T)
r.squaredGLMM(fit.densitytheta_phasic)

# plot ----
# tonics slope
ordinary_residuals <- residuals(fit.exp30to45_dim1)
coeff_of_interest <- as.numeric(fixef(fit.exp30to45_dim1)["exp30to45_tonic_z"])
predictor_values <- as.numeric(model.frame(fit.exp30to45_dim1)$exp30to45_tonic_z)
partial_residuals_calculated <- ordinary_residuals + coeff_of_interest * predictor_values
df_points_for_plot <- data.frame(
    x_variable = predictor_values,
    y_partial_residual = partial_residuals_calculated)
df_line <- as.data.frame(effects.fitexp30to45_dim1)

palette_cols <- c("#FF7a11", "#FF9038", "#FFa65F",
                  "#FFbc87", "#FFa65F", "#FF9038")
df_points_for_plot$rand_col <- sample(
  palette_cols,
  nrow(df_points_for_plot),
  replace = TRUE
)

plot_tonicslope <- ggplot(data = df_points_for_plot, aes(x = x_variable, y = y_partial_residual)) +
     # Add partial residual points
     geom_point(aes(color = rand_col), size = 0.5 * 2, shape=1, stroke=0.35) +
     scale_color_identity() +
     # Add the fitted line
     geom_line(data = df_line, aes(x = exp30to45_tonic_z, y = fit),
               color = "black", linewidth = 1) +
     # Add confidence interval ribbon
     geom_ribbon(data = df_line,
                 aes(x = exp30to45_tonic_z, y=fit, ymin = lower, ymax = upper),
                 fill = "grey", alpha = 0.3) + # No 'y_partial_residual' should be here or implied
     labs(
        x = expression("Tonic spectral slope 30-45 Hz\n(z-score)"),
         y = expression("Effort (z-score)"),
         title = ""
     ) +
    scale_x_continuous(limits = c(-6, 3), breaks = seq(-6, 3, 1), expand = c(0, NA)) +
    scale_y_continuous(limits = c(-4, 4), breaks = seq(-4, 4, 1), expand = c(0, NA)) +
    theme_prism(base_size = 10, base_fontface="plain", base_line_size=0.2) +
    theme(legend.position = "none")
plot_tonicslope
ggsave("figure/fig5/dim1_tonicslope_corr.svg", plot=plot_tonicslope, width=4, height=4)

# phasic theta density
ordinary_residuals <- residuals(fit.densitytheta_phasic)
coeff_of_interest <- as.numeric(fixef(fit.densitytheta_phasic)["densitytheta_phasic_z"])
predictor_values <- as.numeric(model.frame(fit.densitytheta_phasic)$densitytheta_phasic_z)
partial_residuals_calculated <- ordinary_residuals + coeff_of_interest * predictor_values
df_points_for_plot <- data.frame(
    x_variable = predictor_values,
    y_partial_residual = partial_residuals_calculated)
df_line <- as.data.frame(effects.fitthetadensity_dim1)

palette_cols <- c("#0072B2", "#008bd9","#01a4ff","#29b2ff","#50c0ff","#8bd5ff")
df_points_for_plot$rand_col <- sample(
  palette_cols,
  nrow(df_points_for_plot),
  replace = TRUE
)

plot_densitytheta <- ggplot(data = df_points_for_plot, aes(x = x_variable, y = y_partial_residual)) +
     # Add partial residual points
     geom_point(aes(color = rand_col), size = 0.5 * 2, shape=1, stroke=0.35) +
     scale_color_identity() +
     # Add the fitted line
     geom_line(data = df_line, aes(x = densitytheta_phasic_z, y = fit),
               color = "black", linewidth = 1) +
     # Add confidence interval ribbon
     geom_ribbon(data = df_line,
                 aes(x = densitytheta_phasic_z, y=fit, ymin = lower, ymax = upper),
                 fill = "grey", alpha = 0.3) + # No 'y_partial_residual' should be here or implied
     labs(
        x = expression("Phasic theta density\n(z-score)"),
         y = expression("Effort (z-score)"),
         title = ""
     ) +
    scale_x_continuous(limits = c(-3, 4), breaks = seq(-3, 4, 1), expand = c(0, NA)) +
    scale_y_continuous(limits = c(-4, 4), breaks = seq(-4, 4, 1), expand = c(0, NA)) +
    theme_prism(base_size = 10, base_fontface="plain", base_line_size=0.2) +
    theme(legend.position = "none")
plot_densitytheta
ggsave("figure/fig5/dim1_phasicthetaden_corr.svg", plot=plot_densitytheta, width=4, height=4)
```
# Dim 2
```{r}
#Dim2 ----
rm(list = setdiff(ls(), "df_dim_week"))

df_dim_norm <- df_dim_week %>% filter(dimension=="Dim2") %>%  
  relocate(channel, .after = 8)  %>% 
  dplyr::select(-channel_baseline)
df_dim_norm <- df_dim_norm %>% 
 mutate(across(10:last_col(), scale, .names = "{.col}_z"))

fit.duration_dim2 <- lmer(dimvalue_z ~ NREM_perc_z + NREM_perc_baseline_z + phasic_perc_z + phasic_perc_baseline_z + base_dimvalue_z + condition:night + night + test_no  + order + (1|participant), data=df_dim_norm)
effects.fit.duration_dim2  <- effect("phasic_perc_z", fit.duration_dim2 , partial.residuals=T)
r.squaredGLMM(fit.duration_dim2 )

fit.densitytheta_dim2 <- lmer(dimvalue_z ~ densitytheta_phasic_z + densitytheta_phasic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
effects.fitdensitytheta_dim2 <- effect("densitytheta_phasic_z", fit.densitytheta_dim2, partial.residuals=T)
r.squaredGLMM(fit.densitytheta_dim2)

# Plot ----
# phasic perc
ordinary_residuals <- residuals(fit.duration_dim2)
coeff_of_interest <- as.numeric(fixef(fit.duration_dim2)["phasic_perc_z"])
predictor_values <- as.numeric(model.frame(fit.duration_dim2)$phasic_perc_z)
partial_residuals_calculated <- ordinary_residuals + coeff_of_interest * predictor_values
df_points_for_plot <- data.frame(
    x_variable = predictor_values,
    y_partial_residual = partial_residuals_calculated)
df_line <- as.data.frame(effects.fit.duration_dim2)

palette_cols <- c("#0072B2", "#008bd9","#01a4ff","#29b2ff","#50c0ff","#8bd5ff")
df_points_for_plot$rand_col <- sample(
  palette_cols,
  nrow(df_points_for_plot),
  replace = TRUE
)

plot_corr_1 <- ggplot(data = df_points_for_plot, aes(x = x_variable, y = y_partial_residual)) +
     # Add partial residual points
     geom_point(aes(color = rand_col), size = 0.5 * 2, shape=1, stroke=0.35) +
     scale_color_identity() +
     # Add the fitted line
     geom_line(data = df_line, aes(x = phasic_perc_z, y = fit),
               color = "black", linewidth = 1) +
     # Add confidence interval ribbon
     geom_ribbon(data = df_line,
                 aes(x = phasic_perc_z, y=fit, ymin = lower, ymax = upper),
                 fill = "grey", alpha = 0.3) + # No 'y_partial_residual' should be here or implied
     labs(
        x = expression("Phasic percentage (z-score)"),
         y = expression("Response time (z-score)"),
         title = ""
     ) +
    scale_x_continuous(limits = c(-2, 4), breaks = seq(-2, 4, 1), expand = c(0, NA)) +
    scale_y_continuous(limits = c(-4, 4), breaks = seq(-4, 4, 1), expand = c(0, NA)) +
    theme_prism(base_size = 10, base_fontface="plain", base_line_size=0.2) +
    theme(legend.position = "none")
plot_corr_1

# phasic theta density 
ordinary_residuals <- residuals(fit.densitytheta_dim2)
coeff_of_interest <- as.numeric(fixef(fit.densitytheta_dim2)["densitytheta_phasic_z"])
predictor_values <- as.numeric(model.frame(fit.densitytheta_dim2)$densitytheta_phasic_z)
partial_residuals_calculated <- ordinary_residuals + coeff_of_interest * predictor_values
df_points_for_plot <- data.frame(
    x_variable = predictor_values,
    y_partial_residual = partial_residuals_calculated)
df_line <- as.data.frame(effects.fitdensitytheta_dim2)

df_points_for_plot$rand_col <- sample(
  palette_cols,
  nrow(df_points_for_plot),
  replace = TRUE
)
plot_corr_2 <- ggplot(data = df_points_for_plot, aes(x = x_variable, y = y_partial_residual)) +
     # Add partial residual points
     geom_point(aes(color = rand_col), size = 0.5 * 2, shape=1, stroke=0.35) +
     scale_color_identity() +
     # Add the fitted line
     geom_line(data = df_line, aes(x = densitytheta_phasic_z, y = fit),
               color = "black", linewidth = 1) +
     # Add confidence interval ribbon
     geom_ribbon(data = df_line,
                 aes(x = densitytheta_phasic_z, y=fit, ymin = lower, ymax = upper),
                 fill = "grey", alpha = 0.3) + # No 'y_partial_residual' should be here or implied
     labs(
        x = expression("Phasic theta density (z-score)"),
         y = expression("Response time (z-score)"),
         title = ""
     ) +
    scale_x_continuous(limits = c(-3, 5), breaks = seq(-3, 5, 1), expand = c(0, NA)) +
    scale_y_continuous(limits = c(-4, 4), breaks = seq(-4, 4, 1), expand = c(0, NA)) +
    theme_prism(base_size = 10, base_fontface="plain", base_line_size=0.2) +
    theme(legend.position = "none")
plot_corr_2

#ggsave("figure/fig5/dim2_phasicperc_corr.svg", plot=plot_corr_1, width=4, height=4)
#ggsave("figure/fig5/dim2_phasicthetadensity_corr.svg", plot=plot_corr_2, width=4, height=4)
```
# Dim 3
```{r}
rm(list = setdiff(ls(), "df_dim_week"))

df_dim_norm <- df_dim_week %>% filter(dimension=="Dim3") %>%  
  relocate(channel, .after = 8)  %>% 
  dplyr::select(-channel_baseline)
df_dim_norm <- df_dim_norm %>% 
 mutate(across(10:last_col(), scale, .names = "{.col}_z"))

fit.snralpha_dim3 <- lmer(dimvalue_z ~ snralpha_tonic_z + snralpha_tonic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
effects.fitsnralpha_dim3 <- effect("snralpha_tonic_z", fit.snralpha_dim3, partial.residuals=T)
r.squaredGLMM(fit.snralpha_dim3)

# Plot ----
# alpha snr
ordinary_residuals <- residuals(fit.snralpha_dim3)
coeff_of_interest <- as.numeric(fixef(fit.snralpha_dim3)["snralpha_tonic_z"])
predictor_values <- as.numeric(model.frame(fit.snralpha_dim3)$snralpha_tonic_z)
partial_residuals_calculated <- ordinary_residuals + coeff_of_interest * predictor_values
df_points_for_plot <- data.frame(
    x_variable = predictor_values,
    y_partial_residual = partial_residuals_calculated)
df_line <- as.data.frame(effects.fitsnralpha_dim3)

palette_cols <- c("#FF7a11", "#FF9038", "#FFa65F",
                  "#FFbc87", "#FFa65F", "#FF9038")
df_points_for_plot$rand_col <- sample(
  palette_cols,
  nrow(df_points_for_plot),
  replace = TRUE
)

plot_corr <- ggplot(data = df_points_for_plot, aes(x = x_variable, y = y_partial_residual)) +
     # Add partial residual points
     geom_point(aes(color = rand_col), size = 0.5 * 2, shape=1, stroke=0.35) +
     scale_color_identity() +
     # Add the fitted line
     geom_line(data = df_line, aes(x = snralpha_tonic_z, y = fit),
               color = "black", linewidth = 1) +
     # Add confidence interval ribbon
     geom_ribbon(data = df_line,
                 aes(x = snralpha_tonic_z, y=fit, ymin = lower, ymax = upper),
                 fill = "grey", alpha = 0.3) + # No 'y_partial_residual' should be here or implied
     labs(
        x = expression("Tonic alpha amplitude (z-score)"),
         y = expression("Response consistency (z-score)"),
         title = ""
     ) +
    scale_x_continuous(limits = c(-2, 5), breaks = seq(-2, 5, 1), expand = c(0, NA)) +
    scale_y_continuous(limits = c(-4, 4), breaks = seq(-4, 4, 1), expand = c(0, NA)) +
    theme_prism(base_size = 10, base_fontface="plain", base_line_size=0.2) +
    theme(legend.position = "none")
plot_corr
#ggsave("figure/fig5/dim3_tonicsnrapha_corr.svg", plot=plot_corr, width=4, height=4)
```
# Dim 4
```{r}
rm(list = setdiff(ls(), "df_dim_week"))

df_dim_norm <- df_dim_week %>% filter(dimension=="Dim4") %>%  
  relocate(channel, .after = 8)  %>% 
  dplyr::select(-channel_baseline)
df_dim_norm <- df_dim_norm %>% 
 mutate(across(10:last_col(), scale, .names = "{.col}_z"))

fit.exp30to45_dim4 <- lmer(dimvalue_z ~ exp30to45_phasic_z + exp30to45_phasic_baseline_z +  base_dimvalue_z +  NREM_perc_z + swa_NREM_z + NREM_perc_baseline_z + swa_NREM_baseline_z + condition:night + night + test_no + tst_min_z + channel + order + (1|participant), data=df_dim_norm)
effects.fitexp30to45_dim4 <- effect("exp30to45_phasic_z", fit.exp30to45_dim4, partial.residuals=T) 
r.squaredGLMM(fit.exp30to45_dim4)

# plot ----
# phasic slope
ordinary_residuals <- residuals(fit.exp30to45_dim4)
coeff_of_interest <- as.numeric(fixef(fit.exp30to45_dim4)["exp30to45_phasic_z"])
predictor_values <- as.numeric(model.frame(fit.exp30to45_dim4)$exp30to45_phasic_z)
partial_residuals_calculated <- ordinary_residuals + coeff_of_interest * predictor_values
df_points_for_plot <- data.frame(
    x_variable = predictor_values,
    y_partial_residual = partial_residuals_calculated)
df_line <- as.data.frame(effects.fitexp30to45_dim4)

palette_cols <- c("#0072B2", "#008bd9","#01a4ff","#29b2ff","#50c0ff","#8bd5ff")
df_points_for_plot$rand_col <- sample(
  palette_cols,
  nrow(df_points_for_plot),
  replace = TRUE
)

plot_corr <- ggplot(data = df_points_for_plot, aes(x = x_variable, y = y_partial_residual)) +
     # Add partial residual points
     geom_point(aes(color = rand_col), size = 0.5 * 2, shape=1, stroke=0.35) +
     scale_color_identity() +
     # Add the fitted line
     geom_line(data = df_line, aes(x = exp30to45_phasic_z, y = fit),
               color = "black", linewidth = 1) +
     # Add confidence interval ribbon
     geom_ribbon(data = df_line,
                 aes(x = exp30to45_phasic_z, y=fit, ymin = lower, ymax = upper),
                 fill = "grey", alpha = 0.3) + # No 'y_partial_residual' should be here or implied
     labs(
        x = expression("Phasic spectral slope (30-45 Hz) (z-score)"),
         y = expression("Attentional lapse (z-score)"),
         title = ""
     ) +
    scale_x_continuous(limits = c(-4, 3), breaks = seq(-4, 3, 1), expand = c(0, NA)) +
    scale_y_continuous(limits = c(-4, 4), breaks = seq(-4, 4, 1), expand = c(0, NA)) +
    theme_prism(base_size = 10, base_fontface="plain", base_line_size=0.2) +
    theme(legend.position = "none")
plot_corr
#ggsave("figure/fig5/dim4_phasicslope_corr.svg", plot=plot_corr, width=4, height=4)
```
