---
title: "overnight modulation"
output: html_notebook
---

#Import functions
```{r}
library(lmerTest)
library(emmeans)
library(lme4)
library(tidyverse)
library(broom)
library(ggpubr)
library(ggprism)
library(nplyr)
library(effects)
library(corrplot)
library(ppcor)
library(ordinal)
library(dplyr)
library(MuMIn)
library(modelbased)
```

## BASELINE FIRST LAST (FIG S10)
# 1. Load dataset
```{r}
df <- readRDS("overnightslopechanges_1_06AUg26.rds")

cols <- c("participant", "condition", "night", "order", "channel")
df <- df  %>% mutate_at(cols, factor)
factor(df$night, order=TRUE,
       levels= c("1", "2", "3", "4", "5", "6", "7", "8", "9"))
```
#2. lmes
# significance based on "time" from anova results
```{r}
df_baseline <- df %>% filter(night=="1") %>% 
  dplyr::select(c(1:6,23:54)) #exp130cycnremfirst:offset3045cycnremlast

df_baseline <- df_baseline %>%  pivot_longer(
  cols = c(7:38), #all variables values
    names_to = c(".value", "time"),
    names_pattern = "(.+)_(first|last)"
)

cols <- c("participant", "condition", "night", "order", "channel", "time")
df_baseline <- df_baseline  %>% mutate_at(cols, factor)

fit.baseline_NREM30to45 <- lmer(exponent_30_45_cyc_nrem
 ~ time + channel + order + tst + (1|participant), data=df_baseline)
anova.fitbaseline_NREM30to45 <- anova(fit.baseline_NREM30to45)

fit.baseline_phasic30to45 <- lmer(exponent_30_45_cyc_phasic
 ~ time + channel + order + tst + (1|participant), data=df_baseline)
anova.fitbaseline_phasic30to45 <- anova(fit.baseline_phasic30to45)

fit.baseline_tonic30to45 <- lmer(exponent_30_45_cyc_tonic
 ~ time + channel + order + tst + (1|participant), data=df_baseline)
anova.fitbaseline_tonic30to45 <- anova(fit.baseline_tonic30to45)

# estimated means
baseline_NREM30to45_esmmeans <- estimate_means(fit.baseline_NREM30to45 , by = c("time"))
baseline_phasic30to45_esmmeans <- estimate_means(fit.baseline_phasic30to45 , by = c("time"))
baseline_tonic30to45_esmmeans <- estimate_means(fit.baseline_tonic30to45 , by = c("time"))
```
#3. Plot
```{r}
library(gghalves)
df_baseline_average <- df_baseline %>% ungroup() %>% 
  dplyr::select(!c(2:6)) %>% 
  group_by(participant, time) %>% 
  dplyr::summarise(across(everything(), mean, na.rm=TRUE))

# NREM
plot_baseline_NREM30to45 <- ggplot(df_baseline_average, aes(x = time, y = exponent_30_45_cyc_nrem, fill = time)) +
  # Left half violin for first
  geom_half_violin(data = subset(df_baseline_average, time == "first"),side = "l",  # <-- flip to left
 alpha = 0.8, trim = FALSE, position = position_nudge(x = -0.1)) +
# Right half violin for last
  geom_half_violin(data = subset(df_baseline_average, time == "last"),side = "r", alpha = 0.8, trim = FALSE, position = position_nudge(x = 0.1)) +
# join same participants with line across state
   geom_line(aes(group = participant), colour = "black", linewidth = 0.3, alpha = 0.2, position = position_jitter(width = 0.05, seed = 123)) +
  geom_point(aes(shape = time, colour=time), size=1, position = position_jitter(width = 0.05, seed = 123)) +
 scale_fill_manual(values = c("first" = "#009E73B2", "last" = "#40E36BB2")) + 
  scale_colour_manual(values = c("first" = "#009E73B2", "last" = "#40E36BB2")) + 
  scale_shape_manual(values = c(21,21)) +
  scale_y_continuous(limits = c(-6, -1.5), breaks = seq(-6,-1.5,0.5), expand = c(0, NA)) + # set scales to begin at , intervals of 3 until highest value , expand prevents padding at top and bottom of y axis so it will be in line with x axis
  ylab("NREM spectral slope 30 - 45 Hz" ~(mu*V^2/Hz)) +
  theme_prism(base_size = 10, base_fontface="plain", base_line_size=0.2) +
  theme(legend.position = "none") 

plot_baseline_NREM30to45 <- plot_baseline_NREM30to45 +
   geom_errorbar(data = subset(baseline_NREM30to45_esmmeans, time == "first"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.5, position = position_nudge(x = -0.2)) +
    geom_point(data = subset(baseline_NREM30to45_esmmeans, time == "first"), aes(x=time, y=Mean, shape=time, colour=time), fill="#009E73", colour="black", size =2,  position = position_nudge(x = -0.2)) +
   # add error bar and mean for tonic (esmmeans)
    geom_errorbar(data = subset(baseline_NREM30to45_esmmeans, time == "last"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.5, position = position_nudge(x = 0.2)) +
    geom_point(data = subset(baseline_NREM30to45_esmmeans, time == "last"), aes(x=time, y=Mean, shape=time, colour=time),colour="black", size =2,  position = position_nudge(x = 0.2))  +
 # geom_line(data = baseline_ITPF_state_esmmeans, aes(x=state, y=Mean, group=1), colour = "black", linewidth = 1) +
  scale_x_discrete(name = NULL) 
ggsave("figure/figS10/baseline_NREM30to45_changeovernight.svg", plot=plot_baseline_NREM30to45, width=3, height=3)

# phasic
plot_baseline_phasic30to45 <- ggplot(df_baseline_average, aes(x = time, y = exponent_30_45_cyc_phasic, fill = time)) +
  # Left half violin for first
  geom_half_violin(data = subset(df_baseline_average, time == "first"),side = "l",  # <-- flip to left
 alpha = 0.8, trim = FALSE, position = position_nudge(x = -0.1)) +
# Right half violin for last
  geom_half_violin(data = subset(df_baseline_average, time == "last"),side = "r", alpha = 0.8, trim = FALSE, position = position_nudge(x = 0.1)) +
# join same participants with line across state
   geom_line(aes(group = participant), colour = "black", linewidth = 0.3, alpha = 0.2, position = position_jitter(width = 0.05, seed = 123)) +
  geom_point(aes(shape = time, colour=time), size=1, position = position_jitter(width = 0.05, seed = 123)) +
 scale_fill_manual(values = c("first" = "#0072B2B2", "last" = "#139FFFB2")) + 
  scale_colour_manual(values = c("first" = "#0072B2B2", "last" = "#139FFFB2")) + 
  scale_shape_manual(values = c(21,21)) +
  scale_y_continuous(limits = c(-6, -1.5), breaks = seq(-6,-1.5,0.5), expand = c(0, NA)) + # set scales to begin at , intervals of 3 until highest value , expand prevents padding at top and bottom of y axis so it will be in line with x axis
  ylab("NREM spectral slope 30 - 45 Hz" ~(mu*V^2/Hz)) +
  theme_prism(base_size = 10, base_fontface="plain", base_line_size=0.2) +
  theme(legend.position = "none") 

plot_baseline_phasic30to45 <- plot_baseline_phasic30to45 +
   geom_errorbar(data = subset(baseline_phasic30to45_esmmeans, time == "first"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.5, position = position_nudge(x = -0.2)) +
    geom_point(data = subset(baseline_phasic30to45_esmmeans, time == "first"), aes(x=time, y=Mean, shape=time, colour=time), fill="#0072B2B2", colour="black", size =2,  position = position_nudge(x = -0.2)) +
   # add error bar and mean for tonic (esmmeans)
    geom_errorbar(data = subset(baseline_phasic30to45_esmmeans, time == "last"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.5, position = position_nudge(x = 0.2)) +
    geom_point(data = subset(baseline_phasic30to45_esmmeans, time == "last"), aes(x=time, y=Mean, shape=time, colour=time),colour="black", size =2,  position = position_nudge(x = 0.2))  +
 # geom_line(data = baseline_ITPF_state_esmmeans, aes(x=state, y=Mean, group=1), colour = "black", linewidth = 1) +
  scale_x_discrete(name = NULL) 
plot_baseline_phasic30to45
#ggsave("figure/figS10/baseline_phasic30to45_changeovernight.svg", plot=plot_baseline_phasic30to45, width=3, height=3)

# tonic
plot_baseline_tonic30to45 <- ggplot(df_baseline_average, aes(x = time, y = exponent_30_45_cyc_tonic, fill = time)) +
  # Left half violin for first
  geom_half_violin(data = subset(df_baseline_average, time == "first"),side = "l",  # <-- flip to left
 alpha = 0.8, trim = FALSE, position = position_nudge(x = -0.1)) +
# Right half violin for last
  geom_half_violin(data = subset(df_baseline_average, time == "last"),side = "r", alpha = 0.8, trim = FALSE, position = position_nudge(x = 0.1)) +
# join same participants with line across state
   geom_line(aes(group = participant), colour = "black", linewidth = 0.3, alpha = 0.2, position = position_jitter(width = 0.05, seed = 123)) +
  geom_point(aes(shape = time, colour=time), size=1, position = position_jitter(width = 0.05, seed = 123)) +
 scale_fill_manual(values = c("first" = "#D55E00B2", "last" = "#E8A215B2")) + 
  scale_colour_manual(values = c("first" = "#D55E00B2", "last" = "#E8A215B2")) + 
  scale_shape_manual(values = c(21,21)) +
  scale_y_continuous(limits = c(-6, -1.5), breaks = seq(-6,-1.5,0.5), expand = c(0, NA)) + # set scales to begin at , intervals of 3 until highest value , expand prevents padding at top and bottom of y axis so it will be in line with x axis
  ylab("NREM spectral slope 30 - 45 Hz" ~(mu*V^2/Hz)) +
  theme_prism(base_size = 10, base_fontface="plain", base_line_size=0.2) +
  theme(legend.position = "none") 

plot_baseline_tonic30to45 <- plot_baseline_tonic30to45 +
   geom_errorbar(data = subset(baseline_tonic30to45_esmmeans, time == "first"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.5, position = position_nudge(x = -0.2)) +
    geom_point(data = subset(baseline_tonic30to45_esmmeans, time == "first"), aes(x=time, y=Mean, shape=time, colour=time), fill="#D55E00B2", colour="black", size =2,  position = position_nudge(x = -0.2)) +
   # add error bar and mean for tonic (esmmeans)
    geom_errorbar(data = subset(baseline_tonic30to45_esmmeans, time == "last"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.5, position = position_nudge(x = 0.2)) +
    geom_point(data = subset(baseline_tonic30to45_esmmeans, time == "last"), aes(x=time, y=Mean, shape=time, colour=time),colour="black", size =2,  position = position_nudge(x = 0.2))  +
 # geom_line(data = baseline_ITPF_state_esmmeans, aes(x=state, y=Mean, group=1), colour = "black", linewidth = 1) +
  scale_x_discrete(name = NULL) 
plot_baseline_tonic30to45
#ggsave("figure/figS10/baseline_tonic30to45_changeovernight.svg", plot=plot_baseline_tonic30to45, width=3, height=3)
```
#4  How does the "modulation" associate with slope/alpha/theta? 
```{r}
rm(list = setdiff(ls(), "df"))

library(effects) # plot partial regression
library(performance) # calc marginal(fixed-effects var) and conditional (fixed + random variance) R2
# Calculate Cohen D = estimate for fixed effect / (sqrt of sum of variances of random effects)

df_baseline <- df %>%
  filter(night == "1")

df_baseline <- df_baseline %>%  
  mutate(exponent_30_45_cyc_nrem_firstlast_diff_z = scale(exponent_30_45_cyc_nrem_firstlast_diff)) %>% 
  mutate(m_exponent_30_45_cyc_phasic_z = scale(m_exponent_30_45_cyc_phasic)) %>% 
  mutate(m_exponent_30_45_cyc_tonic_z = scale(m_exponent_30_45_cyc_tonic)) %>% 
  mutate(density_theta_phasic_z = scale(density_theta_phasic)) %>% 
  mutate(snr_alpha_phasic_z = scale(log(snr_alpha_phasic))) %>% 
  mutate(density_alpha_phasic_z = scale(density_alpha_phasic)) %>% 
  mutate(density_theta_tonic_z = scale(density_theta_tonic)) %>% 
  mutate(snr_alpha_tonic_z = scale(log(snr_alpha_tonic))) %>% 
  mutate(density_alpha_tonic_z = scale(density_alpha_tonic)) %>%
  mutate(IAPF_phasic_z = scale(IAPF_phasic)) %>% 
  mutate(IAPF_tonic_z = scale(IAPF_tonic)) %>%
  mutate(swa_NREM_z = scale(swa_NREM)) 

df_baseline$NREM_perc_z <- scale(df_baseline$NREM_perc)

# phasic ----
fit.phasicbaseline_exp30to45 <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ m_exponent_30_45_cyc_phasic_z + channel + order + swa_NREM_z + NREM_perc_z + tst + (1|participant), data=df_baseline)
phasicslope_summary <- as.data.frame(coef(summary(fit.phasicbaseline_exp30to45))) 
phasicslope_summary <- phasicslope_summary[2,]
r.squaredGLMM(fit.phasicbaseline_exp30to45)

fit.phasicbaseline_thetadensity <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ density_theta_phasic_z + channel + order + swa_NREM_z + NREM_perc_z + tst + (1|participant), data=df_baseline)
phasic_dentheta_summary <- as.data.frame(coef(summary(fit.phasicbaseline_thetadensity))) 
phasic_dentheta_summary <- phasic_dentheta_summary[2,]
r.squaredGLMM(fit.phasicbaseline_thetadensity)

fit.phasicbaseline_alphadensity <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ density_alpha_phasic_z + channel + order + swa_NREM_z + NREM_perc_z + tst + (1|participant), data=df_baseline)
phasic_denalpha_summary <- as.data.frame(coef(summary(fit.phasicbaseline_alphadensity))) 
phasic_denalpha_summary <- phasic_denalpha_summary[2,]
r.squaredGLMM(fit.phasicbaseline_alphadensity)

fit.phasicbaseline_alphamplitude <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ snr_alpha_phasic_z + channel + order + swa_NREM_z + NREM_perc_z + tst + (1|participant), data=df_baseline)
phasic_snralpha_summary <- as.data.frame(coef(summary(fit.phasicbaseline_alphamplitude))) 
phasic_snralpha_summary <- phasic_snralpha_summary[2,]
r.squaredGLMM(fit.phasicbaseline_alphamplitude)

fit.phasicbaseline_IAPF <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ IAPF_phasic_z + channel + order + swa_NREM_z + NREM_perc_z + tst + (1|participant), data=df_baseline)
phasic_IAPF_summary <- as.data.frame(coef(summary(fit.phasicbaseline_IAPF))) 
phasic_IAPF_summary <- phasic_IAPF_summary[2,]
r.squaredGLMM(fit.phasicbaseline_IAPF)

## tonic ----
fit.tonicbaseline_exp30to45 <- lmer(exponent_30_45_cyc_nrem_firstlast_diff
 ~ m_exponent_30_45_cyc_tonic_z + channel + order + swa_NREM_z + NREM_perc_z + tst + (1|participant), data=df_baseline)
tonicslope_summary <- as.data.frame(coef(summary(fit.tonicbaseline_exp30to45))) 
tonicslope_summary <- tonicslope_summary[2,]
r.squaredGLMM(fit.tonicbaseline_exp30to45)

fit.tonicbaseline_thetadensity <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ density_theta_tonic_z + channel + order + swa_NREM_z + NREM_perc_z + tst + (1|participant), data=df_baseline)
tonic_dentheta_summary <- as.data.frame(coef(summary(fit.tonicbaseline_thetadensity))) 
tonic_dentheta_summary <- tonic_dentheta_summary[2,]
r.squaredGLMM(fit.tonicbaseline_thetadensity)

fit.tonicbaseline_alphadensity <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ density_alpha_tonic_z + channel + order + swa_NREM_z + NREM_perc_z + tst + (1|participant), data=df_baseline)
tonic_denalpha_summary <- as.data.frame(coef(summary(fit.tonicbaseline_alphadensity))) 
tonic_denalpha_summary <- tonic_denalpha_summary[2,]
r.squaredGLMM(fit.tonicbaseline_alphadensity)

fit.tonicbaseline_alphamplitude <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ snr_alpha_tonic_z + channel + order + swa_NREM_z + NREM_perc_z + tst + (1|participant), data=df_baseline)
tonic_snralpha_summary <- as.data.frame(coef(summary(fit.tonicbaseline_alphamplitude))) 
tonic_snralpha_summary <- tonic_snralpha_summary[2,]
r.squaredGLMM(fit.tonicbaseline_alphamplitude)

fit.tonicbaseline_IAPF <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ IAPF_tonic_z + channel + order + swa_NREM_z + NREM_perc_z + tst + (1|participant), data=df_baseline)
tonic_IAPF_summary <- as.data.frame(coef(summary(fit.tonicbaseline_IAPF))) 
tonic_IAPF_summary <- tonic_IAPF_summary[2,]
r.squaredGLMM(fit.tonicbaseline_IAPF)

results_adj <- rbind(phasicslope_summary, phasic_dentheta_summary, phasic_snralpha_summary, phasic_denalpha_summary,phasic_IAPF_summary, tonicslope_summary, tonic_dentheta_summary, tonic_snralpha_summary, tonic_denalpha_summary,tonic_IAPF_summary) 
colnames(results_adj)[5] <- "pvalue"
results_adj <- results_adj %>%
  mutate(adj_pvalue = p.adjust(pvalue, method = "fdr"))
results_adj
```
#5. Plot table
```{r}
results_adj$sig <- ifelse(
  results_adj$adj_pvalue < 0.001, "***", 
  ifelse(results_adj$adj_pvalue < 0.01, "**",
    ifelse(results_adj$adj_pvalue < 0.05, "*", NA)))
results_adj <- results_adj %>% 
  rownames_to_column("row_names") #%>% 
results_adj$row_names <- gsub("scale\\(([^)]+)\\)", "\\1",  results_adj$row_names)

my_order <- c("IAPF_phasic_z", "IAPF_tonic_z", "density_alpha_phasic_z","density_alpha_tonic_z",  "snr_alpha_phasic_z", "snr_alpha_tonic_z",  "density_theta_phasic_z",  "density_theta_tonic_z", "m_exponent_30_45_cyc_phasic_z","m_exponent_30_45_cyc_tonic_z")


results_adj <- results_adj %>% 
  mutate(row_names = factor(row_names, levels=my_order)) %>% 
  arrange(row_names) %>% 
  mutate(across(2:6, as.numeric)) %>%  
  mutate(y = 0) 

corr_plot <- ggplot(results_adj, aes(x = row_names, y=1, fill = Estimate)) +
   geom_tile(data = results_adj %>%
             filter(is.na(sig)), #for non sig estimates =grey
            colour = "black",
            fill   = "grey85") +
  geom_tile(data = results_adj %>%
             filter(!is.na(sig)),
            aes(fill = Estimate),
            colour = "black") + # coloured for sig estimates 
 scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0) +
  coord_fixed() +
  geom_text(aes(label = ifelse(
    !is.na(sig),
    paste(round(Estimate, 2), sig, sep = "\n"),  
    as.character(round(Estimate, 2)))),
  size = 3) +
  theme_prism(base_size = 12, base_fontface="plain", base_line_size=0.2) +
  scale_x_discrete(limits = my_order, labels=c('phasic\nalpha\npeak\nfrequency','tonic\nalpha\npeak\nfrequency', 'phasic\nalpha\ndensity', 'tonic\nalpha\ndensity', 'phasic\nalpha\namplitude', 'tonic\nalpha\namplitude', 'phasic\ntheta\ndensity','tonic\ntheta\ndensity','phasic\nslope\n30-45Hz','tonic\nslope\n30-45Hz'))
#ggsave("figure/figS10/NREMovernightslope_corr_baseline.svg", plot=corr_plot, width=13, height=3)

```
#6 Plot phasic
```{r}
# Plot (loop) ----
plot_partial_resid <- function(fit, predictor, xlab, x_limits = c(-2, 5), x_breaks = seq(-2, 5, 1)) {
  
  # Handle both lm and lmer
  is_lmer <- inherits(fit, "lmerMod")
  
  # Extract coefficients - different for lm vs lmer
  ordinary_residuals  <- residuals(fit)
  coeff_of_interest   <- if(is_lmer) {
    as.numeric(fixef(fit)[predictor])      # lmer uses fixef()
  } else {
    as.numeric(coef(fit)[predictor])       # lm uses coef()
  }
  
  # Extract predictor values - same for both
  predictor_values <- as.numeric(model.frame(fit)[[predictor]])
  
  # Calculate partial residuals
  partial_residuals_calculated <- ordinary_residuals + coeff_of_interest * predictor_values

  df_points_for_plot <- data.frame(
    x_variable         = predictor_values,
    y_partial_residual = partial_residuals_calculated
  )

  # effect() works for both lm and lmer
  eff    <- effect(predictor, fit, partial.residuals = TRUE)
  df_line <- as.data.frame(eff)

  palette_cols <- c("#0072B2", "#008bd9", "#01a4ff", "#29b2ff", "#50c0ff", "#8bd5ff")
  df_points_for_plot$rand_col <- sample(
    palette_cols,
    nrow(df_points_for_plot),
    replace = TRUE
  )
  
  ggplot(data = df_points_for_plot,
         aes(x = x_variable, y = y_partial_residual)) +
    geom_point(aes(color = rand_col), size = 0.5 * 2, shape = 1, stroke = 0.35) +
    scale_color_identity() +
    geom_ribbon(data = df_line,
                aes_string(x = predictor, ymin = "lower", ymax = "upper"),
                fill = "grey", alpha = 0.3,
                inherit.aes = FALSE) +
    geom_line(data = df_line,
              aes_string(x = predictor, y = "fit"),
              color = "black", linewidth = 1,
              inherit.aes = FALSE) +
    labs(
      x     = xlab,
      y     = expression("NREM spectral slope change\nlast~NREM-first~NREM (z-score)"),
      title = ""
    ) +
    scale_x_continuous(limits = x_limits,
                       breaks = x_breaks,
                       expand = c(0, NA)) +
    scale_y_continuous(limits = c(-3, 3),
                       breaks = seq(-3, 3, 1),
                       expand = c(0, NA)) +
    theme_prism(base_size = 10, base_fontface = "plain",
                base_line_size = 0.2) +
    theme(
      legend.position = "none",
      plot.margin     = margin(10, 10, 18, 18),
      axis.title.x    = element_text(margin = margin(t = 10))
    )
}

# phasic ---- 
plot_phasicslope <- plot_partial_resid(
  fit       = fit.phasicbaseline_exp30to45,
  predictor = "m_exponent_30_45_cyc_phasic_z",
  xlab      = "phasic spectral slope 30 - 45 Hz (z-score)",
  x_limits  = c(-2, 2),
  x_breaks  = seq(-2, 2, 1)
)

plot_phasicthetadensity <- plot_partial_resid(
  fit       = fit.phasicbaseline_thetadensity,
  predictor = "density_theta_phasic_z",
  xlab      = "phasic theta density (z-score)",
  x_limits  = c(-2, 2),
  x_breaks  = seq(-2, 2, 1)
)

plot_phasicalphasnr <- plot_partial_resid(
  fit       = fit.phasicbaseline_alphamplitude,
  predictor = "snr_alpha_phasic_z",
  xlab      = "phasic alpha amplitude (log, z-score)",
  x_limits  = c(-2, 2),
  x_breaks  = seq(-2, 2, 1)
)

plot_phasicalphadensity <- plot_partial_resid(
  fit       = fit.phasicbaseline_alphadensity,
  predictor = "density_alpha_phasic_z",
  xlab      = "phasic alpha density (z-score)",
  x_limits  = c(-2, 2),
  x_breaks  = seq(-2, 2, 1)
)

plot_phasicIAPF <- plot_partial_resid(
  fit       = fit.phasicbaseline_IAPF,
  predictor = "IAPF_phasic_z",
  xlab      = "phasic IAPF (z-score)",
  x_limits  = c(-2, 2),
  x_breaks  = seq(-2, 2, 1)
)

ggsave("figure/figS10/baseline_phasicslope_corr.svg", plot=plot_phasicslope, width=4, height=4)
ggsave("figure/figS10/baseline_phasicthetadensity_corr.svg", plot=plot_phasicthetadensity, width=4, height=4)
ggsave("figure/figS10/baseline_phasicalphasnr_corr.svg", plot=plot_phasicalphasnr, width=4, height=4)
ggsave("figure/figS10/baseline_phasicalphadensity_corr.svg", plot=plot_phasicalphadensity, width=4, height=4)
ggsave("figure/figS10/baseline_phasicIAPF_corr.svg", plot=plot_phasicIAPF, width=4, height=4)

```
#7 Plot tonic
```{r}
# Plot (loop) ----
plot_partial_resid <- function(fit, predictor, xlab, x_limits = c(-2, 5), x_breaks = seq(-2, 5, 1)) {
  
  # Handle both lm and lmer
  is_lmer <- inherits(fit, "lmerMod")
  
  # Extract coefficients - different for lm vs lmer
  ordinary_residuals  <- residuals(fit)
  coeff_of_interest   <- if(is_lmer) {
    as.numeric(fixef(fit)[predictor])      # lmer uses fixef()
  } else {
    as.numeric(coef(fit)[predictor])       # lm uses coef()
  }
  
  # Extract predictor values - same for both
  predictor_values <- as.numeric(model.frame(fit)[[predictor]])
  
  # Calculate partial residuals
  partial_residuals_calculated <- ordinary_residuals + coeff_of_interest * predictor_values

  df_points_for_plot <- data.frame(
    x_variable         = predictor_values,
    y_partial_residual = partial_residuals_calculated
  )

  # effect() works for both lm and lmer
  eff    <- effect(predictor, fit, partial.residuals = TRUE)
  df_line <- as.data.frame(eff)

  palette_cols <- c("#FF7a11", "#FF9038", "#FFa65F",
                  "#FFbc87", "#FFa65F", "#FF9038")
  df_points_for_plot$rand_col <- sample(
    palette_cols,
    nrow(df_points_for_plot),
    replace = TRUE
  )
  
  ggplot(data = df_points_for_plot,
         aes(x = x_variable, y = y_partial_residual)) +
    geom_point(aes(color = rand_col), size = 0.5 * 2, shape = 1, stroke = 0.35) +
    scale_color_identity() +
    geom_ribbon(data = df_line,
                aes_string(x = predictor, ymin = "lower", ymax = "upper"),
                fill = "grey", alpha = 0.3,
                inherit.aes = FALSE) +
    geom_line(data = df_line,
              aes_string(x = predictor, y = "fit"),
              color = "black", linewidth = 1,
              inherit.aes = FALSE) +
    labs(
      x     = xlab,
      y     = expression("NREM spectral slope change\nlast~NREM-first~NREM (z-score)"),
      title = ""
    ) +
    scale_x_continuous(limits = x_limits,
                       breaks = x_breaks,
                       expand = c(0, NA)) +
    scale_y_continuous(limits = c(-3, 3),
                       breaks = seq(-3, 3, 1),
                       expand = c(0, NA)) +
    theme_prism(base_size = 10, base_fontface = "plain",
                base_line_size = 0.2) +
    theme(
      legend.position = "none",
      plot.margin     = margin(10, 10, 18, 18),
      axis.title.x    = element_text(margin = margin(t = 10))
    )

}

# tonic ---- 
plot_tonicslope <- plot_partial_resid(
  fit       = fit.tonicbaseline_exp30to45,
  predictor = "m_exponent_30_45_cyc_tonic_z",
  xlab      = "tonic spectral slope 30 - 45 Hz (z-score)",
  x_limits  = c(-2, 2),
  x_breaks  = seq(-2, 2, 1)
)

plot_tonicthetadensity <- plot_partial_resid(
  fit       = fit.tonicbaseline_thetadensity,
  predictor = "density_theta_tonic_z",
  xlab      = "tonic theta density (z-score)",
  x_limits  = c(-2, 2),
  x_breaks  = seq(-2, 2, 1)
)

plot_tonicalphasnr <- plot_partial_resid(
  fit       = fit.tonicbaseline_alphamplitude,
  predictor = "snr_alpha_tonic_z",
  xlab      = "tonic alpha amplitude (log, z-score)",
  x_limits  = c(-2, 2),
  x_breaks  = seq(-2, 2, 1)
)

plot_tonicalphadensity <- plot_partial_resid(
  fit       = fit.tonicbaseline_alphadensity,
  predictor = "density_alpha_tonic_z",
  xlab      = "tonic alpha density (z-score)",
  x_limits  = c(-2, 2),
  x_breaks  = seq(-2, 2, 1)
)

plot_tonicIAPF <- plot_partial_resid(
  fit       = fit.tonicbaseline_IAPF,
  predictor = "IAPF_tonic_z",
  xlab      = "tonic IAPF (z-score)",
  x_limits  = c(-2, 2),
  x_breaks  = seq(-2, 2, 1)
)

ggsave("figure/figS10/baseline_tonicslope_corr.svg", plot=plot_tonicslope, width=4, height=4)
ggsave("figure/figS10/baseline_tonicthetadensity_corr.svg", plot=plot_tonicthetadensity, width=4, height=4)
ggsave("figure/figS10/baseline_tonicalphasnr_corr.svg", plot=plot_tonicalphasnr, width=4, height=4)
ggsave("figure/figS10/baseline_tonicalphadensity_corr.svg", plot=plot_tonicalphadensity, width=4, height=4)
ggsave("figure/figS10/baseline_tonicIAPF_corr.svg", plot=plot_tonicIAPF, width=4, height=4)

```
#8. Supplementary How does the "modulation" associate with slope/alpha/theta?  - unified model for phasiv vs tonic testing
```{r}
rm(list = ls()[-match(c("df", "df_baseline", "results_adj"), ls())])

#exp30-45Hz
fit.baseline_exp30to45 <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ m_exponent_30_45_cyc_phasic_z + m_exponent_30_45_cyc_tonic_z + channel + order +  swa_NREM_z + NREM_perc_z + tst + (1|participant) , data=df_baseline)
slope_summary <- as.data.frame(coef(summary(fit.baseline_exp30to45))) 
slope_summary <- slope_summary[2:3,]

#theta density
fit.baseline_thetadensity <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ density_theta_phasic_z + density_theta_tonic_z+ channel + order + swa_NREM_z + NREM_perc_z + tst + (1|participant), data=df_baseline)
thetadensity_summary <- as.data.frame(coef(summary(fit.baseline_thetadensity))) 
thetadensity_summary <- thetadensity_summary[2:3,]

#alpha snr
fit.baseline_alphamplitude <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ snr_alpha_phasic_z + snr_alpha_tonic_z + channel + order + swa_NREM_z + NREM_perc_z + tst + (1|participant), data=df_baseline)
snralpha_summary <- as.data.frame(coef(summary(fit.baseline_alphamplitude))) 
snralpha_summary <- snralpha_summary[2:3,]

#alpha density
fit.baseline_alphadensity <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ density_alpha_phasic_z + density_alpha_tonic_z + channel + order + swa_NREM_z + NREM_perc_z + tst + (1|participant) , data=df_baseline)
denalpha_summary <- as.data.frame(coef(summary(fit.baseline_alphadensity))) 
denalpha_summary <- denalpha_summary[2:3,]

#IAPF
fit.baseline_IAPF <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ IAPF_phasic_z + IAPF_tonic_z + channel + order + swa_NREM_z + NREM_perc_z + tst + (1|participant) , data=df_baseline)
IAPF_summary <- as.data.frame(coef(summary(fit.baseline_IAPF))) 
IAPF_summary <- IAPF_summary[2:3,]

##
library(multcomp)

# run glht ----
run_glht <- function(model, contrasts) {
   comp <- glht(model, linfct = contrasts)
   s    <- summary(comp)
   
    tab <- data.frame(
    estimate   = s$test$coefficients,
    SE         = s$test$sigma,
    z          = s$test$tstat,
    p          = s$test$pvalues
  )
  
}

library(knitr)
library(kableExtra)

# exp30-45Hz
glht_exp30to45 <- run_glht(
  model     = fit.baseline_exp30to45,
  contrasts = "m_exponent_30_45_cyc_phasic_z - m_exponent_30_45_cyc_tonic_z =0"
)

# density theta
glht_densitytheta <- run_glht(
  model     = fit.baseline_thetadensity,
  contrasts = "density_theta_phasic_z - density_theta_tonic_z = 0"
)

# snr alpha
glht_snralpha <- run_glht(
  model     = fit.baseline_alphamplitude,
  contrasts = "snr_alpha_phasic_z - snr_alpha_tonic_z = 0"
)

# density alpha
glht_densityalpha <- run_glht(
  model     = fit.baseline_alphadensity,
  contrasts = "density_alpha_phasic_z - density_alpha_tonic_z = 0"
)


# IAPF
glht_IAPF <- run_glht(
  model     = fit.baseline_IAPF,
  contrasts = "IAPF_phasic_z - IAPF_tonic_z = 0"
)

final_glht_basetable <- rbind(
  glht_IAPF,
  glht_densityalpha,
  glht_snralpha,
  glht_densitytheta,
  glht_exp30to45
) %>% mutate(adj_pvalue = p.adjust(p, method = "fdr"))

# Row counts for pack_rows
n_IAPF         <- nrow(glht_IAPF)
n_densityalpha <- nrow(glht_densityalpha)
n_snralpha     <- nrow(glht_snralpha)
n_densitytheta <- nrow(glht_densitytheta)
n_exp30to45    <- nrow(glht_exp30to45)

# Create kable
final_glht_basetable %>%
  kable(format  = "html",
        digits  = 4,
        caption = "Phasic vs Tonic Coefficient Comparison — Baseline") %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  pack_rows("IAPF", 
            1, 
            n_IAPF) %>%
  pack_rows("Alpha Density", 
            n_IAPF + 1, 
            n_IAPF + n_densityalpha) %>%
  pack_rows("Alpha SNR", 
            n_IAPF + n_densityalpha + 1, 
            n_IAPF + n_densityalpha + n_snralpha) %>%
  pack_rows("Theta Density", 
            n_IAPF + n_densityalpha + n_snralpha + 1, 
            n_IAPF + n_densityalpha + n_snralpha + n_densitytheta) %>%
  pack_rows("Spectral Exponent 30-45Hz", 
            n_IAPF + n_densityalpha + n_snralpha + n_densitytheta + 1, 
            n_IAPF + n_densityalpha + n_snralpha + n_densitytheta + n_exp30to45)

```

## WEEK FIRST/LAST (FIG6)
#1.Fig6a,b,d,e,g,h (SS and IS overnight changes for NREM, phasic, tonic)
```{r}
rm(list = setdiff(ls(), "df"))  # Remove all but df

df_week_violins <- df %>% 
  dplyr::select(c(1:6,23:54)) #exp130cycnremfirst:offset3045cycnremlast

df_week_violins <- df_week_violins %>%  pivot_longer(
  cols = c(7:38), #allvariablesvalues
    names_to = c(".value", "time"),
    names_pattern = "(.+)_(first|last)"
)

cols <- c("participant", "condition", "night", "order", "channel", "time")
df_week_violins <- df_week_violins  %>% mutate_at(cols, factor)

# Extract baseline values and append to original frame 
baseline_values <- df_week_violins %>% 
  filter(night == "1") %>% 
  group_by(condition) %>% 
  nest() %>% 
  nest_rename_with(data, .fn = function(.x){paste0(.x,"_baseline")}, .cols=c(7:22)) %>% 
     nest_slice(data, 
              rep(1:n(), times = 9))
              
df_temp <- df_week_violins %>% 
  group_by(condition) %>% 
  nest() %>% 
  nest_arrange(data, night)

# ---
df_temp[[2]][[1]] <- cbind(df_temp[[2]][[1]],baseline_values[[2]][[1]])
df_temp[[2]][[2]] <- cbind(df_temp[[2]][[2]],baseline_values[[2]][[2]])

#---
df_week_violins <- unnest(df_temp) %>% 
  ungroup()

cols <- c("participant", "condition", "night", "order", "channel")
df_week_violins <- df_week_violins  %>% mutate_at(cols, factor)
factor(df_week_violins$night, order=TRUE,
       levels= c("1", "2", "3", "4", "5", "6", "7", "8", "9"))
```
#2. lmes 
# significance based on "time" from anova results
```{r}
# SE (sufficient sleep) ----
df_weekSE <- df_week_violins %>%  
  filter(condition=="SE")  %>%  
  filter(!night =="9")

# NREM
fit.weekSE_NREM30to45 <- lmer(exponent_30_45_cyc_nrem
 ~ night*time + channel + exponent_30_45_cyc_nrem_baseline + tst + order + (1|participant), data=df_weekSE)
anova.fitweekSE_NREM30to45 <- anova(fit.weekSE_NREM30to45)

# phasic
fit.weekSE_phasic30to45 <- lmer(exponent_30_45_cyc_phasic
 ~ night*time + channel + exponent_30_45_cyc_phasic_baseline + tst + order + (1|participant), data=df_weekSE)
anova.fitweekSE_phasic30to45 <- anova(fit.weekSE_phasic30to45)

# tonic
fit.weekSE_tonic30to45 <- lmer(exponent_30_45_cyc_tonic
 ~ night*time + channel + exponent_30_45_cyc_tonic_baseline + tst + order + (1|participant), data=df_weekSE)
anova.fitweekSE_tonic30to45 <- anova(fit.weekSE_tonic30to45)

exp30to45_SENREMfirstlast_esmmeans <- estimate_means(fit.weekSE_NREM30to45 , by = c( "time"))
exp30to45_SEphasicfirstlast_esmmeans <- estimate_means(fit.weekSE_phasic30to45 , by = c( "time"))
exp30to45_SEtonicfirstlast_esmmeans <- estimate_means(fit.weekSE_tonic30to45 , by = c( "time"))

# SR (insufficient sleep) ----
df_weekSR <- df_week_violins %>%  
  filter(condition=="SR")  %>%  
  filter(!night =="9")

# NREM
fit.weekSR_NREM30to45 <- lmer(exponent_30_45_cyc_nrem
 ~ night*time + channel + exponent_30_45_cyc_nrem_baseline + tst + order + (1|participant), data=df_weekSR)
anova.fitweekSR_NREM30to45 <- anova(fit.weekSR_NREM30to45)

# phasic
fit.weekSR_phasic30to45 <- lmer(exponent_30_45_cyc_phasic
 ~ night*time + channel + exponent_30_45_cyc_phasic_baseline + tst + order + (1|participant), data=df_weekSR)
anova.fitweekSR_phasic30to45 <- anova(fit.weekSR_phasic30to45)

# tonic
fit.weekSR_tonic30to45 <- lmer(exponent_30_45_cyc_tonic
 ~ night*time + channel + exponent_30_45_cyc_tonic_baseline + tst + order + (1|participant), data=df_weekSR)
anova.fitweekSR_tonic30to45 <- anova(fit.weekSR_tonic30to45)

exp30to45_SRNREMfirstlast_esmmeans <- estimate_means(fit.weekSR_NREM30to45 , by = c( "time"))
exp30to45_SRphasicfirstlast_esmmeans <- estimate_means(fit.weekSR_phasic30to45 , by = c( "time"))
exp30to45_SRtonicfirstlast_esmmeans <- estimate_means(fit.weekSR_tonic30to45 , by = c( "time"))
```
#3. Plot
```{r}
library(gghalves)
# SE ----
# Average for visualisation
df_weekSE_average <- df_weekSE %>% ungroup() %>% 
  dplyr::select(c(2,7,8:45)) %>% #participant, time , variables
  group_by(participant, time) %>% 
  dplyr::summarise(across(everything(), mean, na.rm=TRUE))

# NREM ----
plotSE_NREM30to45_firstlast <- ggplot(df_weekSE_average, aes(x = time, y = exponent_30_45_cyc_nrem, fill = time)) +
  # Left half violin for SE
  geom_half_violin(data = subset(df_weekSE_average, time == "first"),side = "l",  # <-- flip to left
 alpha = 0.8, trim = FALSE, position = position_nudge(x = -0.1)) +
# Right half violin for SR
  geom_half_violin(data = subset(df_weekSE_average, time == "last"), side = "r", alpha = 0.8, trim = FALSE, position = position_nudge(x = 0.1)) +
# join same participants with line across state
   geom_line(aes(group = participant), colour = "black", linewidth = 0.3, alpha = 0.2, position = position_jitter(width = 0.05, seed = 123)) +
  geom_point(aes(shape = time, colour=time), size=1, position = position_jitter(width = 0.05, seed = 123)) +
 scale_fill_manual(values = c("first" = "#009E73B2", "last" = "#40E36BB2")) + 
  scale_colour_manual(values = c("first" = "#009E73B2", "last" = "#40E36BB2")) + 
  scale_shape_manual(values = c(16,16)) +
  scale_y_continuous(limits = c(-6, -1.5), breaks = seq(-6, -1.5,0.5), expand = c(0, NA)) + # set scales to begin at , intervals of 3 until highest value , expand prevents padding at top and bottom of y axis so it will be in line with x axis
   ylab("spectral slope" ~(mu*V^2/Hz)) + 
  theme_prism(base_size = 10, base_fontface="plain", base_line_size=0.2) +
  theme(legend.position = "none") 

plotSE_NREM30to45_firstlast <- plotSE_NREM30to45_firstlast +
  # error bar and average for "first"
   geom_errorbar(data = subset(exp30to45_SENREMfirstlast_esmmeans, time == "first"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.2, position = position_nudge(x = -0.2)) +
    geom_point(data = subset(exp30to45_SENREMfirstlast_esmmeans, time == "first"), aes(x=time, y=Mean, colour=time), fill="#009E73B2", shape=21, colour="black", size =1, stroke=0.2,  position = position_nudge(x = -0.2)) +
    # error bar and average for "last"
    geom_errorbar(data = subset(exp30to45_SENREMfirstlast_esmmeans, time == "last"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.2, position = position_nudge(x = 0.2)) +
    geom_point(data = subset(exp30to45_SENREMfirstlast_esmmeans, time == "last"), aes(x=time, y=Mean, colour=time), fill="#40E36BB2", shape=21, colour="black", size =1,stroke=0.2,   position = position_nudge(x = 0.2))  +
 # geom_line(data = baseline_ITPF_state_esmmeans, aes(x=state, y=Mean, group=1), colour = "black", linewidth = 1) +
  scale_x_discrete(name = NULL) 
plotSE_NREM30to45_firstlast
ggsave("figure/fig6/NREM30to45_firstlast_SE.svg", plot=plotSE_NREM30to45_firstlast, width=1.5, height=2)

# phasic ----
plotSE_phasic30to45_firstlast <- ggplot(df_weekSE_average, aes(x = time, y = exponent_30_45_cyc_phasic, fill = time)) +
  # Left half violin for SE
  geom_half_violin(data = subset(df_weekSE_average, time == "first"),side = "l",  # <-- flip to left
 alpha = 0.8, trim = FALSE, position = position_nudge(x = -0.1)) +
# Right half violin for SR
  geom_half_violin(data = subset(df_weekSE_average, time == "last"), side = "r", alpha = 0.8, trim = FALSE, position = position_nudge(x = 0.1)) +
# join same participants with line across state
   geom_line(aes(group = participant), colour = "black", linewidth = 0.3, alpha = 0.2, position = position_jitter(width = 0.05, seed = 123)) +
  geom_point(aes(shape = time, colour=time), size=1, position = position_jitter(width = 0.05, seed = 123)) +
 scale_fill_manual(values = c("first" = "#0072B2B2", "last" = "#139FFFB2")) + 
  scale_colour_manual(values = c("first" = "#0072B2B2", "last" = "#139FFFB2")) + 
  scale_shape_manual(values = c(16,16)) +
  scale_y_continuous(limits = c(-6, -1.5), breaks = seq(-6, -1.5,0.5), expand = c(0, NA)) + # set scales to begin at , intervals of 3 until highest value , expand prevents padding at top and bottom of y axis so it will be in line with x axis
   ylab("spectral slope" ~(mu*V^2/Hz)) + 
  theme_prism(base_size = 10, base_fontface="plain", base_line_size=0.2) +
  theme(legend.position = "none") 

plotSE_phasic30to45_firstlast <- plotSE_phasic30to45_firstlast +
  # error bar and average for "first"
   geom_errorbar(data = subset(exp30to45_SEphasicfirstlast_esmmeans, time == "first"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.2, position = position_nudge(x = -0.2)) +
    geom_point(data = subset(exp30to45_SEphasicfirstlast_esmmeans, time == "first"), aes(x=time, y=Mean, colour=time), fill="#0072B2B2", shape=21, colour="black", size =1, stroke=0.2,  position = position_nudge(x = -0.2)) +
    # error bar and average for "last"
    geom_errorbar(data = subset(exp30to45_SEphasicfirstlast_esmmeans, time == "last"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.2, position = position_nudge(x = 0.2)) +
    geom_point(data = subset(exp30to45_SEphasicfirstlast_esmmeans, time == "last"), aes(x=time, y=Mean, colour=time), fill="#139FFFB2", shape=21, colour="black", size =1,stroke=0.2,   position = position_nudge(x = 0.2))  +
 # geom_line(data = baseline_ITPF_state_esmmeans, aes(x=state, y=Mean, group=1), colour = "black", linewidth = 1) +
  scale_x_discrete(name = NULL) 
plotSE_phasic30to45_firstlast
ggsave("figure/fig6/phasic30to45_firstlast_SE.svg", plot=plotSE_phasic30to45_firstlast, width=1.5, height=2)

# tonic ----
plotSE_tonic30to45_firstlast <- ggplot(df_weekSE_average, aes(x = time, y = exponent_30_45_cyc_tonic, fill = time)) +
  # Left half violin for SE
  geom_half_violin(data = subset(df_weekSE_average, time == "first"),side = "l",  # <-- flip to left
 alpha = 0.8, trim = FALSE, position = position_nudge(x = -0.1)) +
# Right half violin for SR
  geom_half_violin(data = subset(df_weekSE_average, time == "last"), side = "r", alpha = 0.8, trim = FALSE, position = position_nudge(x = 0.1)) +
# join same participants with line across state
   geom_line(aes(group = participant), colour = "black", linewidth = 0.3, alpha = 0.2, position = position_jitter(width = 0.05, seed = 123)) +
  geom_point(aes(shape = time, colour=time), size=1, position = position_jitter(width = 0.05, seed = 123)) +
 scale_fill_manual(values = c("first" = "#D55E00B2", "last" = "#E8A215B2")) + 
  scale_colour_manual(values = c("first" = "#D55E00B2", "last" = "#E8A215B2")) + 
  scale_shape_manual(values = c(16,16)) +
  scale_y_continuous(limits = c(-6, -1.5), breaks = seq(-6, -1.5,0.5), expand = c(0, NA)) + # set scales to begin at , intervals of 3 until highest value , expand prevents padding at top and bottom of y axis so it will be in line with x axis
   ylab("spectral slope" ~(mu*V^2/Hz)) + 
  theme_prism(base_size = 10, base_fontface="plain", base_line_size=0.2) +
  theme(legend.position = "none") 

plotSE_tonic30to45_firstlast <- plotSE_tonic30to45_firstlast +
  # error bar and average for "first"
   geom_errorbar(data = subset(exp30to45_SEtonicfirstlast_esmmeans, time == "first"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.2, position = position_nudge(x = -0.2)) +
    geom_point(data = subset(exp30to45_SEtonicfirstlast_esmmeans, time == "first"), aes(x=time, y=Mean, colour=time), fill="#D55E00B2", shape=21, colour="black", size =1, stroke=0.2,  position = position_nudge(x = -0.2)) +
    # error bar and average for "last"
    geom_errorbar(data = subset(exp30to45_SEtonicfirstlast_esmmeans, time == "last"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.2, position = position_nudge(x = 0.2)) +
    geom_point(data = subset(exp30to45_SEtonicfirstlast_esmmeans, time == "last"), aes(x=time, y=Mean, colour=time), fill="#E8A215B2", shape=21, colour="black", size =1,stroke=0.2,   position = position_nudge(x = 0.2))  +
 # geom_line(data = baseline_ITPF_state_esmmeans, aes(x=state, y=Mean, group=1), colour = "black", linewidth = 1) +
  scale_x_discrete(name = NULL) 
plotSE_tonic30to45_firstlast
ggsave("figure/fig6/tonic30to45_firstlast_SE.svg", plot=plotSE_tonic30to45_firstlast, width=1.5, height=2)

# SR ----
# Average for visualisation
df_weekSR_average <- df_weekSR %>% ungroup() %>% 
  dplyr::select(c(2,7,8:45)) %>% #participant, time , variables
  group_by(participant, time) %>% 
  dplyr::summarise(across(everything(), mean, na.rm=TRUE))

# NREM ----
plotSR_NREM30to45_firstlast <- ggplot(df_weekSR_average, aes(x = time, y = exponent_30_45_cyc_nrem, fill = time)) +
  # Left half violin for SE
  geom_half_violin(data = subset(df_weekSR_average, time == "first"),side = "l",  # <-- flip to left
 alpha = 0.8, trim = FALSE, position = position_nudge(x = -0.1)) +
# Right half violin for SR
  geom_half_violin(data = subset(df_weekSR_average, time == "last"), side = "r", alpha = 0.8, trim = FALSE, position = position_nudge(x = 0.1)) +
# join same participants with line across state
   geom_line(aes(group = participant), colour = "black", linewidth = 0.3, alpha = 0.2, position = position_jitter(width = 0.05, seed = 123)) +
  geom_point(aes(shape = time, colour=time), size=1, position = position_jitter(width = 0.05, seed = 123)) +
 scale_fill_manual(values = c("first" = "#009E73B2", "last" = "#40E36BB2")) + 
  scale_colour_manual(values = c("first" = "#009E73B2", "last" = "#40E36BB2")) + 
  scale_shape_manual(values = c(16,16)) +
  scale_y_continuous(limits = c(-6, -1.5), breaks = seq(-6, -1.5,0.5), expand = c(0, NA)) + # set scales to begin at , intervals of 3 until highest value , expand prevents padding at top and bottom of y axis so it will be in line with x axis
   ylab("spectral slope" ~(mu*V^2/Hz)) + 
  theme_prism(base_size = 10, base_fontface="plain", base_line_size=0.2) +
  theme(legend.position = "none") 

plotSR_NREM30to45_firstlast <- plotSR_NREM30to45_firstlast +
  # error bar and average for "first"
   geom_errorbar(data = subset(exp30to45_SRNREMfirstlast_esmmeans, time == "first"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.2, position = position_nudge(x = -0.2)) +
    geom_point(data = subset(exp30to45_SRNREMfirstlast_esmmeans, time == "first"), aes(x=time, y=Mean, colour=time), fill="#009E73B2", shape=21, colour="black", size =1, stroke=0.2,  position = position_nudge(x = -0.2)) +
    # error bar and average for "last"
    geom_errorbar(data = subset(exp30to45_SRNREMfirstlast_esmmeans, time == "last"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.2, position = position_nudge(x = 0.2)) +
    geom_point(data = subset(exp30to45_SRNREMfirstlast_esmmeans, time == "last"), aes(x=time, y=Mean, colour=time), fill="#40E36BB2", shape=21, colour="black", size =1,stroke=0.2,   position = position_nudge(x = 0.2))  +
 # geom_line(data = baseline_ITPF_state_esmmeans, aes(x=state, y=Mean, group=1), colour = "black", linewidth = 1) +
  scale_x_discrete(name = NULL) 
plotSR_NREM30to45_firstlast
#ggsave("figure/fig6/NREM30to45_firstlast_SR.svg", plot=plotSR_NREM30to45_firstlast, width=1.5, height=2)

# phasic ----
plotSR_phasic30to45_firstlast <- ggplot(df_weekSR_average, aes(x = time, y = exponent_30_45_cyc_phasic, fill = time)) +
  # Left half violin for SE
  geom_half_violin(data = subset(df_weekSR_average, time == "first"),side = "l",  # <-- flip to left
 alpha = 0.8, trim = FALSE, position = position_nudge(x = -0.1)) +
# Right half violin for SR
  geom_half_violin(data = subset(df_weekSR_average, time == "last"), side = "r", alpha = 0.8, trim = FALSE, position = position_nudge(x = 0.1)) +
# join same participants with line across state
   geom_line(aes(group = participant), colour = "black", linewidth = 0.3, alpha = 0.2, position = position_jitter(width = 0.05, seed = 123)) +
  geom_point(aes(shape = time, colour=time), size=1, position = position_jitter(width = 0.05, seed = 123)) +
 scale_fill_manual(values = c("first" = "#0072B2B2", "last" = "#139FFFB2")) + 
  scale_colour_manual(values = c("first" = "#0072B2B2", "last" = "#139FFFB2")) + 
  scale_shape_manual(values = c(16,16)) +
  scale_y_continuous(limits = c(-6, -1.5), breaks = seq(-6, -1.5,0.5), expand = c(0, NA)) + # set scales to begin at , intervals of 3 until highest value , expand prevents padding at top and bottom of y axis so it will be in line with x axis
   ylab("spectral slope" ~(mu*V^2/Hz)) + 
  theme_prism(base_size = 10, base_fontface="plain", base_line_size=0.2) +
  theme(legend.position = "none") 

plotSR_phasic30to45_firstlast <- plotSR_phasic30to45_firstlast +
  # error bar and average for "first"
   geom_errorbar(data = subset(exp30to45_SRphasicfirstlast_esmmeans, time == "first"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.2, position = position_nudge(x = -0.2)) +
    geom_point(data = subset(exp30to45_SRphasicfirstlast_esmmeans, time == "first"), aes(x=time, y=Mean, colour=time), fill="#0072B2B2", shape=21, colour="black", size =1, stroke=0.2,  position = position_nudge(x = -0.2)) +
    # error bar and average for "last"
    geom_errorbar(data = subset(exp30to45_SRphasicfirstlast_esmmeans, time == "last"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.2, position = position_nudge(x = 0.2)) +
    geom_point(data = subset(exp30to45_SRphasicfirstlast_esmmeans, time == "last"), aes(x=time, y=Mean, colour=time), fill="#139FFFB2", shape=21, colour="black", size =1,stroke=0.2,   position = position_nudge(x = 0.2))  +
 # geom_line(data = baseline_ITPF_state_esmmeans, aes(x=state, y=Mean, group=1), colour = "black", linewidth = 1) +
  scale_x_discrete(name = NULL) 
plotSR_phasic30to45_firstlast
#ggsave("figure/fig6/phasic30to45_firstlast_SR.svg", plot=plotSR_phasic30to45_firstlast, width=1.5, height=2)

# tonic ----
plotSR_tonic30to45_firstlast <- ggplot(df_weekSR_average, aes(x = time, y = exponent_30_45_cyc_tonic, fill = time)) +
  # Left half violin for SE
  geom_half_violin(data = subset(df_weekSR_average, time == "first"),side = "l",  # <-- flip to left
 alpha = 0.8, trim = FALSE, position = position_nudge(x = -0.1)) +
# Right half violin for SR
  geom_half_violin(data = subset(df_weekSR_average, time == "last"), side = "r", alpha = 0.8, trim = FALSE, position = position_nudge(x = 0.1)) +
# join same participants with line across state
   geom_line(aes(group = participant), colour = "black", linewidth = 0.3, alpha = 0.2, position = position_jitter(width = 0.05, seed = 123)) +
  geom_point(aes(shape = time, colour=time), size=1, position = position_jitter(width = 0.05, seed = 123)) +
 scale_fill_manual(values = c("first" = "#D55E00B2", "last" = "#E8A215B2")) + 
  scale_colour_manual(values = c("first" = "#D55E00B2", "last" = "#E8A215B2")) + 
  scale_shape_manual(values = c(16,16)) +
  scale_y_continuous(limits = c(-6, -1.5), breaks = seq(-6, -1.5,0.5), expand = c(0, NA)) + # set scales to begin at , intervals of 3 until highest value , expand prevents padding at top and bottom of y axis so it will be in line with x axis
   ylab("spectral slope" ~(mu*V^2/Hz)) + 
  theme_prism(base_size = 10, base_fontface="plain", base_line_size=0.2) +
  theme(legend.position = "none") 

plotSR_tonic30to45_firstlast <- plotSR_tonic30to45_firstlast +
  # error bar and average for "first"
   geom_errorbar(data = subset(exp30to45_SRtonicfirstlast_esmmeans, time == "first"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.2, position = position_nudge(x = -0.2)) +
    geom_point(data = subset(exp30to45_SRtonicfirstlast_esmmeans, time == "first"), aes(x=time, y=Mean, colour=time), fill="#D55E00B2", shape=21, colour="black", size =1, stroke=0.2,  position = position_nudge(x = -0.2)) +
    # error bar and average for "last"
    geom_errorbar(data = subset(exp30to45_SRtonicfirstlast_esmmeans, time == "last"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.2, position = position_nudge(x = 0.2)) +
    geom_point(data = subset(exp30to45_SRtonicfirstlast_esmmeans, time == "last"), aes(x=time, y=Mean, colour=time), fill="#E8A215B2", shape=21, colour="black", size =1,stroke=0.2,   position = position_nudge(x = 0.2))  +
 # geom_line(data = baseline_ITPF_state_esmmeans, aes(x=state, y=Mean, group=1), colour = "black", linewidth = 1) +
  scale_x_discrete(name = NULL) 
plotSR_tonic30to45_firstlast
#ggsave("figure/fig6/tonic30to45_firstlast_SR.svg", plot=plotSR_tonic30to45_firstlast, width=1.5, height=2)
```
## Figure 6c,f,i 
```{r}
rm(list = setdiff(ls(), "df"))  # Remove all but df

# Extract baseline values and append to original frame 
baseline_values <-df %>% 
  filter(night == "1") %>% 
  group_by(condition) %>% 
  nest() %>% 
  nest_rename_with(data, .fn = function(.x){paste0(.x,"_baseline")}, .cols=c(6:110)) %>% 
     nest_slice(data, 
              rep(1:n(), times = 9))
              
df_temp <- df %>% 
  group_by(condition) %>% 
  nest() %>% 
  nest_arrange(data, night)

# ---
df_temp[[2]][[1]] <- cbind(df_temp[[2]][[1]],baseline_values[[2]][[1]])
df_temp[[2]][[2]] <- cbind(df_temp[[2]][[2]],baseline_values[[2]][[2]])

#---
df_all <- unnest(df_temp) %>% 
  ungroup()

df_week_exp30to45 <- df_all %>% filter(!night=="9") %>% 
  dplyr::select(1:6 | contains("exponent_30_45")) %>% 
   pivot_longer(
    cols = c(19:26), #m_exponent stages
    names_to = "state_cycle",
    names_pattern = "m_exponent_30_45_cyc_(.*)",
    values_to = "exponent_cycle"
)

cols <- c("participant", "condition", "night", "order", "channel")
df <- df  %>% mutate_at(cols, factor)
factor(df$night, order=TRUE,
       levels= c("1", "2", "3", "4", "5", "6", "7", "8", "9"))
```
#2. lmes
# posthoc based on significant night*cond interaction from anova results
```{r}
df_week_exp30to45_NREM <- df_week_exp30to45 %>%  filter(state_cycle =="nrem")
df_week_exp30to45_phasic <- df_week_exp30to45 %>%  filter(state_cycle =="phasic")
df_week_exp30to45_tonic <- df_week_exp30to45 %>%  filter(state_cycle =="tonic")

fit.NREMweek_exp30_45_firstlast <- lmer(exponent_30_45_cyc_nrem_firstlast_diff
 ~ night + channel + night:condition + condition:channel + exponent_30_45_cyc_nrem_firstlast_diff_baseline + tst  + order + (1|participant), data=df_week_exp30to45_NREM)
anova.fitNREMweek_firstlast_exp30_45 <- anova(fit.NREMweek_exp30_45_firstlast)

fit.phasicweek_exp30_45_firstlast <- lmer(exponent_30_45_cyc_phasic_firstlast_diff
 ~ night + channel + night:condition + condition:channel + exponent_30_45_cyc_phasic_firstlast_diff_baseline + tst  + order + (1|participant), data=df_week_exp30to45_phasic)
anova.fitphasicweek_firstlast_exp30_45 <- anova(fit.phasicweek_exp30_45_firstlast)

fit.tonicweek_exp30_45_firstlast <- lmer(exponent_30_45_cyc_tonic_firstlast_diff
 ~ night + channel + night:condition + condition:channel + exponent_30_45_cyc_tonic_firstlast_diff_baseline + tst  + order +(1|participant), data=df_week_exp30to45_tonic)
anova.fittonicweek_firstlast_exp30_45 <- anova(fit.tonicweek_exp30_45_firstlast)

# estimated means
q2_exp30to45_NREMfirstlast_esmmeans <- estimate_means(fit.NREMweek_exp30_45_firstlast , by = c( "night", "condition"))
q2_exp30to45_phasicfirstlast_esmmeans <- estimate_means(fit.phasicweek_exp30_45_firstlast , by = c( "night", "condition"))
q2_exp30to45_tonicfirstlast_esmmeans <- estimate_means(fit.tonicweek_exp30_45_firstlast , by = c( "night", "condition"))
```
#3. Posthoc 
```{r}
pairs(emmeans(fit.NREMweek_exp30_45_firstlast, ~night:condition, by="night", p.adjust = "tukey"))
pairs(emmeans(fit.tonicweek_exp30_45_firstlast, ~night:condition, by="night", p.adjust = "tukey"))

```
#4 Plot
```{r}
NREM30to45_firstlast <- ggplot(q2_exp30to45_NREMfirstlast_esmmeans, aes(x = night, y = Mean, shape=condition, group=condition, colour=condition)) +
  geom_line(position = position_dodge(0.3)) +
  geom_errorbar(aes(x=night, y=Mean, ymin=Mean-SE, ymax=Mean+SE,), linetype=1, width=0.4, lwd=0.3, position = position_dodge(0.3)) +
  geom_point(fill="white", size=2, position = position_dodge(0.3)) +
  #geom_point(aes(colour=condition),fill="white", size=2, position = position_dodge(0.3)) +
  theme_prism(base_size = 10, base_fontface="plain", base_line_size=0.2) +
  scale_y_continuous(limits = c(-0.6, 0), breaks = seq(-0.6, 0, 0.1), expand = c(0, NA)) +
  scale_x_discrete(labels=c("B", "1", "2", "3", "4", "5", "6", "7")) +
   scale_fill_manual(values = c("SE" = "#009E73B2", "SR" = "#009E73B2")) + 
  scale_colour_manual(values = c("SE" = "#009E73B2", "SR" = "#009E73B2")) + 
  xlab("night") +  ylab("spectral slope change\n(last NREM - first NREM)") +
    scale_shape_manual(values = c(16,21)) +
   theme(legend.position="none") 
NREM30to45_firstlast

phasic30to45_firstlast <- ggplot(q2_exp30to45_phasicfirstlast_esmmeans, aes(x = night, y = Mean, shape=condition, group=condition, colour=condition)) +
  geom_line(position = position_dodge(0.3)) +
  geom_errorbar(aes(x=night, y=Mean, ymin=Mean-SE, ymax=Mean+SE,), linetype=1, width=0.4, lwd=0.3, position = position_dodge(0.3)) +
  geom_point(fill="white", size=2, position = position_dodge(0.3)) +
  #geom_point(aes(colour=condition),fill="white", size=2, position = position_dodge(0.3)) +
  theme_prism(base_size = 10, base_fontface="plain", base_line_size=0.2) +
  scale_y_continuous(limits = c(-0.4, 0.4), breaks = seq(-0.4, 0.4, 0.1), expand = c(0, NA)) +
  scale_x_discrete(labels=c("B", "1", "2", "3", "4", "5", "6", "7")) +
   scale_fill_manual(values = c("SE" = "#0072B2", "SR" = "#0072B2")) + 
  scale_colour_manual(values = c("SE" = "#0072B2", "SR" = "#0072B2")) + 
  xlab("night") +  ylab("spectral slope change\n(last phasic - first phasic)") +
    scale_shape_manual(values = c(16,21)) +
   theme(legend.position="none") 
phasic30to45_firstlast

tonic30to45_firstlast <- ggplot(q2_exp30to45_tonicfirstlast_esmmeans, aes(x = night, y = Mean, shape=condition, group=condition, colour=condition)) +
  geom_line(position = position_dodge(0.3)) +
  geom_errorbar(aes(x=night, y=Mean, ymin=Mean-SE, ymax=Mean+SE,), linetype=1, width=0.4, lwd=0.3, position = position_dodge(0.3)) +
  geom_point(fill="white", size=2, position = position_dodge(0.3)) +
  #geom_point(aes(colour=condition),fill="white", size=2, position = position_dodge(0.3)) +
  theme_prism(base_size = 10, base_fontface="plain", base_line_size=0.2) +
  scale_y_continuous(limits = c(-0.2, 0.3), breaks = seq(-0.2, 0.3, 0.1), expand = c(0, NA)) +
  scale_x_discrete(labels=c("B", "1", "2", "3", "4", "5", "6", "7")) +
   scale_fill_manual(values = c("SE" = "#D55E00B2", "SR" = "#D55E00B2")) + 
  scale_colour_manual(values = c("SE" = "#D55E00B2", "SR" = "#D55E00B2")) + 
  xlab("night") +  ylab("spectral slope change\n(last tonic - first tonic)") +
    scale_shape_manual(values = c(16,21)) +
   theme(legend.position="none") 
tonic30to45_firstlast
  
ggsave("figure/fig6/NREM30to45_firstlast_timecourse.svg", plot=NREM30to45_firstlast, width=3, height=3)
ggsave("figure/fig6/phasic30to45_firstlast_timecourse.svg", plot=phasic30to45_firstlast, width=3, height=3)
ggsave("figure/fig6/tonic30to45_firstlast_timecourse.svg", plot=tonic30to45_firstlast, width=3, height=3)
```
#5 Associations with slope/alpha/theta (Fig 6j-0) 
```{r}
rm(list = ls()[-match(c("df", "df_all"), ls())])

df_week <- df_all %>%
  filter(!night=="9") %>%
   dplyr::select(-c(112:116))

df_week <- df_week %>% 
  mutate(across(7:last_col(), scale, .names = "{.col}_z"))

df_week$tst_z <- scale(df_week$tst)

##
## phasic ----
fit.week_exp30to45_phasic <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ m_exponent_30_45_cyc_phasic_z  + m_exponent_30_45_cyc_phasic_baseline_z + exponent_30_45_cyc_nrem_firstlast_diff_baseline_z + night + condition:night + channel +order + swa_NREM_z + swa_NREM_baseline_z + NREM_perc_z + NREM_perc_baseline_z + tst_z + (1|participant), data=df_week)
phasicslope_summary <- as.data.frame(coef(summary(fit.week_exp30to45_phasic))) 
phasicslope_summary <- phasicslope_summary[2,]
r.squaredGLMM(fit.week_exp30to45_phasic)

fit.week_densitytheta_phasic <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ density_theta_phasic_z  + density_theta_phasic_baseline_z + exponent_30_45_cyc_nrem_firstlast_diff_baseline_z + night + channel +order + condition:night + swa_NREM_z + swa_NREM_baseline_z + NREM_perc_z + NREM_perc_baseline_z + tst_z + (1|participant), data=df_week)
phasic_dentheta_summary <- as.data.frame(coef(summary(fit.week_densitytheta_phasic))) 
phasic_dentheta_summary <- phasic_dentheta_summary[2,]
r.squaredGLMM(fit.week_densitytheta_phasic)

fit.week_snralpha_phasic <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ snr_alpha_phasic_z +  snr_alpha_phasic_baseline_z + exponent_30_45_cyc_nrem_firstlast_diff_baseline_z + night + condition:night + channel +order + swa_NREM_z + swa_NREM_baseline_z + NREM_perc_z + NREM_perc_baseline_z + tst_z  + (1|participant), data=df_week)
phasic_snralpha_summary <- as.data.frame(coef(summary(fit.week_snralpha_phasic))) 
phasic_snralpha_summary <- phasic_snralpha_summary[2,]
r.squaredGLMM(fit.week_snralpha_phasic)

fit.week_densityalpha_phasic <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ density_alpha_phasic_z +  density_alpha_phasic_baseline_z + exponent_30_45_cyc_nrem_firstlast_diff_baseline_z + night + condition:night + channel +order +  swa_NREM_z + swa_NREM_baseline_z + NREM_perc_z + NREM_perc_baseline_z + tst_z + (1|participant), data=df_week)
phasic_denalpha_summary <- as.data.frame(coef(summary(fit.week_densityalpha_phasic))) 
phasic_denalpha_summary <- phasic_denalpha_summary[2,]
r.squaredGLMM(fit.week_densityalpha_phasic)

fit.week_IAPF_phasic <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ IAPF_phasic_z +  IAPF_phasic_baseline_z + exponent_30_45_cyc_nrem_firstlast_diff_baseline_z + night + condition:night + channel +order + swa_NREM_z + swa_NREM_baseline_z + NREM_perc_z + NREM_perc_baseline_z + tst_z + (1|participant), data=df_week)
phasic_IAPF_summary <- as.data.frame(coef(summary(fit.week_IAPF_phasic))) 
phasic_IAPF_summary <- phasic_IAPF_summary[2,]
r.squaredGLMM(fit.week_IAPF_phasic)

## tonic ----
fit.week_exp30to45_tonic <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ m_exponent_30_45_cyc_tonic_z  + m_exponent_30_45_cyc_tonic_baseline_z + exponent_30_45_cyc_nrem_firstlast_diff_baseline_z + night + condition:night + channel +order + swa_NREM_z + swa_NREM_baseline_z + NREM_perc_z + NREM_perc_baseline_z + tst_z + (1|participant), data=df_week)
tonicslope_summary <- as.data.frame(coef(summary(fit.week_exp30to45_tonic))) 
tonicslope_summary <- tonicslope_summary[2,]
r.squaredGLMM(fit.week_exp30to45_tonic)

fit.week_densitytheta_tonic <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ density_theta_tonic_z  + density_theta_tonic_baseline_z + exponent_30_45_cyc_nrem_firstlast_diff_baseline_z + night + channel +order + condition:night + swa_NREM_z + swa_NREM_baseline_z + NREM_perc_z + NREM_perc_baseline_z + tst_z + (1|participant), data=df_week)
tonic_dentheta_summary <- as.data.frame(coef(summary(fit.week_densitytheta_tonic))) 
tonic_dentheta_summary <- tonic_dentheta_summary[2,]
r.squaredGLMM(fit.week_densitytheta_tonic)

fit.week_snralpha_tonic <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ snr_alpha_tonic_z +  snr_alpha_tonic_baseline_z + exponent_30_45_cyc_nrem_firstlast_diff_baseline_z + night + condition:night + channel +order + swa_NREM_z + swa_NREM_baseline_z + NREM_perc_z + NREM_perc_baseline_z + tst_z  + (1|participant), data=df_week)
tonic_snralpha_summary <- as.data.frame(coef(summary(fit.week_snralpha_tonic))) 
tonic_snralpha_summary <- tonic_snralpha_summary[2,]
r.squaredGLMM(fit.week_snralpha_tonic)

fit.week_densityalpha_tonic <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ density_alpha_tonic_z +  density_alpha_tonic_baseline_z + exponent_30_45_cyc_nrem_firstlast_diff_baseline_z + night + condition:night + channel +order +  swa_NREM_z + swa_NREM_baseline_z + NREM_perc_z + NREM_perc_baseline_z + tst_z + (1|participant), data=df_week)
tonic_denalpha_summary <- as.data.frame(coef(summary(fit.week_densityalpha_tonic))) 
tonic_denalpha_summary <- tonic_denalpha_summary[2,]
r.squaredGLMM(fit.week_densityalpha_tonic)

fit.week_IAPF_tonic <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ IAPF_tonic_z +  IAPF_tonic_baseline_z + exponent_30_45_cyc_nrem_firstlast_diff_baseline_z + night + condition:night + channel +order + swa_NREM_z + swa_NREM_baseline_z + NREM_perc_z + NREM_perc_baseline_z + tst_z + (1|participant), data=df_week)
tonic_IAPF_summary <- as.data.frame(coef(summary(fit.week_IAPF_tonic))) 
tonic_IAPF_summary <- tonic_IAPF_summary[2,]
r.squaredGLMM(fit.week_IAPF_tonic)

##

results_adj <- rbind(phasicslope_summary, phasic_dentheta_summary, phasic_denalpha_summary,phasic_snralpha_summary,phasic_IAPF_summary,tonicslope_summary, tonic_dentheta_summary, tonic_denalpha_summary, tonic_snralpha_summary,tonic_IAPF_summary) 
colnames(results_adj)[5] <- "pvalue"
results_adj <- results_adj %>%
  mutate(adj_pvalue = p.adjust(pvalue, method = "fdr"))
results_adj
```
#6 Plot table
```{r}
results_adj$sig <- ifelse(
  results_adj$adj_pvalue < 0.001, "***", 
  ifelse(results_adj$adj_pvalue < 0.01, "**",
    ifelse(results_adj$adj_pvalue < 0.05, "*", NA)))
results_adj <- results_adj %>% 
  rownames_to_column("row_names") #%>% 
results_adj$row_names <- gsub("scale\\(([^)]+)\\)", "\\1",  results_adj$row_names)

my_order <- c("IAPF_phasic_z", "IAPF_tonic_z", "density_alpha_phasic_z","density_alpha_tonic_z",  "snr_alpha_phasic_z", "snr_alpha_tonic_z",  "density_theta_phasic_z",  "density_theta_tonic_z", "m_exponent_30_45_cyc_phasic_z","m_exponent_30_45_cyc_tonic_z")

results_adj <- results_adj %>% 
  mutate(row_names = factor(row_names, levels=my_order)) %>% 
  arrange(row_names) %>% 
  mutate(across(2:6, as.numeric)) %>%  
  mutate(y = 0) 

corr_plot <- ggplot(results_adj, aes(x = row_names, y=1, fill = Estimate)) +
   geom_tile(data = results_adj %>%
             filter(is.na(sig)), #for non sig estimates =grey
            colour = "black",
            fill   = "grey85") +
  geom_tile(data = results_adj %>%
             filter(!is.na(sig)),
            aes(fill = Estimate),
            colour = "black") + # coloured for sig estimates 
 scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0) +
  coord_fixed() +
  geom_text(aes(label = ifelse(
    !is.na(sig),
    paste(round(Estimate, 2), sig, sep = "\n"),  
    as.character(round(Estimate, 2)))),
  size = 3) +
  theme_prism(base_size = 12, base_fontface="plain", base_line_size=0.2) +
  scale_x_discrete(limits = my_order, labels=c('Phasic\nalpha\npeak\nfrequency','Tonic\nalpha\npeak\nfrequency', 'Phasic\nalpha\ndensity', 'Tonic\nalpha\ndensity', 'Phasic\nalpha\namplitude', 'Tonic\nalpha\namplitude', 'Phasic\ntheta\ndensity','Tonic\ntheta\ndensity','Phasic\nslope\n30-45Hz','Tonic\nslope\n30-45Hz'))
#ggsave("figure/fig6/NREMovernightslope_corr.svg", plot=corr_plot, width=13, height=3)

```
#7 Plot phasic
```{r}
# Plot (loop) ----
plot_partial_resid <- function(fit, predictor, xlab, x_limits = c(-2, 5), x_breaks = seq(-2, 5, 1)) {
  ordinary_residuals <- residuals(fit)
  coeff_of_interest <- as.numeric(fixef(fit)[predictor])
  predictor_values <- as.numeric(model.frame(fit)[[predictor]])
  partial_residuals_calculated <- ordinary_residuals + coeff_of_interest * predictor_values

  df_points_for_plot <- data.frame(
    x_variable = predictor_values,
    y_partial_residual = partial_residuals_calculated
  )

  eff <- effect(predictor, fit, partial.residuals = TRUE)
  df_line <- as.data.frame(eff)

  palette_cols <- c("#0072B2", "#008bd9", "#01a4ff","#29b2ff", "#50c0ff", "#8bd5ff")
df_points_for_plot$rand_col <- sample(
  palette_cols,
  nrow(df_points_for_plot),
  replace = TRUE
)

  ggplot(data = df_points_for_plot,
         aes(x = x_variable, y = y_partial_residual)) +
     geom_point(aes(color = rand_col), size = 0.5 * 2, shape=1, stroke=0.35) +
     scale_color_identity() +
    geom_line(data = df_line,
              aes_string(x = predictor, y = "fit"),
              color = "black", linewidth = 1) +
    geom_ribbon(data = df_line,
                aes_string(x = predictor, y = "fit",
                           ymin = "lower", ymax = "upper"),
                fill = "grey", alpha = 0.3) +
    labs(
      x = xlab,
      y = expression("NREM spectral slope change\nlast~NREM-first~NREM (z-score)"),
      title = ""
    ) +
    scale_x_continuous(limits = x_limits,
                       breaks = x_breaks,
                       expand = c(0, NA)) +
    scale_y_continuous(limits = c(-6.5, 7.5),
                       breaks = seq(-6, 7, 1),
                       expand = c(0, NA)) +
    theme_prism(base_size = 10, base_fontface = "plain",
                base_line_size = 0.2) +
    theme(
      legend.position = "none",
      plot.margin = margin(10, 10, 18, 18),
      axis.title.x = element_text(margin = margin(t = 10))
    )
}

# phasic ---- 
plot_phasicslope <- plot_partial_resid(
  fit       = fit.week_exp30to45_phasic,
  predictor = "m_exponent_30_45_cyc_phasic_z",
  xlab      = "phasic spectral slope 30 - 45 Hz (z-score)",
  x_limits  = c(-5, 3),
  x_breaks  = seq(-5, 3, 1)
)

plot_phasicthetadensity <- plot_partial_resid(
  fit       = fit.week_densitytheta_phasic,
  predictor = "density_theta_phasic_z",
  xlab      = "phasic theta density (z-score)",
  x_limits  = c(-3, 5),
  x_breaks  = seq(-3, 5, 1)
)

plot_phasicalphasnr <- plot_partial_resid(
  fit       = fit.week_snralpha_phasic,
  predictor = "snr_alpha_phasic_z",
  xlab      = "phasic alpha amplitude (log, z-score)",
  x_limits  = c(-2, 6),
  x_breaks  = seq(-2, 6, 1)
)

plot_phasicalphadensity <- plot_partial_resid(
  fit       = fit.week_densityalpha_phasic,
  predictor = "density_alpha_phasic_z",
  xlab      = "phasic alpha density (z-score)",
  x_limits  = c(-3, 4),
  x_breaks  = seq(-3, 4, 1)
)

plot_phasicIAPF <- plot_partial_resid(
  fit       = fit.week_IAPF_phasic,
  predictor = "IAPF_phasic_z",
  xlab      = "phasic alpha peak frequency (z-score)",
  x_limits  = c(-3, 4),
  x_breaks  = seq(-3, 4, 1)
)

ggsave("figure/figS12/phasicslope_corr.svg", plot=plot_phasicslope, width=4, height=4)
ggsave("figure/figS12/phasicthetadensity_corr.svg", plot=plot_phasicthetadensity, width=4, height=4)
ggsave("figure/figS12/phasicalphasnr_corr.svg", plot=plot_phasicalphasnr, width=4, height=4)
ggsave("figure/figS12/phasicalphadensity_corr.svg", plot=plot_phasicalphadensity, width=4, height=4)
ggsave("figure/fig6/phasicIAPF_corr.svg", plot=plot_phasicIAPF, width=4, height=4)

```
#8 Plot tonic
```{r}
# Plot (loop) ----
plot_partial_resid <- function(fit, predictor, xlab, x_limits = c(-2, 5), x_breaks = seq(-2, 5, 1)) {
  ordinary_residuals <- residuals(fit)
  coeff_of_interest <- as.numeric(fixef(fit)[predictor])
  predictor_values <- as.numeric(model.frame(fit)[[predictor]])
  partial_residuals_calculated <- ordinary_residuals + coeff_of_interest * predictor_values

  df_points_for_plot <- data.frame(
    x_variable = predictor_values,
    y_partial_residual = partial_residuals_calculated
  )

  eff <- effect(predictor, fit, partial.residuals = TRUE)
  df_line <- as.data.frame(eff)

  palette_cols <- c("#FF7a11", "#FF9038", "#FFa65F",
                  "#FFbc87", "#FFa65F", "#FF9038")
df_points_for_plot$rand_col <- sample(
  palette_cols,
  nrow(df_points_for_plot),
  replace = TRUE
)

  ggplot(data = df_points_for_plot,
         aes(x = x_variable, y = y_partial_residual)) +
     geom_point(aes(color = rand_col), size = 0.5 * 2, shape=1, stroke=0.35) +
     scale_color_identity() +
    geom_line(data = df_line,
              aes_string(x = predictor, y = "fit"),
              color = "black", linewidth = 1) +
    geom_ribbon(data = df_line,
                aes_string(x = predictor, y = "fit",
                           ymin = "lower", ymax = "upper"),
                fill = "grey", alpha = 0.3) +
    labs(
      x = xlab,
      y = expression("NREM spectral slope change\nlast~NREM-first~NREM (z-score)"),
      title = ""
    ) +
    scale_x_continuous(limits = x_limits,
                       breaks = x_breaks,
                       expand = c(0, NA)) +
    scale_y_continuous(limits = c(-6.5, 7.5),
                       breaks = seq(-6, 7, 1),
                       expand = c(0, NA)) +
    theme_prism(base_size = 10, base_fontface = "plain",
                base_line_size = 0.2) +
    theme(
      legend.position = "none",
      plot.margin = margin(10, 10, 18, 18),
      axis.title.x = element_text(margin = margin(t = 10))
    )
}

# tonic ---- 
plot_tonicslope <- plot_partial_resid(
  fit       = fit.week_exp30to45_tonic,
  predictor = "m_exponent_30_45_cyc_tonic_z",
  xlab      = "tonic spectral slope 30 - 45 Hz (z-score)",
  x_limits  = c(-5, 3),
  x_breaks  = seq(-5, 3, 1)
)

plot_tonicthetadensity <- plot_partial_resid(
  fit       = fit.week_densitytheta_tonic,
  predictor = "density_theta_tonic_z",
  xlab      = "tonic theta density (z-score)",
  x_limits  = c(-3, 5),
  x_breaks  = seq(-3, 5, 1)
)

plot_tonicalphasnr <- plot_partial_resid(
  fit       = fit.week_snralpha_tonic,
  predictor = "snr_alpha_tonic_z",
  xlab      = "tonic alpha amplitude (log, z-score)",
  x_limits  = c(-2, 6),
  x_breaks  = seq(-2, 6, 1)
)

plot_tonicalphadensity <- plot_partial_resid(
  fit       = fit.week_densityalpha_tonic,
  predictor = "density_alpha_tonic_z",
  xlab      = "tonic alpha density (z-score)",
  x_limits  = c(-3, 4),
  x_breaks  = seq(-3, 4, 1)
)

plot_tonicIAPF <- plot_partial_resid(
  fit       = fit.week_IAPF_tonic,
  predictor = "IAPF_tonic_z",
  xlab      = "tonic alpha peak frequency (z-score)",
  x_limits  = c(-3, 4),
  x_breaks  = seq(-3, 4, 1)
)

ggsave("figure/fig6/tonicslope_corr.svg", plot=plot_tonicslope, width=4, height=4)
ggsave("figure/fig6/tonicthetadensity_corr.svg", plot=plot_tonicthetadensity, width=4, height=4)
ggsave("figure/fig6/tonicalphasnr_corr.svg", plot=plot_tonicalphasnr, width=4, height=4)
ggsave("figure/figS12/tonicalphadensity_corr.svg", plot=plot_tonicalphadensity, width=4, height=4)
ggsave("figure/figS12/tonicIAPF_corr.svg", plot=plot_tonicIAPF, width=4, height=4)

```
#9. Supplementary Associations with slope/alpha/theta (Fig 6j-0) - unified model for phasic vs tonic testing
```{r}
## lmes ----
fit.week_exp30to45 <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ m_exponent_30_45_cyc_phasic_z + m_exponent_30_45_cyc_tonic_z + m_exponent_30_45_cyc_phasic_baseline_z +  m_exponent_30_45_cyc_tonic_baseline_z + exponent_30_45_cyc_nrem_firstlast_diff_baseline_z + night + condition:night + channel +order + swa_NREM_z + swa_NREM_baseline_z + NREM_perc_z + NREM_perc_baseline_z + tst_z + (1|participant), data=df_week)
slope_summary <- as.data.frame(coef(summary(fit.week_exp30to45))) 
slope_summary <- slope_summary[2:3,]


fit.week_densitytheta <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ density_theta_phasic_z + density_theta_tonic_z + density_theta_phasic_baseline_z + density_theta_tonic_baseline_z + exponent_30_45_cyc_nrem_firstlast_diff_baseline_z + night + channel +order + condition:night + swa_NREM_z + swa_NREM_baseline_z + NREM_perc_z + NREM_perc_baseline_z + tst_z + (1|participant), data=df_week)
dentheta_summary <- as.data.frame(coef(summary(fit.week_densitytheta))) 
dentheta_summary <- dentheta_summary[2:3,]


fit.week_snralpha <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ snr_alpha_phasic_z +  snr_alpha_tonic_z +  snr_alpha_phasic_baseline_z +  snr_alpha_tonic_baseline_z +  exponent_30_45_cyc_nrem_firstlast_diff_baseline_z + night + condition:night + channel +order + swa_NREM_z + swa_NREM_baseline_z + NREM_perc_z + NREM_perc_baseline_z + tst_z  + (1|participant), data=df_week)
snralpha_summary <- as.data.frame(coef(summary(fit.week_snralpha))) 
snralpha_summary <- snralpha_summary[2:3,]


fit.week_densityalpha <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ density_alpha_phasic_z +  density_alpha_tonic_z +  density_alpha_phasic_baseline_z +  density_alpha_tonic_baseline_z +  exponent_30_45_cyc_nrem_firstlast_diff_baseline_z + night + condition:night + channel +order +  swa_NREM_z + swa_NREM_baseline_z + NREM_perc_z + NREM_perc_baseline_z + tst_z + (1|participant), data=df_week)
denalpha_summary <- as.data.frame(coef(summary(fit.week_densityalpha))) 
denalpha_summary <- denalpha_summary[2:3,]


fit.week_IAPF <- lmer(exponent_30_45_cyc_nrem_firstlast_diff_z
 ~ IAPF_phasic_z +   IAPF_tonic_z +  IAPF_phasic_baseline_z + IAPF_tonic_baseline_z +  exponent_30_45_cyc_nrem_firstlast_diff_baseline_z + night + condition:night + channel +order + swa_NREM_z + swa_NREM_baseline_z + NREM_perc_z + NREM_perc_baseline_z + tst_z + (1|participant), data=df_week)
IAPF_summary <- as.data.frame(coef(summary(fit.week_IAPF))) 
IAPF_summary <- IAPF_summary[2:3,]


# run glht for phasic vs tonic coeff comparision ----
run_glht <- function(model, contrasts) {
   comp <- glht(model, linfct = contrasts)
   s    <- summary(comp)
   
    tab <- data.frame(
    estimate   = s$test$coefficients,
    SE         = s$test$sigma,
    z          = s$test$tstat,
    p          = s$test$pvalues
  )
  
}

# IAPF
glht_IAPF <- run_glht(
  model     = fit.week_IAPF,
  contrasts = "IAPF_phasic_z - IAPF_tonic_z = 0"
)

# density alpha
glht_densityalpha <- run_glht(
  model     = fit.week_densityalpha,
  contrasts = "density_alpha_phasic_z - density_alpha_tonic_z = 0"
)

# snr alpha
glht_snralpha <- run_glht(
  model     = fit.week_snralpha,
  contrasts = "snr_alpha_phasic_z - snr_alpha_tonic_z = 0"
)

# density theta
glht_densitytheta <- run_glht(
  model     = fit.week_densitytheta,
  contrasts = "density_theta_phasic_z - density_theta_tonic_z = 0"
)

# exp30-45Hz
glht_exp30to45 <- run_glht(
  model     = fit.week_exp30to45,
  contrasts = "m_exponent_30_45_cyc_phasic_z - m_exponent_30_45_cyc_tonic_z =0"
)

final_glht_weektable <- rbind(
  glht_IAPF,
  glht_densityalpha,
  glht_snralpha,
  glht_densitytheta,
  glht_exp30to45
) %>% mutate(adj_pvalue = p.adjust(p, method="fdr")) 

# Row counts for pack_rows
n_IAPF         <- nrow(glht_IAPF)
n_densityalpha <- nrow(glht_densityalpha)
n_snralpha     <- nrow(glht_snralpha)
n_densitytheta <- nrow(glht_densitytheta)
n_exp30to45    <- nrow(glht_exp30to45)

# Create kable
final_glht_weektable %>%
  kable(format  = "html",
        digits  = 4,
        caption = "Phasic vs Tonic Coefficient Comparison — Week") %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  pack_rows("IAPF", 
            1, 
            n_IAPF) %>%
  pack_rows("Alpha Density", 
            n_IAPF + 1, 
            n_IAPF + n_densityalpha) %>%
  pack_rows("Alpha SNR", 
            n_IAPF + n_densityalpha + 1, 
            n_IAPF + n_densityalpha + n_snralpha) %>%
  pack_rows("Theta Density", 
            n_IAPF + n_densityalpha + n_snralpha + 1, 
            n_IAPF + n_densityalpha + n_snralpha + n_densitytheta) %>%
  pack_rows("Spectral Exponent 30-45Hz", 
            n_IAPF + n_densityalpha + n_snralpha + n_densitytheta + 1, 
            n_IAPF + n_densityalpha + n_snralpha + n_densitytheta + n_exp30to45)

```