---
title: "triplets excitability"
output: html_notebook
---

#Import functions
```{r}
library(devtools)
library(lmerTest)
library(lme4)
library(emmeans)
library(tidyverse)
library(broom)
library(kableExtra)
library(ggpubr)
library(ggprism)
library(modelbased)
```

#1. Load dataset
```{r}
df <- readRDS("df_triplet_18Aug26.rds")

cols <- c("participant", "condition", "night", "order", "channel")
df <- df  %>% mutate_at(cols, factor)
factor(df$night, order=TRUE,
       levels= c("1", "2", "3", "4", "5", "6", "7", "8", "9"))

df <- df %>% relocate(order, .after =tst)
```
#2. lmes
# significance based on "NREM (pre/post)" from anova results
```{r}
df_baseline <- df %>% filter(night=="1") %>% 
  dplyr::select(c(1:6,23:30)) # pres and posts

df_baseline <- df_baseline %>% 
  pivot_longer(
  cols = c(7:14), 
    names_to = c(".value", "NREM"),
    names_pattern = "(.+)_(pre|post)"
)

fit.baseline_NREM30to45 <- lmer(exponent_30_45
 ~ channel + order + NREM + tst + (1|participant), data=df_baseline)
anova.fitbaseline_NREM30to45 <- anova(fit.baseline_NREM30to45)

# estimated means
baseline_NREM30to45_esmmeans <- estimate_means(fit.baseline_NREM30to45 , by = c("NREM"))
```
#3. Baseline: plot Fig S11a
```{r}
library(gghalves)
df_baseline_average <- df_baseline %>% ungroup() %>% 
  dplyr::select(!c(2:6)) %>% 
  group_by(participant, NREM) %>% 
  dplyr::summarise(across(everything(), mean, na.rm=TRUE))

df_baseline_average$NREM <- factor(df_baseline_average$NREM, levels = c("pre", "post"))

plot_baseline_NREM30to45 <- ggplot(df_baseline_average, aes(x = NREM, y = exponent_30_45, fill = NREM)) +
  # Left half violin for first
  geom_half_violin(data = subset(df_baseline_average, NREM == "pre"),side = "l",  # <-- flip to left
 alpha = 0.8, trim = FALSE, position = position_nudge(x = -0.1)) +
# Right half violin for last
  geom_half_violin(data = subset(df_baseline_average, NREM == "post"),side = "r", alpha = 0.8, trim = FALSE, position = position_nudge(x = 0.1)) +
# join same participants with line across state
   geom_line(aes(group = participant), colour = "black", linewidth = 0.3, alpha = 0.2, position = position_jitter(width = 0.05, seed = 123)) +
  geom_point(aes(shape = NREM, colour=NREM), size=1, position = position_jitter(width = 0.05, seed = 123)) +
 scale_fill_manual(values = c("pre" = "#009E73", "post" = "#CC79A7")) + 
  scale_colour_manual(values = c("pre" = "#009E73", "post" = "#CC79A7")) + 
  scale_shape_manual(values = c(21,21)) +
  scale_y_continuous(limits = c(-5, -1.5), breaks = seq(-5, -1.5,0.5), expand = c(0, NA)) + # set scales to begin at , intervals of 3 until highest value , expand prevents padding at top and bottom of y axis so it will be in line with x axis
   ylab("NREM spectral slope 30 - 45 Hz" ~(mu*V^2/Hz)) + 
  theme_prism(base_size = 10, base_fontface="plain", base_line_size=0.2) +
  theme(legend.position = "none") 

plot_baseline_NREM30to45 <- plot_baseline_NREM30to45 +
   geom_errorbar(data = subset(baseline_NREM30to45_esmmeans, NREM == "pre"), aes(x=NREM, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.5, position = position_nudge(x = -0.2)) +
    geom_point(data = subset(baseline_NREM30to45_esmmeans, NREM == "pre"), aes(x=NREM, y=Mean, shape=NREM, colour=NREM), fill="#009E73", colour="black", size =2,  position = position_nudge(x = -0.2)) +
   # add error bar and mean for tonic (esmmeans)
    geom_errorbar(data = subset(baseline_NREM30to45_esmmeans, NREM == "post"), aes(x=NREM, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.5, position = position_nudge(x = 0.2)) +
    geom_point(data = subset(baseline_NREM30to45_esmmeans, NREM == "post"), aes(x=NREM, y=Mean, shape=NREM, colour=NREM),colour="black", size =2,  position = position_nudge(x = 0.2))  +
 # geom_line(data = baseline_ITPF_state_esmmeans, aes(x=state, y=Mean, group=1), colour = "black", linewidth = 1) +
  scale_x_discrete(name = NULL) 
plot_baseline_NREM30to45
#ggsave("figure/figS11/baseline_NREM30to45_triplet.svg", plot=plot_baseline_NREM30to45, width=3, height=3)
```
#4. Baseline: associations with slope/alpha/theta FigS11b-g 
```{r}
df_baseline <- df %>%
  filter(night == "1")

df_baseline <- df_baseline %>%  
  mutate(across(exponent_1_30_prepost_diff:spindle_power_between_tonic, scale, .names = "{.col}_z"))

df_baseline$NREM_perc_z <- scale(df_baseline$NREM_perc)

#phasic ----
fit.phasicbaseline_exp30to45 <- lmer(exponent_30_45_prepost_diff_z
 ~ exponent_30_45_between_phasic_z + channel + order + swa_between_phasic_z + NREM_perc_z + scale(tst) + (1|participant), data=df_baseline)
phasicslope_summary <- as.data.frame(coef(summary(fit.phasicbaseline_exp30to45))) 
phasicslope_summary <- phasicslope_summary[2,]
r.squaredGLMM(fit.phasicbaseline_exp30to45)

fit.phasicbaseline_dentheta <- lmer(exponent_30_45_prepost_diff_z
 ~ den_theta_between_phasic_z + channel + order + swa_between_phasic_z +  NREM_perc_z + scale(tst) + (1|participant), data=df_baseline)
phasic_dentheta_summary <- as.data.frame(coef(summary(fit.phasicbaseline_dentheta))) 
phasic_dentheta_summary <- phasic_dentheta_summary[2,]
r.squaredGLMM(fit.phasicbaseline_dentheta)

fit.phasicbaseline_snralpha <- lmer(exponent_30_45_prepost_diff_z
 ~ snr_alpha_between_phasic_z + channel + order + swa_between_phasic_z +  NREM_perc_z + scale(tst) + (1|participant), data=df_baseline)
phasic_snralpha_summary <- as.data.frame(coef(summary(fit.phasicbaseline_snralpha))) 
phasic_snralpha_summary <- phasic_snralpha_summary[2,]
r.squaredGLMM(fit.phasicbaseline_snralpha)

fit.phasicbaseline_denalpha <- lmer(exponent_30_45_prepost_diff_z
 ~ den_alpha_between_phasic_z + channel + order + swa_between_phasic_z +  NREM_perc_z + scale(tst) + (1|participant), data=df_baseline)
phasic_denalpha_summary <- as.data.frame(coef(summary(fit.phasicbaseline_denalpha))) 
phasic_denalpha_summary <- phasic_denalpha_summary[2,]
r.squaredGLMM(fit.phasicbaseline_denalpha)

fit.phasicbaseline_IAPF <- lmer(exponent_30_45_prepost_diff_z
 ~ IAPF_between_phasic_z + channel + order + swa_between_phasic_z +  NREM_perc_z + scale(tst) + (1|participant), data=df_baseline)
phasic_IAPF_summary <- as.data.frame(coef(summary(fit.phasicbaseline_IAPF))) 
phasic_IAPF_summary <- phasic_IAPF_summary[2,]
r.squaredGLMM(fit.phasicbaseline_IAPF)

## tonic ----
fit.tonicbaseline_exp30to45 <- lmer(exponent_30_45_prepost_diff_z
 ~ exponent_30_45_between_tonic_z + channel + order + swa_between_tonic_z +  NREM_perc_z + scale(tst) + (1|participant), data=df_baseline)
tonicslope_summary <- as.data.frame(coef(summary(fit.tonicbaseline_exp30to45))) 
toniccslope_summary <- tonicslope_summary[2,]
r.squaredGLMM(fit.tonicbaseline_exp30to45)

fit.tonicbaseline_snralpha <- lmer(exponent_30_45_prepost_diff_z
 ~ snr_alpha_between_tonic_z + channel + order + swa_between_tonic_z +  NREM_perc_z + scale(tst) + (1|participant), data=df_baseline)
tonic_snralpha_summary <- as.data.frame(coef(summary(fit.tonicbaseline_snralpha))) 
tonic_snralpha_summary <- tonic_snralpha_summary[2,]
r.squaredGLMM(fit.tonicbaseline_snralpha)

fit.tonicbaseline_dentheta <- lmer(exponent_30_45_prepost_diff_z
 ~ den_theta_between_tonic_z + channel + order + swa_between_tonic_z +  NREM_perc_z + scale(tst) + (1|participant), data=df_baseline)
tonic_dentheta_summary <- as.data.frame(coef(summary(fit.tonicbaseline_dentheta))) 
tonic_dentheta_summary <- tonic_dentheta_summary[2,]
r.squaredGLMM(fit.tonicbaseline_dentheta)

fit.tonicbaseline_denalpha <- lmer(exponent_30_45_prepost_diff_z
 ~ den_alpha_between_tonic_z + channel + order + swa_between_tonic_z +  NREM_perc_z + scale(tst) + (1|participant), data=df_baseline)
tonic_denalpha_summary <- as.data.frame(coef(summary(fit.tonicbaseline_denalpha))) 
tonic_denalpha_summary <- tonic_denalpha_summary[2,]
r.squaredGLMM(fit.tonicbaseline_denalpha)

fit.tonicbaseline_IAPF <- lmer(exponent_30_45_prepost_diff_z
 ~ IAPF_between_tonic_z + channel + order + swa_between_tonic_z +  NREM_perc_z + scale(tst) + (1|participant), data=df_baseline)
tonic_IAPF_summary <- as.data.frame(coef(summary(fit.tonicbaseline_IAPF))) 
tonic_IAPF_summary <- tonic_IAPF_summary[2,]
r.squaredGLMM(fit.tonicbaseline_IAPF)

##

results_adj <- rbind(phasicslope_summary, phasic_dentheta_summary, phasic_snralpha_summary,phasic_denalpha_summary,phasic_IAPF_summary, toniccslope_summary, tonic_dentheta_summary, tonic_snralpha_summary, tonic_denalpha_summary,tonic_IAPF_summary) 
colnames(results_adj)[5] <- "pvalue"
results_adj <- results_adj %>%
  mutate(adj_pvalue = p.adjust(pvalue, method = "fdr"))
results_adj
```
#5 Plot table corr
```{r}
results_adj$sig <- ifelse(
  results_adj$adj_pvalue < 0.001, "***", 
  ifelse(results_adj$adj_pvalue < 0.01, "**",
    ifelse(results_adj$adj_pvalue < 0.05, "*", NA)))
results_adj <- results_adj %>% 
  rownames_to_column("row_names") #%>% 
results_adj$row_names <- gsub("scale\\(([^)]+)\\)", "\\1",  results_adj$row_names)

my_order <- c("IAPF_between_phasic_z", "IAPF_between_tonic_z","den_alpha_between_phasic_z","den_alpha_between_tonic_z",  "snr_alpha_between_phasic_z", "snr_alpha_between_tonic_z","den_theta_between_phasic_z",  "den_theta_between_tonic_z", "exponent_30_45_between_phasic_z","exponent_30_45_between_tonic_z")

results_adj <- results_adj %>% 
  mutate(row_names = factor(row_names, levels=my_order)) %>% 
  arrange(row_names) %>% 
  mutate(across(2:6, as.numeric)) %>%  
  mutate(y = 0) 

corr_plot <- ggplot(results_adj, aes(x = row_names, y=1, fill = Estimate)) +
   geom_tile(data = results_adj %>%
             filter(is.na(sig)), #for non sig estimates =grey
            colour = "black",
            fill   = "grey85") +
  geom_tile(data = results_adj %>%
             filter(!is.na(sig)),
            aes(fill = Estimate),
            colour = "black") + # coloured for sig estimates 
 scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0) +
  coord_fixed() +
  geom_text(aes(label = ifelse(
    !is.na(sig),
    paste(round(Estimate, 2), sig, sep = "\n"),  
    as.character(round(Estimate, 2)))),
  size = 3) +
  theme_prism(base_size = 12, base_fontface="plain", base_line_size=0.2) +
  scale_x_discrete(limits = my_order, labels=c('phasic\nalpha\npeak\nfrequency','tonic\nalpha\npeak\nfrequency', 'phasic\nalpha\ndensity', 'tonic\nalpha\ndensity', 'phasic\nalpha\namplitude', 'tonic\nalpha\namplitude', 'phasic\ntheta\ndensity','tonic\ntheta\ndensity','phasic\nslope\n30-45Hz','tonic\nslope\n30-45Hz'))
#ggsave("figure/figS11/baselinetripletallplot_corr.svg", plot=corr_plot, width=13, height=3)

```
#6 Plot phasic
```{r}
# Plot (loop) ----
plot_partial_resid <- function(fit, predictor, xlab, x_limits = c(-2, 5), x_breaks = seq(-2, 5, 1)) {
  ordinary_residuals <- residuals(fit)
  coeff_of_interest <- as.numeric(fixef(fit)[predictor])
  predictor_values <- as.numeric(model.frame(fit)[[predictor]])
  partial_residuals_calculated <- ordinary_residuals + coeff_of_interest * predictor_values

  df_points_for_plot <- data.frame(
    x_variable = predictor_values,
    y_partial_residual = partial_residuals_calculated
  )

  eff <- effect(predictor, fit, partial.residuals = TRUE)
  df_line <- as.data.frame(eff)

    palette_cols <- c("#0072B2", "#008bd9", "#01a4ff","#29b2ff", "#50c0ff", "#8bd5ff")
df_points_for_plot$rand_col <- sample(
  palette_cols,
  nrow(df_points_for_plot),
  replace = TRUE
)

  ggplot(data = df_points_for_plot,
         aes(x = x_variable, y = y_partial_residual)) +
     geom_point(aes(color = rand_col), size = 0.5 * 2, shape=1, stroke=0.35) +
     scale_color_identity() +
    geom_line(data = df_line,
              aes_string(x = predictor, y = "fit"),
              color = "black", linewidth = 1) +
    geom_ribbon(data = df_line,
                aes_string(x = predictor, y = "fit",
                           ymin = "lower", ymax = "upper"),
                fill = "grey", alpha = 0.3) +
    labs(
      x = xlab,
      y = expression("NREM spectral slope change\nNREM post - NREM pre (z-score)"),
      title = ""
    ) +
    scale_x_continuous(limits = x_limits,
                       breaks = x_breaks,
                       expand = c(0, NA)) +
    scale_y_continuous(limits = c(-3, 3),
                       breaks = seq(-3, 3, 1),
                       expand = c(0, NA)) +
    theme_prism(base_size = 10, base_fontface = "plain",
                base_line_size = 0.2) +
    theme(
      legend.position = "none",
      plot.margin = margin(10, 10, 18, 18),
      axis.title.x = element_text(margin = margin(t = 10))
    )
}

# phasic ---- 
plot_phasicslope <- plot_partial_resid(
  fit       = fit.phasicbaseline_exp30to45,
  predictor = "exponent_30_45_between_phasic_z",
  xlab      = "phasic spectral slope 30 - 45 Hz (z-score)",
  x_limits  = c(-2, 2),
  x_breaks  = seq(-2, 2, 1)
)

plot_phasicthetadensity <- plot_partial_resid(
  fit       = fit.phasicbaseline_dentheta,
  predictor = "den_theta_between_phasic_z",
  xlab      = "phasic theta density (z-score)",
  x_limits  = c(-2, 2),
  x_breaks  = seq(-2, 2, 1)
)

plot_phasicalphasnr <- plot_partial_resid(
  fit       = fit.phasicbaseline_snralpha,
  predictor = "snr_alpha_between_phasic_z",
  xlab      = "phasic alpha amplitude (log, z-score)",
  x_limits  = c(-2, 2),
  x_breaks  = seq(-2, 2, 1)
)

plot_phasicalphadensity <- plot_partial_resid(
  fit       = fit.phasicbaseline_denalpha,
  predictor = "den_alpha_between_phasic_z",
  xlab      = "phasic alpha density (z-score)",
  x_limits  = c(-2, 2),
  x_breaks  = seq(-2, 2, 1)
)

plot_phasicIAPF <- plot_partial_resid(
  fit       = fit.phasicbaseline_IAPF,
  predictor = "IAPF_between_phasic_z",
  xlab      = "phasic alpha peak frequency (z-score)",
  x_limits  = c(-2, 2),
  x_breaks  = seq(-2, 2, 1)
)

#ggsave("figure/figS11/baseline_phasicslope_corr.svg", plot=plot_phasicslope, width=4, height=4)
#ggsave("figure/figS11/baseline_phasicthetadensity_corr.svg", plot=plot_phasicthetadensity, width=4, height=4)
#ggsave("figure/figS11/baseline_phasicalphasnr_corr.svg", plot=plot_phasicalphasnr, width=4, height=4)
#ggsave("figure/figS11/baseline_phasicalphadensity_corr.svg", plot=plot_phasicalphadensity, width=4, height=4)
#ggsave("figure/figS11/baseline_phasicIAPF_corr.svg", plot=plot_phasicIAPF, width=4, height=4)


```
#7 Plot tonic
```{r}
# Plot (loop) ----
plot_partial_resid <- function(fit, predictor, xlab, x_limits = c(-2, 5), x_breaks = seq(-2, 5, 1)) {
  ordinary_residuals <- residuals(fit)
  coeff_of_interest <- as.numeric(fixef(fit)[predictor])
  predictor_values <- as.numeric(model.frame(fit)[[predictor]])
  partial_residuals_calculated <- ordinary_residuals + coeff_of_interest * predictor_values

  df_points_for_plot <- data.frame(
    x_variable = predictor_values,
    y_partial_residual = partial_residuals_calculated
  )

  eff <- effect(predictor, fit, partial.residuals = TRUE)
  df_line <- as.data.frame(eff)
  
    palette_cols <- c("#FF7a11", "#FF9038", "#FFa65F",
                  "#FFbc87", "#FFa65F", "#FF9038")
df_points_for_plot$rand_col <- sample(
  palette_cols,
  nrow(df_points_for_plot),
  replace = TRUE
)

  ggplot(data = df_points_for_plot,
         aes(x = x_variable, y = y_partial_residual)) +
     geom_point(aes(color = rand_col), size = 0.5 * 2, shape=1, stroke=0.35) +
     scale_color_identity() +
    geom_line(data = df_line,
              aes_string(x = predictor, y = "fit"),
              color = "black", linewidth = 1) +
    geom_ribbon(data = df_line,
                aes_string(x = predictor, y = "fit",
                           ymin = "lower", ymax = "upper"),
                fill = "grey", alpha = 0.3) +
    labs(
      x = xlab,
      y = expression("NREM spectral slope change\nNREM post - NREM pre (z-score)"),
      title = ""
    ) +
    scale_x_continuous(limits = x_limits,
                       breaks = x_breaks,
                       expand = c(0, NA)) +
    scale_y_continuous(limits = c(-3, 3),
                       breaks = seq(-3, 3, 1),
                       expand = c(0, NA)) +
    theme_prism(base_size = 10, base_fontface = "plain",
                base_line_size = 0.2) +
    theme(
      legend.position = "none",
      plot.margin = margin(10, 10, 18, 18),
      axis.title.x = element_text(margin = margin(t = 10))
    )
}

# tonic ---- 
plot_tonicslope <- plot_partial_resid(
  fit       = fit.tonicbaseline_exp30to45,
  predictor = "exponent_30_45_between_tonic_z",
  xlab      = "tonic spectral slope 30 - 45 Hz (z-score)",
  x_limits  = c(-2, 2),
  x_breaks  = seq(-2, 2, 1)
)

plot_tonicthetadensity <- plot_partial_resid(
  fit       = fit.tonicbaseline_dentheta,
  predictor = "den_theta_between_tonic_z",
  xlab      = "tonic theta density (z-score)",
  x_limits  = c(-2, 2),
  x_breaks  = seq(-2, 2, 1)
)

plot_tonicalphasnr <- plot_partial_resid(
  fit       = fit.tonicbaseline_snralpha,
  predictor = "snr_alpha_between_tonic_z",
  xlab      = "tonic alpha amplitude (log, z-score)",
  x_limits  = c(-2, 2),
  x_breaks  = seq(-2, 2, 1)
)

plot_tonicalphadensity <- plot_partial_resid(
  fit       = fit.tonicbaseline_denalpha,
  predictor = "den_alpha_between_tonic_z",
  xlab      = "tonic alpha density (z-score)",
  x_limits  = c(-2, 2),
  x_breaks  = seq(-2, 2, 1)
)

plot_tonicIAPF <- plot_partial_resid(
  fit       = fit.tonicbaseline_IAPF,
  predictor = "IAPF_between_tonic_z",
  xlab      = "tonic alpha peak frequency (z-score)",
  x_limits  = c(-2, 2),
  x_breaks  = seq(-2, 2, 1)
)

ggsave("figure/figS11/baseline_tonicslope_corr.svg", plot=plot_tonicslope, width=4, height=4)
ggsave("figure/figS11/baseline_tonicthetadensity_corr.svg", plot=plot_tonicthetadensity, width=4, height=4)
ggsave("figure/figS11/baseline_tonicalphasnr_corr.svg", plot=plot_tonicalphasnr, width=4, height=4)
ggsave("figure/figS11/baseline_tonicalphadensity_corr.svg", plot=plot_tonicalphadensity, width=4, height=4)
ggsave("figure/figS11/baseline_tonicIAPF_corr.svg", plot=plot_tonicIAPF, width=4, height=4)

```
#8. Baseline: associations with slope/alpha/theta FigS11b-g - unified model 
```{r}
fit.baseline_exp30to45 <- lmer(exponent_30_45_prepost_diff_z
 ~ exponent_30_45_between_phasic_z + exponent_30_45_between_tonic_z + swa_between_phasic_z + swa_between_tonic_z + channel + order + scale(tst) + (1|participant), data=df_baseline)

fit.baseline_dentheta <- lmer(exponent_30_45_prepost_diff_z
 ~ den_theta_between_phasic_z + den_theta_between_tonic_z + swa_between_phasic_z + swa_between_tonic_z + channel + order + scale(tst) + (1|participant), data=df_baseline)

fit.baseline_snralpha <- lmer(exponent_30_45_prepost_diff_z
 ~ snr_alpha_between_phasic_z + snr_alpha_between_tonic_z + swa_between_phasic_z + swa_between_tonic_z + channel + order + scale(tst) + (1|participant), data=df_baseline)

fit.baseline_denalpha <- lmer(exponent_30_45_prepost_diff_z
 ~ den_alpha_between_phasic_z + den_alpha_between_tonic_z+ swa_between_phasic_z + swa_between_tonic_z + channel + order + scale(tst) + (1|participant), data=df_baseline)

fit.baseline_IAPF <- lmer(exponent_30_45_prepost_diff_z
 ~ IAPF_between_phasic_z + IAPF_between_tonic_z + swa_between_phasic_z + swa_between_tonic_z + channel + order + scale(tst) + (1|participant), data=df_baseline)


##
# run glht for phasic vs tonic coeff comparision ----
run_glht <- function(model, contrasts) {
   comp <- glht(model, linfct = contrasts)
   s    <- summary(comp)
   
    tab <- data.frame(
    estimate   = s$test$coefficients,
    SE         = s$test$sigma,
    z          = s$test$tstat,
    p          = s$test$pvalues
  )
  
}

# IAPF
glht_IAPF <- run_glht(
  model     = fit.baseline_IAPF,
  contrasts = "IAPF_between_phasic_z - IAPF_between_tonic_z = 0"
)

# density alpha
glht_densityalpha <- run_glht(
  model     = fit.baseline_denalpha,
  contrasts = "den_alpha_between_phasic_z - den_alpha_between_tonic_z = 0"
)

# snr alpha
glht_snralpha <- run_glht(
  model     = fit.baseline_snralpha,
  contrasts = "snr_alpha_between_phasic_z - snr_alpha_between_tonic_z = 0"
)

# density theta
glht_densitytheta <- run_glht(
  model     = fit.baseline_dentheta,
  contrasts = "den_theta_between_phasic_z - den_theta_between_tonic_z = 0"
)

# exp30-45Hz
glht_exp30to45 <- run_glht(
  model     = fit.baseline_exp30to45,
  contrasts = "exponent_30_45_between_phasic_z - exponent_30_45_between_tonic_z =0"
)

final_glht_basetable <- rbind(
 glht_IAPF,
  glht_densityalpha,
  glht_snralpha,
  glht_densitytheta,
  glht_exp30to45
)  %>% mutate(adj_pvalue = p.adjust(p, method="fdr")) 

# Row counts for pack_rows
n_IAPF         <- nrow(glht_IAPF)
n_densityalpha <- nrow(glht_densityalpha)
n_snralpha     <- nrow(glht_snralpha)
n_densitytheta <- nrow(glht_densitytheta)
n_exp30to45    <- nrow(glht_exp30to45)

# Create kable
final_glht_basetable %>%
  kable(format  = "html",
        digits  = 4,
        caption = "Phasic vs Tonic Coefficient Comparison — Week") %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  pack_rows("IAPF", 
            1, 
            n_IAPF) %>%
  pack_rows("Alpha Density", 
            n_IAPF + 1, 
            n_IAPF + n_densityalpha) %>%
  pack_rows("Alpha SNR", 
            n_IAPF + n_densityalpha + 1, 
            n_IAPF + n_densityalpha + n_snralpha) %>%
  pack_rows("Theta Density", 
            n_IAPF + n_densityalpha + n_snralpha + 1, 
            n_IAPF + n_densityalpha + n_snralpha + n_densitytheta) %>%
  pack_rows("Spectral Exponent 30-45Hz", 
            n_IAPF + n_densityalpha + n_snralpha + n_densitytheta + 1, 
            n_IAPF + n_densityalpha + n_snralpha + n_densitytheta + n_exp30to45)

```




#9. append baseline values for whole week analysis 
```{r}
rm(list = setdiff(ls(), "df"))  # Remove all but df

baseline_values <- df %>% 
  filter(night == "1") %>% 
  group_by(condition) %>% 
  nest() %>% 
  nest_rename_with(data, .fn = function(.x){paste0(.x,"_baseline")}, .cols=c(6:81)) %>% 
     nest_slice(data, 
              rep(1:n(), times = 9)) 
              
df_temp <- df %>% 
  group_by(condition) %>% 
  nest() %>% 
  nest_arrange(data, night)

# ---
df_temp[[2]][[1]] <- cbind(df_temp[[2]][[1]],baseline_values[[2]][[1]])
df_temp[[2]][[2]] <- cbind(df_temp[[2]][[2]],baseline_values[[2]][[2]])

#---
df_temp <- unnest(df_temp) %>% 
  ungroup()
####

df_week <- df_temp %>%  
  filter(!night=="9") %>% 
  dplyr::select(c(1:6,23:30))
df_week <- df_week %>%  pivot_longer(
  cols = c(7:14), 
    names_to  = c("value", "time", "state"),
    names_pattern = "^(exponent_\\d+_\\d+|offset_\\d+_\\d+)_(pre|post)_(nrem|rem|phasic|tonic)$",
    values_to = "measurement"
)


df_week_baseline <- df_temp %>%  
  filter(!night=="9") %>% 
  dplyr::select(c(1:6,97:104))
df_week_baseline <- df_week_baseline %>%  pivot_longer(
  cols = c(7:14), 
    names_to  = c("value", "time", "state"),
    names_pattern = "^(exponent_\\d+_\\d+|offset_\\d+_\\d+)_(pre|post)_(nrem|rem|phasic|tonic)_baseline$",
    values_to = "measurement_baseline"
) %>% dplyr::select(10)

df_week_long <- cbind(
  df_week,
  df_week_baseline)

cols <- c("participant", "condition", "night", "order", "channel", "time", "state")
df_week_long <- df_week_long  %>% mutate_at(cols, factor)
```
#10. lmes and plot
# significance based on "time (pre/post)" from anova results (Fig S9A)
```{r}
df_week_SE <- df_week_long %>%  
  filter(condition=="SE") %>%  
  filter(state=="nrem") %>% 
  filter(value=="exponent_30_45")

df_week_SR <- df_week_long %>%  
  filter(condition=="SR") %>%  
    filter(state=="nrem") %>% 
  filter(value=="exponent_30_45")

# NREM
#SE
fit.week_NREM30to45_SE <- lmer(measurement
 ~ night*time + channel + measurement_baseline + tst + order + (1|participant), data=df_week_SE)
anova.fitweek_NREM30to45_SE <- anova(fit.week_NREM30to45_SE)

#SR
fit.week_NREM30to45_SR <- lmer(measurement
 ~ night*time + channel + measurement_baseline + tst + order + (1|participant), data=df_week_SR)
anova.fitweek_NREM30to45_SR <- anova(fit.week_NREM30to45_SR)

# Plot ----
# SE
exp30to45_prepost_SE_esmmeans <- estimate_means(fit.week_NREM30to45_SE , by = c( "time"))
exp30to45_prepost_SR_esmmeans <- estimate_means(fit.week_NREM30to45_SR , by = c( "time"))


library(gghalves)
# Average for visualisation
df_week_average_SE <- df_week_SE %>% ungroup() %>% 
  dplyr::select(c(2,8,10:11)) %>% #participant, time , variables
  group_by(participant, time) %>% 
  dplyr::summarise(across(everything(), mean, na.rm=TRUE))

df_week_average_SR <- df_week_SR %>% ungroup() %>% 
  dplyr::select(c(2,8,10:11)) %>% #participant, time , variables
  group_by(participant, time) %>% 
  dplyr::summarise(across(everything(), mean, na.rm=TRUE))


# SE ----
plot_NREM30to45_prepost_SE <- ggplot(df_week_average_SE, aes(x = time, y = measurement, fill = time)) +
  # Left half violin for pre
  geom_half_violin(data = subset(df_week_average_SE, time == "pre"),side = "l",  # <-- flip to left
 alpha = 0.8, trim = FALSE, position = position_nudge(x = -0.1)) +
# Right half violin for post
  geom_half_violin(data = subset(df_week_average_SE, time == "post"), side = "r", alpha = 0.8, trim = FALSE, position = position_nudge(x = 0.1)) +
# join same participants with line across state
   geom_line(aes(group = participant), colour = "black", linewidth = 0.3, alpha = 0.2, position = position_jitter(width = 0.05, seed = 123)) +
  geom_point(aes(shape = time, colour=time), size=1, position = position_jitter(width = 0.05, seed = 123)) +
 scale_fill_manual(values = c("pre" = "#009E73", "post" = "#CC79A7")) + 
  scale_colour_manual(values = c("pre" = "#009E73", "post" = "#CC79A7")) + 
  scale_shape_manual(values = c(1,1)) +
  scale_y_continuous(limits = c(-5, -1.5), breaks = seq(-5, -1.5,0.5), expand = c(0, NA)) + # set scales to begin at , intervals of 3 until highest value , expand prevents padding at top and bottom of y axis so it will be in line with x axis
   ylab("NREM spectral slope 30 - 45 Hz" ~(mu*V^2/Hz)) + 
  theme_prism(base_size = 6, base_fontface="plain", base_line_size=0.2) +
  theme(legend.position = "none") 

plot_NREM30to45_prepost_SE <- plot_NREM30to45_prepost_SE +
  # error bar and average for "first"
   geom_errorbar(data = subset(exp30to45_prepost_SE_esmmeans, time == "pre"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.2, position = position_nudge(x = -0.2)) +
    geom_point(data = subset(exp30to45_prepost_SE_esmmeans, time == "pre"), aes(x=time, y=Mean, colour=time), fill="#009E73", shape=21, colour="black", size =1, stroke=0.2,  position = position_nudge(x = -0.2)) +
    # error bar and average for "last"
    geom_errorbar(data = subset(exp30to45_prepost_SE_esmmeans, time == "post"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.2, position = position_nudge(x = 0.2)) +
    geom_point(data = subset(exp30to45_prepost_SE_esmmeans, time == "post"), aes(x=time, y=Mean, colour=time), fill="#CC79A7", shape=21, colour="black", size =1,stroke=0.2,   position = position_nudge(x = 0.2))  +
 # geom_line(data = baseline_ITPF_state_esmmeans, aes(x=state, y=Mean, group=1), colour = "black", linewidth = 1) +
  scale_x_discrete(name = NULL) 
plot_NREM30to45_prepost_SE

# SR ----
plot_NREM30to45_prepost_SR <- ggplot(df_week_average_SR, aes(x = time, y = measurement, fill = time)) +
  # Left half violin for pre
  geom_half_violin(data = subset(df_week_average_SR, time == "pre"),side = "l",  # <-- flip to left
 alpha = 0.8, trim = FALSE, position = position_nudge(x = -0.1)) +
# Right half violin for post
  geom_half_violin(data = subset(df_week_average_SR, time == "post"), side = "r", alpha = 0.8, trim = FALSE, position = position_nudge(x = 0.1)) +
# join same participants with line across state
   geom_line(aes(group = participant), colour = "black", linewidth = 0.3, alpha = 0.2, position = position_jitter(width = 0.05, seed = 123)) +
  geom_point(aes(shape = time, colour=time), size=1, position = position_jitter(width = 0.05, seed = 123)) +
 scale_fill_manual(values = c("pre" = "#009E73", "post" = "#CC79A7")) + 
  scale_colour_manual(values = c("pre" = "#009E73", "post" = "#CC79A7")) + 
  scale_shape_manual(values = c(1,1)) +
  scale_y_continuous(limits = c(-5, -1.5), breaks = seq(-5, -1.5,0.5), expand = c(0, NA)) + # set scales to begin at , intervals of 3 until highest value , expand prevents padding at top and bottom of y axis so it will be in line with x axis
   ylab("NREM spectral slope 30 - 45 Hz" ~(mu*V^2/Hz)) + 
  theme_prism(base_size = 6, base_fontface="plain", base_line_size=0.2) +
  theme(legend.position = "none") 

plot_NREM30to45_prepost_SR <- plot_NREM30to45_prepost_SR +
  # error bar and average for "first"
   geom_errorbar(data = subset(exp30to45_prepost_SR_esmmeans, time == "pre"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.2, position = position_nudge(x = -0.2)) +
    geom_point(data = subset(exp30to45_prepost_SR_esmmeans, time == "pre"), aes(x=time, y=Mean, colour=time), fill="#009E73", shape=21, colour="black", size =1, stroke=0.2,  position = position_nudge(x = -0.2)) +
    # error bar and average for "last"
    geom_errorbar(data = subset(exp30to45_prepost_SR_esmmeans, time == "post"), aes(x=time, y=Mean, ymin=Mean-SE, ymax=Mean+SE), width=0.1, lwd=0.2, position = position_nudge(x = 0.2)) +
    geom_point(data = subset(exp30to45_prepost_SR_esmmeans, time == "post"), aes(x=time, y=Mean, colour=time), fill="#CC79A7", shape=21, colour="black", size =1,stroke=0.2,   position = position_nudge(x = 0.2))  +
 # geom_line(data = baseline_ITPF_state_esmmeans, aes(x=state, y=Mean, group=1), colour = "black", linewidth = 1) +
  scale_x_discrete(name = NULL) 
plot_NREM30to45_prepost_SR

#ggsave("figure/figS9/week_NREM30to45prepost_SE.svg", plot=plot_NREM30to45_prepost_SE, width=1.5, height=2)
#ggsave("figure/figS9/week_NREM30to45prepost_SR.svg", plot=plot_NREM30to45_prepost_SR, width=1.5, height=2)

```
#11. Fig S9g
```{r}
df_week <- df_temp  %>% 
  filter (!night ==9)

fit.NREMweek_exp30_45_prepost <- lmer(exponent_30_45_prepost_diff
 ~ night + channel + night:condition + condition:channel + exponent_30_45_prepost_diff_baseline + tst + order + (1|participant), data=df_week)
anova.fitNREMweek_prepost_exp30_45 <- anova(fit.NREMweek_exp30_45_prepost)

# Posthoc ----
pairs(emmeans(fit.NREMweek_exp30_45_prepost, ~night:condition, by="night", p.adjust = "tukey"))
#Perform contrasts comparing each level of night to the baseline (night == 1) separately by condition

# Plot 
q2_exp30to45_NREMprepost_esmmeans <- estimate_means(fit.NREMweek_exp30_45_prepost , by = c( "night", "condition"))

NREM30to45_triplet <-ggplot(q2_exp30to45_NREMprepost_esmmeans, aes(x = night, y = Mean, shape=condition, group=condition, colour=condition)) +
  geom_line(position = position_dodge(0.3)) +
  geom_errorbar(aes(x=night, y=Mean, ymin=Mean-SE, ymax=Mean+SE,), linetype=1, width=0.4, lwd=0.3, position = position_dodge(0.3)) +
  geom_point(fill="white", size=2, position = position_dodge(0.3)) +
  #geom_point(aes(colour=condition),fill="white", size=2, position = position_dodge(0.3)) +
  theme_prism(base_size = 10, base_fontface="plain", base_line_size=0.2) +
  scale_y_continuous(limits = c(-1.1, -0.6), breaks = seq(-1.1, -0.6, 0.1), expand = c(0, NA)) +
  scale_x_discrete(labels=c("B", "1", "2", "3", "4", "5", "6", "7")) +
   scale_fill_manual(values = c("SE" = "#009E73B2", "SR" = "#009E73B2")) + 
  scale_colour_manual(values = c("SE" = "#009E73B2", "SR" = "#009E73B2")) + 
  xlab("night") +  ylab("spectral slope change\n(NREMpost - NREMpre") +
    scale_shape_manual(values = c(16,21)) +
   theme(legend.position="none") 
NREM30to45_triplet
#ggsave("figure/figS9/week_tripletprepostdiff.svg", plot=NREM30to45_triplet, width=4, height=4)
```
#12. Associations and plots (Fig S9k-s)
```{r}
df_week <- df_week %>%  
    filter(!night=="9") %>%
   dplyr::select(-c(83:87)) %>%
  mutate(across(exponent_1_30_prepost_diff:last_col(), scale, .names = "{.col}_z"))

#phasic
fit.week_exp30to45_phasic <- lmer(exponent_30_45_prepost_diff_z
 ~ exponent_30_45_between_phasic_z + exponent_30_45_between_phasic_baseline_z + exponent_30_45_prepost_diff_baseline_z + swa_between_phasic_z + swa_between_phasic_baseline_z + NREM_perc_z + NREM_perc_baseline_z + channel +night + condition:night + scale(tst) + (1|participant), data=df_week)
phasicslope_summary <- as.data.frame(coef(summary(fit.week_exp30to45_phasic))) 
phasicslope_summary <- phasicslope_summary[2,]
r.squaredGLMM(fit.week_exp30to45_phasic)

fit.week_IAPF_phasic <- lmer(exponent_30_45_prepost_diff_z
 ~ IAPF_between_phasic_z + IAPF_between_phasic_baseline_z + exponent_30_45_prepost_diff_baseline_z + swa_between_phasic_z + swa_between_phasic_baseline_z + NREM_perc_z + NREM_perc_baseline_z + channel +night + condition:night + scale(tst) + (1|participant), data=df_week)
phasic_IAPF_summary <- as.data.frame(coef(summary(fit.week_IAPF_phasic))) 
phasic_IAPF_summary <- phasic_IAPF_summary[2,]
r.squaredGLMM(fit.week_IAPF_phasic)

fit.week_dentheta_phasic <- lmer(exponent_30_45_prepost_diff_z
 ~ den_theta_between_phasic_z + den_theta_between_phasic_baseline_z + exponent_30_45_prepost_diff_baseline_z +swa_between_phasic_z + swa_between_phasic_baseline_z + NREM_perc_z + NREM_perc_baseline_z + channel +night + condition:night + scale(tst) + (1|participant), data=df_week)
phasic_dentheta_summary <- as.data.frame(coef(summary(fit.week_dentheta_phasic))) 
phasic_dentheta_summary <- phasic_dentheta_summary[2,]
r.squaredGLMM(fit.week_dentheta_phasic)

fit.week_snralpha_phasic <- lmer(exponent_30_45_prepost_diff_z
 ~ snr_alpha_between_phasic_z + snr_alpha_between_phasic_baseline_z + exponent_30_45_prepost_diff_baseline_z + swa_between_phasic_z + swa_between_phasic_baseline_z + NREM_perc_z + NREM_perc_baseline_z + channel +night + condition:night + scale(tst) + (1|participant), data=df_week)
phasic_snralpha_summary <- as.data.frame(coef(summary(fit.week_snralpha_phasic))) 
phasic_snralpha_summary <- phasic_snralpha_summary[2,]
r.squaredGLMM(fit.week_snralpha_phasic)

fit.week_denalpha_phasic <- lmer(exponent_30_45_prepost_diff_z
 ~ den_alpha_between_phasic_z + den_alpha_between_phasic_baseline_z + exponent_30_45_prepost_diff_baseline_z + swa_between_phasic_z + swa_between_phasic_baseline_z + NREM_perc_z + NREM_perc_baseline_z + channel +night + condition:night + scale(tst) + (1|participant), data=df_week)
phasic_denalpha_summary <- as.data.frame(coef(summary(fit.week_denalpha_phasic))) 
phasic_denalpha_summary <- phasic_denalpha_summary[2,]
r.squaredGLMM(fit.week_denalpha_phasic)

## tonic----
fit.week_exp30to45_tonic <- lmer(exponent_30_45_prepost_diff_z
 ~ exponent_30_45_between_tonic_z + exponent_30_45_between_tonic_baseline_z + exponent_30_45_prepost_diff_baseline_z + channel +night + condition:night + swa_between_tonic_z + swa_between_tonic_baseline_z + NREM_perc_z + NREM_perc_baseline_z +scale(tst) + (1|participant), data=df_week)
tonicslope_summary <- as.data.frame(coef(summary(fit.week_exp30to45_tonic))) 
tonicslope_summary <- tonicslope_summary[2,]
r.squaredGLMM(fit.week_exp30to45_tonic)

fit.week_IAPF_tonic <- lmer(exponent_30_45_prepost_diff_z
 ~ IAPF_between_tonic_z + IAPF_between_tonic_baseline_z + exponent_30_45_prepost_diff_baseline_z + swa_between_tonic_z + swa_between_tonic_baseline_z + NREM_perc_z + NREM_perc_baseline_z + channel +night + condition:night + scale(tst) + (1|participant), data=df_week)
tonic_IAPF_summary <- as.data.frame(coef(summary(fit.week_IAPF_tonic))) 
tonic_IAPF_summary <- tonic_IAPF_summary[2,]
r.squaredGLMM(fit.week_IAPF_tonic)

fit.week_dentheta_tonic <- lmer(exponent_30_45_prepost_diff_z
 ~ den_theta_between_tonic_z + den_theta_between_tonic_baseline_z + exponent_30_45_prepost_diff_baseline_z + swa_between_tonic_z + swa_between_tonic_baseline_z + NREM_perc_z + NREM_perc_baseline_z  +channel +night + condition:night + scale(tst) + (1|participant), data=df_week)
tonic_dentheta_summary <- as.data.frame(coef(summary(fit.week_dentheta_tonic))) 
tonic_dentheta_summary <- tonic_dentheta_summary[2,]
r.squaredGLMM(fit.week_dentheta_tonic)

fit.week_snralpha_tonic <- lmer(exponent_30_45_prepost_diff_z
 ~ snr_alpha_between_tonic_z + snr_alpha_between_tonic_baseline_z + exponent_30_45_prepost_diff_baseline_z + swa_between_tonic_z + swa_between_tonic_baseline_z + NREM_perc_z + NREM_perc_baseline_z   + channel +night + condition:night + scale(tst) + (1|participant), data=df_week)
tonic_snralpha_summary <- as.data.frame(coef(summary(fit.week_snralpha_tonic))) 
tonic_snralpha_summary <- tonic_snralpha_summary[2,]
r.squaredGLMM(fit.week_snralpha_tonic)

fit.week_denalpha_tonic <- lmer(exponent_30_45_prepost_diff_z
 ~ den_alpha_between_tonic_z + den_alpha_between_tonic_baseline_z + exponent_30_45_prepost_diff_baseline_z +swa_between_phasic_z + swa_between_phasic_baseline_z + NREM_perc_z + NREM_perc_baseline_z + channel +night + condition:night + scale(tst) + (1|participant), data=df_week)
tonic_denalpha_summary <- as.data.frame(coef(summary(fit.week_denalpha_tonic))) 
tonic_denalpha_summary <- tonic_denalpha_summary[2,]
r.squaredGLMM(fit.week_denalpha_tonic)

##

results_adj <- rbind(phasicslope_summary, phasic_dentheta_summary, phasic_snralpha_summary, phasic_denalpha_summary,phasic_IAPF_summary, tonicslope_summary, tonic_dentheta_summary, tonic_snralpha_summary, tonic_denalpha_summary,tonic_IAPF_summary) 
colnames(results_adj)[5] <- "pvalue"
results_adj <- results_adj %>%
  mutate(adj_pvalue = p.adjust(pvalue, method = "fdr"))
results_adj
```
#13 Plot table corr
```{r}
results_adj$sig <- ifelse(
  results_adj$adj_pvalue < 0.001, "***", 
  ifelse(results_adj$adj_pvalue < 0.01, "**",
    ifelse(results_adj$adj_pvalue < 0.05, "*", NA)))
results_adj <- results_adj %>% 
  rownames_to_column("row_names") #%>% 
results_adj$row_names <- gsub("scale\\(([^)]+)\\)", "\\1",  results_adj$row_names)


my_order <- c("IAPF_between_phasic_z", "IAPF_between_tonic_z", "den_alpha_between_phasic_z","den_alpha_between_tonic_z",  "snr_alpha_between_phasic_z", "snr_alpha_between_tonic_z",  "den_theta_between_phasic_z",  "den_theta_between_tonic_z", "exponent_30_45_between_phasic_z","exponent_30_45_between_tonic_z")


results_adj <- results_adj %>% 
  mutate(row_names = factor(row_names, levels=my_order)) %>% 
  arrange(row_names) %>% 
  mutate(across(2:6, as.numeric)) %>%  
  mutate(y = 0) 

corr_plot <- ggplot(results_adj, aes(x = row_names, y=1, fill = Estimate)) +
   geom_tile(data = results_adj %>%
             filter(is.na(sig)), #for non sig estimates =grey
            colour = "black",
            fill   = "grey85") +
  geom_tile(data = results_adj %>%
             filter(!is.na(sig)),
            aes(fill = Estimate),
            colour = "black") + # coloured for sig estimates 
 scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0) +
  coord_fixed() +
  geom_text(aes(label = ifelse(
    !is.na(sig),
    paste(round(Estimate, 2), sig, sep = "\n"),  
    as.character(round(Estimate, 2)))),
  size = 3) +
  theme_prism(base_size = 12, base_fontface="plain", base_line_size=0.2) +
  scale_x_discrete(limits = my_order, labels=c('phasic\nalpha\npeak\nfrequency','tonic\nalpha\npeak\nfrequency', 'phasic\nalpha\ndensity', 'tonic\nalpha\ndensity', 'phasic\nalpha\namplitude', 'tonic\nalpha\namplitude', 'phasic\ntheta\ndensity','tonic\ntheta\ndensity','phasic\nslope\n30-45Hz','tonic\nslope\n30-45Hz'))
#ggsave("figure/figS9/weektripletallplot_corr.svg", plot=corr_plot, width=13, height=3)

```
#14 Plot phasic
```{r}
# Plot (loop) ----
plot_partial_resid <- function(fit, predictor, xlab, x_limits = c(-2, 5), x_breaks = seq(-2, 5, 1)) {
  ordinary_residuals <- residuals(fit)
  coeff_of_interest <- as.numeric(fixef(fit)[predictor])
  predictor_values <- as.numeric(model.frame(fit)[[predictor]])
  partial_residuals_calculated <- ordinary_residuals + coeff_of_interest * predictor_values

  df_points_for_plot <- data.frame(
    x_variable = predictor_values,
    y_partial_residual = partial_residuals_calculated
  )

  eff <- effect(predictor, fit, partial.residuals = TRUE)
  df_line <- as.data.frame(eff)
  
  
  palette_cols <- c("#0072B2", "#008bd9", "#01a4ff","#29b2ff", "#50c0ff", "#8bd5ff")
df_points_for_plot$rand_col <- sample(
  palette_cols,
  nrow(df_points_for_plot),
  replace = TRUE
)

  ggplot(data = df_points_for_plot,
         aes(x = x_variable, y = y_partial_residual)) +
     geom_point(aes(color = rand_col), size = 0.5 * 2, shape=1, stroke=0.35) +
     scale_color_identity() +
    geom_line(data = df_line,
              aes_string(x = predictor, y = "fit"),
              color = "black", linewidth = 1) +
    geom_ribbon(data = df_line,
                aes_string(x = predictor, y = "fit",
                           ymin = "lower", ymax = "upper"),
                fill = "grey", alpha = 0.3) +
    labs(
      x = xlab,
      y = expression("NREM spectral slope change\nNREM post - NREM pre (z-score)"),
      title = ""
    ) +
    scale_x_continuous(limits = x_limits,
                       breaks = x_breaks,
                       expand = c(0, NA)) +
    scale_y_continuous(limits = c(-5, 5),
                       breaks = seq(-5, 5, 1),
                       expand = c(0, NA)) +
    theme_prism(base_size = 10, base_fontface = "plain",
                base_line_size = 0.2) +
    theme(
      legend.position = "none",
      plot.margin = margin(10, 10, 18, 18),
      axis.title.x = element_text(margin = margin(t = 10))
    )
}

# phasic ---- 
plot_phasicslope <- plot_partial_resid(
  fit       = fit.week_exp30to45_phasic,
  predictor = "exponent_30_45_between_phasic_z",
  xlab      = "phasic spectral slope 30 - 45 Hz (z-score)",
  x_limits  = c(-5, 4),
  x_breaks  = seq(-5, 4, 1)
)

plot_phasicthetadensity <- plot_partial_resid(
  fit       = fit.week_dentheta_phasic,
  predictor = "den_theta_between_phasic_z",
  xlab      = "phasic theta density (z-score)",
  x_limits  = c(-3, 5),
  x_breaks  = seq(-3, 5, 1)
)

plot_phasicalphasnr <- plot_partial_resid(
  fit       = fit.week_snralpha_phasic,
  predictor = "snr_alpha_between_phasic_z",
  xlab      = "phasic alpha amplitude (log, z-score)",
  x_limits  = c(-2.5, 8.5),
  x_breaks  = seq(-2.5, 8.5, 1)
)

plot_phasicalphadensity <- plot_partial_resid(
  fit       = fit.week_denalpha_phasic,
  predictor = "den_alpha_between_phasic_z",
  xlab      = "phasic alpha density (z-score)",
  x_limits  = c(-3, 6),
  x_breaks  = seq(-3, 6, 1)
)

plot_phasicIAPF <- plot_partial_resid(
  fit       = fit.week_IAPF_phasic,
  predictor = "IAPF_between_phasic_z",
  xlab      = "phasic alpha peak frequency (z-score)",
  x_limits  = c(-3, 6),
  x_breaks  = seq(-3, 5, 1)
)

ggsave("figure/figS9/phasicslope_corr.svg", plot=plot_phasicslope, width=4, height=4)
ggsave("figure/figS9/phasicthetadensity_corr.svg", plot=plot_phasicthetadensity, width=4, height=4)
ggsave("figure/figS9/phasicalphasnr_corr.svg", plot=plot_phasicalphasnr, width=4, height=4)
ggsave("figure/figS9/phasicalphadensity_corr.svg", plot=plot_phasicalphadensity, width=4, height=4)
ggsave("figure/figS9/plot_phasicIAPF.svg", plot=plot_phasicIAPF, width=4, height=4)

```
#15 Plot tonic
```{r}
# Plot (loop) ----
plot_partial_resid <- function(fit, predictor, xlab, x_limits = c(-2, 5), x_breaks = seq(-2, 5, 1)) {
  ordinary_residuals <- residuals(fit)
  coeff_of_interest <- as.numeric(fixef(fit)[predictor])
  predictor_values <- as.numeric(model.frame(fit)[[predictor]])
  partial_residuals_calculated <- ordinary_residuals + coeff_of_interest * predictor_values

  df_points_for_plot <- data.frame(
    x_variable = predictor_values,
    y_partial_residual = partial_residuals_calculated
  )

  eff <- effect(predictor, fit, partial.residuals = TRUE)
  df_line <- as.data.frame(eff)
  
    palette_cols <- c("#FF7a11", "#FF9038", "#FFa65F",
                  "#FFbc87", "#FFa65F", "#FF9038")
df_points_for_plot$rand_col <- sample(
  palette_cols,
  nrow(df_points_for_plot),
  replace = TRUE
)

  ggplot(data = df_points_for_plot,
         aes(x = x_variable, y = y_partial_residual)) +
     geom_point(aes(color = rand_col), size = 0.5 * 2, shape=1, stroke=0.35) +
     scale_color_identity() +
    geom_line(data = df_line,
              aes_string(x = predictor, y = "fit"),
              color = "black", linewidth = 1) +
    geom_ribbon(data = df_line,
                aes_string(x = predictor, y = "fit",
                           ymin = "lower", ymax = "upper"),
                fill = "grey", alpha = 0.3) +
    labs(
      x = xlab,
      y = expression("NREM spectral slope change\nlast~NREM-first~NREM (z-score)"),
      title = ""
    ) +
    scale_x_continuous(limits = x_limits,
                       breaks = x_breaks,
                       expand = c(0, NA)) +
    scale_y_continuous(limits = c(-5,5),
                       breaks = seq(-5, 5, 1),
                       expand = c(0, NA)) +
    theme_prism(base_size = 10, base_fontface = "plain",
                base_line_size = 0.2) +
    theme(
      legend.position = "none",
      plot.margin = margin(10, 10, 18, 18),
      axis.title.x = element_text(margin = margin(t = 10))
    )
}

# tonic ---- 
plot_tonicslope <- plot_partial_resid(
  fit       = fit.week_exp30to45_tonic,
  predictor = "exponent_30_45_between_tonic_z",
  xlab      = "tonic spectral slope 30 - 45 Hz (z-score)",
  x_limits  = c(-5, 4),
  x_breaks  = seq(-5, 4, 1)
)

plot_tonicthetadensity <- plot_partial_resid(
  fit       = fit.week_dentheta_tonic,
  predictor = "den_theta_between_tonic_z",
  xlab      = "tonic theta density (z-score)",
  x_limits  = c(-3, 5),
  x_breaks  = seq(-3, 5, 1)
)

plot_tonicalphasnr <- plot_partial_resid(
  fit       = fit.week_snralpha_tonic,
  predictor = "snr_alpha_between_tonic_z",
  xlab      = "tonic alpha (log, z-score)",
  x_limits  = c(-2.5, 8.5),
  x_breaks  = seq(-2.5, 8.5, 1)
)

plot_tonicalphadensity <- plot_partial_resid(
  fit       = fit.week_denalpha_tonic,
  predictor = "den_alpha_between_tonic_z",
  xlab      = "tonic alpha density (z-score)",
  x_limits  = c(-3, 6),
  x_breaks  = seq(-3, 6, 1)
)

plot_tonicIAPF <- plot_partial_resid(
  fit       = fit.week_IAPF_tonic,
  predictor = "IAPF_between_tonic_z",
  xlab      = "tonic alpha peak frequency (z-score)",
  x_limits  = c(-3, 5),
  x_breaks  = seq(-3, 5, 1)
)

ggsave("figure/figS9/tonicslope_corr.svg", plot=plot_tonicslope, width=4, height=4)
ggsave("figure/figS9/tonicthetadensity_corr.svg", plot=plot_tonicthetadensity, width=4, height=4)
ggsave("figure/figS9/tonicalphasnr_corr.svg", plot=plot_tonicalphasnr, width=4, height=4)
ggsave("figure/figS9/tonicalphadensity_corr.svg", plot=plot_tonicalphadensity, width=4, height=4)
ggsave("figure/figS9/tonicIAPF_corr.svg", plot=plot_tonicIAPF, width=4, height=4)


```
#Supplementary Associations and plots unified model phasic vs tonic stats (Fig S9k-s)
```{r}
fit.week_exp30to45<- lmer(exponent_30_45_prepost_diff_z
 ~ exponent_30_45_between_phasic_z + exponent_30_45_between_tonic_z + exponent_30_45_between_phasic_baseline_z + exponent_30_45_between_tonic_baseline_z + exponent_30_45_prepost_diff_baseline_z + order + channel +night + condition:night + swa_between_phasic_z + swa_between_tonic_z + swa_between_phasic_baseline_z + swa_between_tonic_baseline_z + scale(tst) + (1|participant), data=df_week)

fit.week_dentheta <- lmer(exponent_30_45_prepost_diff_z
 ~ den_theta_between_phasic_z + den_theta_between_tonic_z + den_theta_between_phasic_baseline_z +  den_theta_between_tonic_baseline_z + exponent_30_45_prepost_diff_baseline_z + order +channel +night + condition:night + swa_between_phasic_z + swa_between_tonic_z + swa_between_phasic_baseline_z + swa_between_tonic_baseline_z +  NREM_perc_z + NREM_perc_baseline_z + scale(tst) + (1|participant), data=df_week)

fit.week_snralpha <- lmer(exponent_30_45_prepost_diff_z
 ~ snr_alpha_between_phasic_z + snr_alpha_between_tonic_z + snr_alpha_between_phasic_baseline_z +  snr_alpha_between_tonic_baseline_z + exponent_30_45_prepost_diff_baseline_z + order +channel +night + condition:night + swa_between_phasic_z + swa_between_tonic_z + swa_between_phasic_baseline_z + swa_between_tonic_baseline_z + NREM_perc_z + NREM_perc_baseline_z +  scale(tst) + (1|participant), data=df_week)

fit.week_denalpha <- lmer(exponent_30_45_prepost_diff_z
 ~ den_alpha_between_phasic_z + den_alpha_between_tonic_z + den_alpha_between_phasic_baseline_z +  den_alpha_between_tonic_baseline_z  + exponent_30_45_prepost_diff_baseline_z + order +channel +night + condition:night + swa_between_phasic_z + swa_between_tonic_z + swa_between_phasic_baseline_z + swa_between_tonic_baseline_z + NREM_perc_z + NREM_perc_baseline_z +  scale(tst) + (1|participant), data=df_week)

fit.week_IAPF<- lmer(exponent_30_45_prepost_diff_z
 ~ IAPF_between_phasic_z + IAPF_between_tonic_z + IAPF_between_phasic_baseline_z +  IAPF_between_tonic_baseline_z + exponent_30_45_prepost_diff_baseline_z + order +channel +night + condition:night + swa_between_phasic_z + swa_between_tonic_z + swa_between_phasic_baseline_z + swa_between_tonic_baseline_z + NREM_perc_z + NREM_perc_baseline_z +  scale(tst) + (1|participant), data=df_week)

##
# run glht for phasic vs tonic coeff comparision ----
library (modelbased)
run_glht <- function(model, contrasts) {
   comp <- glht(model, linfct = contrasts)
   s    <- summary(comp)
   
    tab <- data.frame(
    estimate   = s$test$coefficients,
    SE         = s$test$sigma,
    z          = s$test$tstat,
    p          = s$test$pvalues
  )
  
}

# IAPF
glht_IAPF <- run_glht(
  model     = fit.week_IAPF,
  contrasts = "IAPF_between_phasic_z - IAPF_between_tonic_z = 0"
)

# density alpha
glht_densityalpha <- run_glht(
  model     = fit.week_denalpha,
  contrasts = "den_alpha_between_phasic_z - den_alpha_between_tonic_z = 0"
)

# snr alpha
glht_snralpha <- run_glht(
  model     = fit.week_snralpha,
  contrasts = "snr_alpha_between_phasic_z - snr_alpha_between_tonic_z = 0"
)

# density theta
glht_densitytheta <- run_glht(
  model     = fit.week_dentheta,
  contrasts = "den_theta_between_phasic_z - den_theta_between_tonic_z = 0"
)

# exp30-45Hz
glht_exp30to45 <- run_glht(
  model     = fit.week_exp30to45,
  contrasts = "exponent_30_45_between_phasic_z - exponent_30_45_between_tonic_z =0"
)

final_glht_weektable <- rbind(
  glht_IAPF,
  glht_densityalpha,
  glht_snralpha,
  glht_densitytheta,
  glht_exp30to45
) %>% mutate(adj_pvalue = p.adjust(p, method="fdr")) 

# Row counts for pack_rows
n_IAPF         <- nrow(glht_IAPF)
n_densityalpha <- nrow(glht_densityalpha)
n_snralpha     <- nrow(glht_snralpha)
n_densitytheta <- nrow(glht_densitytheta)
n_exp30to45    <- nrow(glht_exp30to45)

# Create kable
final_glht_weektable %>%
  kable(format  = "html",
        digits  = 4,
        caption = "Phasic vs Tonic Coefficient Comparison — Week") %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  pack_rows("IAPF", 
            1, 
            n_IAPF) %>%
  pack_rows("Alpha Density", 
            n_IAPF + 1, 
            n_IAPF + n_densityalpha) %>%
  pack_rows("Alpha SNR", 
            n_IAPF + n_densityalpha + 1, 
            n_IAPF + n_densityalpha + n_snralpha) %>%
  pack_rows("Theta Density", 
            n_IAPF + n_densityalpha + n_snralpha + 1, 
            n_IAPF + n_densityalpha + n_snralpha + n_densitytheta) %>%
  pack_rows("Spectral Exponent 30-45Hz", 
            n_IAPF + n_densityalpha + n_snralpha + n_densitytheta + 1, 
            n_IAPF + n_densityalpha + n_snralpha + n_densitytheta + n_exp30to45)


```

