---
title: "PANAS stats"
output: html_notebook
---

# import functions
```{r}
library(lmerTest)
library(emmeans)
library(lme4)
library(tidyverse)
library(broom)
library(ggpubr)
library(ggprism)
library(nplyr)
library(effects)
library(corrplot)
library(ppcor)
library(ordinal)
library(dplyr)
library(MuMIn)
```
#Load data
```{r}
df <- read_csv("data/for paper/PANAS/df_PANAS.csv", show_col_types = FALSE)

cols <- c("participant", "gender", "condition", "test_no", "day", "order", "PANAS", "channel")
df <- df %>% mutate_at(cols, factor) 
```
## Changes in PANAS scores (z scored and ranked to achieve normal distribution) over the week (Fig 4)
```{r}
df_PANAS <- df %>% 
  group_by(PANAS) %>% 
  nest() 

PANAS_negative <- pluck(df_PANAS$data[[1]])
PANAS_positive <- pluck(df_PANAS$data[[2]])
```
# 1. lme 
```{r}
# Run lmer ----
fit.PANAS_negative <- lmer(PANAS_score_z ~ condition:day + day + test_no + order + PANAS_score_z_baseline + (1|participant), data = PANAS_negative)
stats_PANAS_negative <- anova(fit.PANAS_negative)

fit.PANAS_positive <- lmer(PANAS_score_z ~ condition:day + day + test_no + order + PANAS_score_z_baseline + (1|participant), data = PANAS_positive)
stats_PANAS_positive <- anova(fit.PANAS_positive)

# estimated means
PANASneg_esmmeans <- estimate_means(fit.PANAS_negative , by = c("day", "condition"))
PANASpos_esmmeans <- estimate_means(fit.PANAS_positive , by= c("day", "condition" ))
```
#2. posthoc
```{r}
# comparing between conditions for each day (in paper)
pairs(emmeans(fit.PANAS_positive, ~day:condition, by="day", p.adjust = "tukey"))
# comparing to baseline 
contrast((emmeans(fit.PANAS_positive, ~ day:condition)), method = "trt.vs.ctrl", ref = 2, adjust = "tukey")

pairs(emmeans(fit.PANAS_negative, ~day:condition, by="day", p.adjust = "tukey"))
contrast((emmeans(fit.PANAS_negative, ~ day:condition)), method = "trt.vs.ctrl", ref = 2, adjust = "tukey")
```
#3. plot
```{r}
PANASneg_esmmeans$PANAS <- rep("NEGATIVE", 14)
PANASpos_esmmeans$PANAS <- rep("POSITIVE", 14)
PANAS_esmmeans <- rbind(PANASpos_esmmeans, PANASneg_esmmeans)

PANAS_esmmeans <- PANAS_esmmeans %>%
  mutate(PANAS = fct_relevel(PANAS, 
           "POSITIVE", "NEGATIVE"))

PANAS_score <- ggplot(PANAS_esmmeans, aes(x = day, y = Mean, linetype=condition, shape=condition, group=condition)) + 
    facet_wrap(~PANAS, labeller = as_labeller(c(
    "POSITIVE" = "General Positive Affect",
    "NEGATIVE" = "General Negative Affect"))) + 
   scale_shape_manual(values = c(16,21)) +
   geom_line(linewidth=0.3, position =position_dodge(0.3)) +
    geom_errorbar(aes(x=day, y=Mean, ymin=Mean-SE, ymax=Mean+SE), linetype=1, width=0.2, position = position_dodge(0.2), lwd=0.5) +
   geom_point(aes(shape=condition),fill="white", size=2, position = position_dodge(0.3)) +
  theme_prism(base_size = 8, base_fontface="plain", base_line_size=0.2) +
  xlab("day") + ylab("z-score normalised mean") +
  scale_y_continuous(limits = c(-0.4, 0.4), breaks = seq(-0.4, 0.4, 0.1), expand = c(0, NA))+
  theme(legend.position="right") +
   scale_x_discrete(labels=c("B", "1", "2", "3", "4", "5", "6")) 

```


## Baseline: associations with all periodic and aperiodic components (Table S2)
#1. lmes 
#NB run #1 PANAS_positive followed by #2 positive table, then repeat this section and the next with PANAS_negative
```{r}
df_baseline <- 
  #PANAS_positive %>% # choose POS or NEG
 PANAS_negative %>%
  dplyr::filter(day=="2")  #baseline

# duration
fit.duration_phasic <- lmer(PANAS_score_z ~   test_no  + order + scale(phasic_perc) + (1|participant), data=df_baseline)
fit.duration_phasic_summary <- as.data.frame(coef(summary(fit.duration_phasic))) 
phasic_coeff <- fit.duration_phasic_summary[7,] 
phasic_confint <- as.data.frame(t(confint(fit.duration_phasic)[9,]))
phasic_coeff <- cbind(phasic_coeff,phasic_confint)

fit.duration_tonic <- lmer(PANAS_score_z ~   test_no  + order + scale(tonic_perc) + (1|participant), data=df_baseline)
fit.duration_tonic_summary <- as.data.frame(coef(summary(fit.duration_tonic))) 
tonic_coeff <- fit.duration_tonic_summary[7,] 
tonic_confint <- as.data.frame(t(confint(fit.duration_tonic)[9,]))
tonic_coeff <- cbind(tonic_coeff,tonic_confint)

fit.duration_NREM <- lmer(PANAS_score_z ~   test_no  + order + scale(NREM_perc) + (1|participant), data=df_baseline)
fit.duration_NREM_summary <- as.data.frame(coef(summary(fit.duration_NREM))) 
NREM_coeff <- fit.duration_NREM_summary[7,] 
NREM_confint <- as.data.frame(t(confint(fit.duration_NREM)[9,]))
NREM_coeff <- cbind(NREM_coeff,NREM_confint)

fit.duration_REM <- lmer(PANAS_score_z ~   test_no  + order + scale(REM_perc) + (1|participant), data=df_baseline)
fit.duration_REM_summary <- as.data.frame(coef(summary(fit.duration_REM))) 
REM_coeff <- fit.duration_REM_summary[7,] 
REM_confint <- as.data.frame(t(confint(fit.duration_REM)[9,]))
REM_coeff <- cbind(REM_coeff,REM_confint)

# oscillations ----
#phasic ----
fit.IAPF_phasic <- lmer(PANAS_score_z ~  test_no + scale(tst) + order + channel + scale(IAPF_phasic) + (1|participant), data=df_baseline)
fit.IAPF_phasic_summary <- as.data.frame(coef(summary(fit.IAPF_phasic))) 
IAPF_phasic_coeff <- fit.IAPF_phasic_summary[11,]
IAPF_phasic_confint <- as.data.frame(t(confint(fit.IAPF_phasic)[13,]))
IAPF_phasic_coeff <- cbind(IAPF_phasic_coeff,IAPF_phasic_confint)

fit.densityalpha_phasic  <- lmer(PANAS_score_z ~  test_no + scale(tst) + order + channel + scale(densityalpha_phasic) +  (1|participant), data=df_baseline)
fit.densityalpha_phasic_summary <- as.data.frame(coef(summary(fit.densityalpha_phasic))) 
densityalpha_phasic_coeff <- fit.densityalpha_phasic_summary[11,]
densityalpha_phasic_confint <- as.data.frame(t(confint(fit.densityalpha_phasic)[13,]))
densityalpha_phasic_coeff <- cbind(densityalpha_phasic_coeff,densityalpha_phasic_confint)

fit.snralpha_phasic <- lmer(PANAS_score_z ~  test_no + scale(tst) + order + channel + scale(snralpha_phasic)  + (1|participant), data=df_baseline)
fit.snralpha_phasic_summary <- as.data.frame(coef(summary(fit.snralpha_phasic))) 
snralpha_phasic_coeff <- fit.snralpha_phasic_summary[11,]
snralpha_phasic_confint <- as.data.frame(t(confint(fit.snralpha_phasic)[13,]))
snralpha_phasic_coeff <- cbind(snralpha_phasic_coeff,snralpha_phasic_confint)

fit.densitytheta_phasic <- lmer(PANAS_score_z ~   test_no + scale(tst) + order + channel + scale(densitytheta_phasic) +  (1|participant), data=df_baseline)
fit.densitytheta_phasic_summary <- as.data.frame(coef(summary(fit.densitytheta_phasic))) 
densitytheta_phasic_coeff <- fit.densitytheta_phasic_summary[11,]
densitytheta_phasic_confint <- as.data.frame(t(confint(fit.densitytheta_phasic)[13,]))
densitytheta_phasic_coeff <- cbind(densitytheta_phasic_coeff,densitytheta_phasic_confint)

fit.snrtheta_phasic <- lmer(PANAS_score_z ~ test_no + scale(tst) + order + channel + scale(snrtheta_phasic) + (1|participant), data=df_baseline)
fit.snrtheta_phasic_summary <- as.data.frame(coef(summary(fit.snrtheta_phasic))) 
snrtheta_phasic_coeff <- fit.snrtheta_phasic_summary[11,]
snrtheta_phasic_confint <- as.data.frame(t(confint(fit.snrtheta_phasic)[13,]))
snrtheta_phasic_coeff <- cbind(snrtheta_phasic_coeff,snrtheta_phasic_confint)

#tonic ----
fit.IAPF_tonic <- lmer(PANAS_score_z ~  test_no + scale(tst) + order + channel + scale(IAPF_tonic) + (1|participant), data=df_baseline)
fit.IAPF_tonic_summary <- as.data.frame(coef(summary(fit.IAPF_tonic))) 
IAPF_tonic_coeff <- fit.IAPF_tonic_summary[11,]
IAPF_tonic_confint <- as.data.frame(t(confint(fit.IAPF_tonic)[13,]))
IAPF_tonic_coeff <- cbind(IAPF_tonic_coeff,IAPF_tonic_confint)

fit.densityalpha_tonic  <- lmer(PANAS_score_z ~  test_no + scale(tst) + order + channel + scale(densityalpha_tonic) +  (1|participant), data=df_baseline)
fit.densityalpha_tonic_summary <- as.data.frame(coef(summary(fit.densityalpha_tonic))) 
densityalpha_tonic_coeff <- fit.densityalpha_tonic_summary[11,]
densityalpha_tonic_confint <- as.data.frame(t(confint(fit.densityalpha_tonic)[13,]))
densityalpha_tonic_coeff <- cbind(densityalpha_tonic_coeff,densityalpha_tonic_confint)

fit.snralpha_tonic <- lmer(PANAS_score_z ~  test_no + scale(tst) + order + channel + scale(snralpha_tonic)  + (1|participant), data=df_baseline)
fit.snralpha_tonic_summary <- as.data.frame(coef(summary(fit.snralpha_tonic))) 
snralpha_tonic_coeff <- fit.snralpha_tonic_summary[11,]
snralpha_tonic_confint <- as.data.frame(t(confint(fit.snralpha_tonic)[13,]))
snralpha_tonic_coeff <- cbind(snralpha_tonic_coeff,snralpha_tonic_confint)

fit.densitytheta_tonic <- lmer(PANAS_score_z ~   test_no + scale(tst) + order + channel + scale(densitytheta_tonic) +  (1|participant), data=df_baseline)
fit.densitytheta_tonic_summary <- as.data.frame(coef(summary(fit.densitytheta_tonic))) 
densitytheta_tonic_coeff <- fit.densitytheta_tonic_summary[11,]
densitytheta_tonic_confint <- as.data.frame(t(confint(fit.densitytheta_tonic)[13,]))
densitytheta_tonic_coeff <- cbind(densitytheta_tonic_coeff,densitytheta_tonic_confint)

fit.snrtheta_tonic <- lmer(PANAS_score_z ~ test_no + scale(tst) + order + channel + scale(snrtheta_tonic) + (1|participant), data=df_baseline)
fit.snrtheta_tonic_summary <- as.data.frame(coef(summary(fit.snrtheta_tonic))) 
snrtheta_tonic_coeff <- fit.snrtheta_tonic_summary[11,]
snrtheta_tonic_confint <- as.data.frame(t(confint(fit.snrtheta_tonic)[13,]))
snrtheta_tonic_coeff <- cbind(snrtheta_tonic_coeff,snrtheta_tonic_confint)

# aperiodic ----
#phasic
fit.exp30to45_phasic <- lmer(PANAS_score_z ~  test_no + scale(tst) + order + channel + scale(exp30to45_phasic) + (1|participant), data=df_baseline)
fit.exp30to45_phasic_summary <- as.data.frame(coef(summary(fit.exp30to45_phasic))) 
exp30to45_phasic_coeff <- fit.exp30to45_phasic_summary[11,]
exp30to45_phasic_confint <- as.data.frame(t(confint(fit.exp30to45_phasic)[13,]))
exp30to45_phasic_coeff <- cbind(exp30to45_phasic_coeff,exp30to45_phasic_confint)

# tonic
fit.exp30to45_tonic <- lmer(PANAS_score_z ~  test_no + scale(tst) + order + channel + scale(exp30to45_tonic) + (1|participant), data=df_baseline)
fit.exp30to45_tonic_summary <- as.data.frame(coef(summary(fit.exp30to45_tonic))) 
exp30to45_tonic_coeff <- fit.exp30to45_tonic_summary[11,]
exp30to45_tonic_confint <- as.data.frame(t(confint(fit.exp30to45_tonic)[13,]))
exp30to45_tonic_coeff <- cbind(exp30to45_tonic_coeff,exp30to45_tonic_confint)
```
#2. combine all results 
```{r}
# PANAS POSITIVE ----
results_base_pos <- rbind(phasic_coeff, tonic_coeff, REM_coeff, NREM_coeff, IAPF_phasic_coeff, densityalpha_phasic_coeff, densitytheta_phasic_coeff, snralpha_phasic_coeff, snrtheta_phasic_coeff,IAPF_tonic_coeff, densityalpha_tonic_coeff, densitytheta_tonic_coeff, snralpha_tonic_coeff, snrtheta_tonic_coeff,exp30to45_phasic_coeff,exp30to45_tonic_coeff) 
colnames(results_base_pos)[5] <- "pvalue"
colnames(results_base_pos)[6] <- "confint_start"
colnames(results_base_pos)[7] <- "confint_end"

results_base_pos <- results_base_pos %>% 
   mutate(across(1:7, as.numeric)) %>% 
  mutate(across(where(is.numeric), ~ format(round(.x, 4), nsmall = 4)))
results_base_pos$confint <- paste(results_base_pos$confint_start, results_base_pos$confint_end, sep=",")

results_base_pos <- results_base_pos %>% 
  rownames_to_column("row_names") 
 results_base_pos$row_names <- gsub("scale\\(([^)]+)\\)", "\\1",  results_base_pos$row_names)
 
results_base_pos$PANAS <- rep("General Positive Affect", 16)

# PANAS NEGATIVE ----
results_base_neg <- rbind(phasic_coeff, tonic_coeff, REM_coeff, NREM_coeff, IAPF_phasic_coeff, densityalpha_phasic_coeff, densitytheta_phasic_coeff, snralpha_phasic_coeff, snrtheta_phasic_coeff,IAPF_tonic_coeff, densityalpha_tonic_coeff, densitytheta_tonic_coeff, snralpha_tonic_coeff, snrtheta_tonic_coeff,exp30to45_phasic_coeff,exp30to45_tonic_coeff) 
colnames(results_base_neg)[5] <- "pvalue"
colnames(results_base_neg)[6] <- "confint_start"
colnames(results_base_neg)[7] <- "confint_end"

results_base_neg <- results_base_neg %>% 
   mutate(across(1:7, as.numeric)) %>% 
  mutate(across(where(is.numeric), ~ format(round(.x, 4), nsmall = 4)))
results_base_neg$confint <- paste(results_base_neg$confint_start, results_base_neg$confint_end, sep=",")

results_base_neg <- results_base_neg %>% 
  rownames_to_column("row_names") 
results_base_neg$row_names <- gsub("scale\\(([^)]+)\\)", "\\1",  results_base_neg$row_names)

results_base_neg$PANAS <- rep("General Negative Affect", 16) 
```
#3. Produce table
```{r}
my_order <- c("NREM_perc", "REM_perc", "phasic_perc", "tonic_perc", "IAPF_phasic", "densityalpha_phasic", "snralpha_phasic", "densitytheta_phasic", "snrtheta_phasic", "IAPF_tonic", "densityalpha_tonic", "snralpha_tonic", "densitytheta_tonic", "snrtheta_tonic", "exp30to45_phasic", "exp30to45_tonic")

PANAS_baseline_adj <- rbind(results_base_pos, results_base_neg)  %>%
  mutate(adj_pvalue = p.adjust(pvalue, method="fdr"))  %>% #fdr adjust
  relocate(adj_pvalue, .after = pvalue)  %>%
  mutate(across(2:9, as.numeric)) %>% 
  mutate(across(2:9, ~ format(round(.x, 4), nsmall = 4)))  %>%
  mutate(row_names = factor(row_names, levels=my_order)) %>% 
  arrange(row_names)
PANAS_baseline_adj$PANAS <- as.factor(PANAS_baseline_adj$PANAS)

# Generate table 
library(knitr)
library(kableExtra)

positive_table <- PANAS_baseline_adj %>% 
  filter(PANAS == "General Positive Affect") %>% 
  dplyr::select(!c(5,8,9,11)) %>% 
  kable("html", digits=4, caption = "General Positive Affect for baseline") %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) 

negative_table <- PANAS_baseline_adj %>% 
  filter(PANAS == "General Negative Affect")  %>% 
 dplyr:: select(!c(5,8,9,11)) %>% 
  kable("html", digits=4, caption = "General Negative Affect for baseline") %>% 
  kable_styling(bootstrap_options = "striped", full_width = F)
```


## Week:
#Load data (Fig 4)
```{r}
df_PANAS <- read_csv("data/for paper/PANAS/df_PANAS_week.csv", show_col_types = FALSE)

cols <- c("participant", "gender", "condition", "test_no", "day", "order", "PANAS", "channel")
df_PANAS <- df_PANAS %>% mutate_at(cols, factor) 

df_PANAS %>% df_PANAS
  group_by(PANAS) %>% 
  nest() 
  
df_week_neg <- pluck(df_PANAS$data[[1]])
df_week_pos <- pluck(df_PANAS$data[[2]]) 
```
#1. lme: assocaitions between PANAS and periodic/aperiodic components that changed with insufficent sleep 
#NB Run #1. for positive PANAS followed by #2, then repeat #1. for negative PANAS followed by #3. 
```{r}
#df_week <- df_week_pos 
df_week <- df_week_neg

fit.duration_NREM <- lmer(PANAS_score_z ~ scale(NREM_perc) + scale(NREM_perc_baseline) + PANAS_score_z_baseline + condition:night + night+test_no  + order + (1|participant), data=df_week)
fit.duration_NREM_summary <- as.data.frame(coef(summary(fit.duration_NREM))) 

fit.duration_REM <- lmer(PANAS_score_z ~ scale(REM_perc) + scale(REM_perc_baseline) + PANAS_score_z_baseline + condition:night + night+test_no  + order + (1|participant), data=df_week)
fit.duration_REM_summary <- as.data.frame(coef(summary(fit.duration_REM))) 

fit.duration_phasic <- lmer(PANAS_score_z ~ scale(phasic_perc) + scale(phasic_perc_baseline) + PANAS_score_z_baseline + condition:night + night + test_no  + order + (1|participant), data=df_week)
fit.duration_phasic_summary <- as.data.frame(coef(summary(fit.duration_phasic))) 

fit.duration_tonic <- lmer(PANAS_score_z ~ scale(tonic_perc) + scale(tonic_perc_baseline) + PANAS_score_z_baseline + condition:night + night+test_no  + order + (1|participant), data=df_week)
fit.duration_tonic_summary <- as.data.frame(coef(summary(fit.duration_tonic))) 

# oscillations ----
fit.IAPF_phasic <- lmer(PANAS_score_z ~ scale(IAPF_phasic) + scale(IAPF_phasic_baseline) + PANAS_score_z_baseline + condition:night + night + test_no + scale(tst) + channel + order + (1|participant), data=df_week)
fit.IAPF_phasic_summary <- as.data.frame(coef(summary(fit.IAPF_phasic))) 

fit.densityalpha_phasic <- lmer(PANAS_score_z ~ scale(densityalpha_phasic) + scale(densityalpha_phasic_baseline) + PANAS_score_z_baseline + condition:night + night + test_no + scale(tst) + channel + order + (1|participant), data=df_week)
fit.densityalpha_phasic_summary <- as.data.frame(coef(summary(fit.densityalpha_phasic))) 

fit.densitytheta_phasic <- lmer(PANAS_score_z ~ scale(densitytheta_phasic) + scale(densitytheta_phasic_baseline) + PANAS_score_z_baseline + condition:night + night + test_no + scale(tst) + channel + order + (1|participant), data=df_week)
fit.densitytheta_phasic_summary <- as.data.frame(coef(summary(fit.densitytheta_phasic))) 

fit.snralpha_phasic <- lmer(PANAS_score_z ~ scale(snralpha_phasic) + scale(snralpha_phasic_baseline) + PANAS_score_z_baseline + condition:night + night + test_no + scale(tst) + channel + order + (1|participant), data=df_week)
fit.snralpha_phasic_summary <- as.data.frame(coef(summary(fit.snralpha_phasic))) 

fit.snrtheta_phasic <- lmer(PANAS_score_z ~ scale(snrtheta_phasic) + scale(snrtheta_phasic_baseline) + PANAS_score_z_baseline + condition:night + night + test_no + scale(tst) + channel + order + (1|participant), data=df_week)
fit.snrtheta_phasic_summary <- as.data.frame(coef(summary(fit.snrtheta_phasic))) 

fit.IAPF_tonic <- lmer(PANAS_score_z ~ scale(IAPF_tonic) + scale(IAPF_tonic_baseline) + PANAS_score_z_baseline + condition:night + night + test_no + scale(tst) + channel + order + (1|participant), data=df_week)
fit.IAPF_tonic_summary <- as.data.frame(coef(summary(fit.IAPF_tonic))) 

fit.densityalpha_tonic <- lmer(PANAS_score_z ~ scale(densityalpha_tonic) + scale(densityalpha_tonic_baseline) + PANAS_score_z_baseline + condition:night + night + test_no + scale(tst) + channel + order + (1|participant), data=df_week)
fit.densityalpha_tonic_summary <- as.data.frame(coef(summary(fit.densityalpha_tonic))) 

fit.densitytheta_tonic <- lmer(PANAS_score_z ~ scale(densitytheta_tonic) + scale(densitytheta_tonic_baseline) + PANAS_score_z_baseline + condition:night + night + test_no + scale(tst) + channel + order + (1|participant), data=df_week)
fit.densitytheta_tonic_summary <- as.data.frame(coef(summary(fit.densitytheta_tonic))) 
densitytheta_tonic_coeff <- fit.densitytheta_tonic_summary[c(2),]
r.squaredGLMM(fit.densitytheta_tonic)

fit.snralpha_tonic <- lmer(PANAS_score_z ~ scale(snralpha_tonic) + scale(snralpha_tonic_baseline) + PANAS_score_z_baseline + condition:night + night + test_no + scale(tst) + channel + order + (1|participant), data=df_week)
fit.snralpha_tonic_summary <- as.data.frame(coef(summary(fit.snralpha_tonic))) 
snralpha_tonic_coeff <- fit.snralpha_tonic_summary[c(2),]
r.squaredGLMM(fit.snralpha_tonic)

fit.snrtheta_tonic <- lmer(PANAS_score_z ~ scale(snrtheta_tonic) + scale(snrtheta_tonic_baseline) + PANAS_score_z_baseline + condition:night + night + test_no + scale(tst) + channel + order + (1|participant), data=df_week)
fit.snrtheta_tonic_summary <- as.data.frame(coef(summary(fit.snrtheta_tonic))) 

# aperiodic ----
fit.exp30to45_phasic <- lmer(PANAS_score_z ~ scale(exp30to45_phasic) + scale(exp30to45_phasic_baseline) + PANAS_score_z_baseline + condition:night + night + test_no + scale(tst) + channel + order + (1|participant), data=df_week)
fit.exp30to45_phasic_summary <- as.data.frame(coef(summary(fit.exp30to45_phasic))) 
```
#3. Create df for positive PANAS
```{r}
results_week_pos <- rbind(phasic_coeff, tonic_coeff, REM_coeff, NREM_coeff, IAPF_phasic_coeff, densityalpha_phasic_coeff, densitytheta_phasic_coeff, snralpha_phasic_coeff, snrtheta_phasic_coeff,IAPF_tonic_coeff, densityalpha_tonic_coeff, densitytheta_tonic_coeff, snralpha_tonic_coeff, snrtheta_tonic_coeff,exp30to45_phasic_coeff,exp30to45_tonic_coeff) 
colnames(results_week_pos)[5] <- "pvalue"
results_week_pos <- results_week_pos %>%
  mutate(across(where(is.numeric), ~ format(round(.x, 4), nsmall = 4)))

results_week_pos <- results_week_pos %>% 
  rownames_to_column("row_names") #%>% 
results_week_pos$row_names <- gsub("scale\\(([^)]+)\\)", "\\1",  results_week_pos$row_names)

results_week_pos$PANAS <- rep("General Positive Affect", 16)
```
#4. Create df for negative PANAS
```{r}
results_week_neg <- rbind(phasic_coeff, tonic_coeff, REM_coeff, NREM_coeff, IAPF_phasic_coeff, densityalpha_phasic_coeff, densitytheta_phasic_coeff, snralpha_phasic_coeff, snrtheta_phasic_coeff,IAPF_tonic_coeff, densityalpha_tonic_coeff, densitytheta_tonic_coeff, snralpha_tonic_coeff, snrtheta_tonic_coeff,exp30to45_phasic_coeff,exp30to45_tonic_coeff) 
colnames(results_week_neg)[5] <- "pvalue"
results_week_neg <- results_week_neg %>%
  mutate(across(where(is.numeric), ~ format(round(.x, 4), nsmall = 4)))


results_week_neg <- results_week_neg %>% 
  rownames_to_column("row_names") 
results_week_neg$row_names <- gsub("scale\\(([^)]+)\\)", "\\1",  results_week_neg$row_names)


results_week_neg$PANAS <- rep("General Negative Affect", 16)
```
#5. Combine both df into one for plotting
```{r}
PANAS_week_masked <- rbind(results_week_pos, results_week_neg) %>% 
 filter(row_names %in% c("phasic_perc", "tonic_perc", "NREM_perc", "REM_perc",
                          "snralpha_tonic", "snralpha_phasic","densitytheta_tonic", "densitytheta_phasic", "exp30to45_phasic", "exp30to45_tonic", "IAPF_phasic", "IAPF_tonic" ))  %>% 
  mutate(adj_pvalue = p.adjust(pvalue, method="fdr")) %>% 
    mutate(Estimate = ifelse(abs(adj_pvalue) < 0.05, Estimate, NaN)) 

PANAS_week_masked$sig <- ifelse(
  PANAS_week_masked$adj_pvalue < 0.001, "***", 
  ifelse(PANAS_week_masked$adj_pvalue < 0.01, "**",
    ifelse(PANAS_week_masked$adj_pvalue < 0.05, "*", NA)))

my_order <- c( "NREM_perc", "REM_perc", "phasic_perc","tonic_perc", "densitytheta_phasic",  "snralpha_phasic","IAPF_phasic", "densitytheta_tonic","snralpha_tonic", "IAPF_tonic","exp30to45_phasic","exp30to45_tonic")

PANAS_week_masked <- PANAS_week_masked %>% 
  mutate(row_names = factor(row_names, levels=my_order)) %>% 
  arrange(row_names) %>% 
   mutate(PANAS = fct_relevel(PANAS, 
           "General Positive Affect", "General Negative Affect"))

PANAS_week_masked <- PANAS_week_masked %>%   mutate(across(2:6, as.numeric)) %>%  add_column(y = 0) 

week_correlationlmm <- ggplot(PANAS_week_masked, aes(x = row_names, y=1, fill = Estimate)) +
  geom_tile(colour="black") +
 scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0) +
    facet_wrap(~PANAS, nrow=2) +
  coord_fixed() +
  geom_text(data = subset(PANAS_week_masked, !is.na(Estimate) & !is.na(sig)),
          aes(label= paste(round(Estimate, 2), sig, sep ="\n")), size=3) +
  theme_prism(base_size = 12, base_fontface="plain", base_line_size=0.2) +
   scale_x_discrete(labels=c('NREM\npercentage','REM\npercentage','phasic\npercentage','tonic\npercentage','phasic\ntheta\ndensity', 'phasic\nalpha\namplitude', 'phasic\nalpha\npeak\nfrequency', 'tonic\ntheta\ndensity', 'tonic\nalpha\namplitude', 'tonic\nalpha\npeak\nfrequency','phasic\nslope\n30-45Hz','tonic\nslope\n30-45Hz')) 
```

#6. partial regression with residuals for chosen variables 
```{r}
library(effects) # plot partial regression
library(performance) # calc marginal(fixed-effects var) and conditional (fixed + random variance) R2
# Calculate Cohen D = estimate for fixed effect / (sqrt of sum of variances of random effects)

df_week <- df_week_pos 
df_week <- df_week %>% 
  mutate(densitytheta_tonic_z = scale(densitytheta_tonic)) %>% 
  mutate(snralpha_tonic_z = scale(snralpha_tonic))

fit.densitytheta_tonic <- lmer(PANAS_score_z ~ densitytheta_tonic_z + scale(densitytheta_tonic_baseline) + PANAS_score_z_baseline + condition:night + night + test_no + scale(tst) + channel + order + (1|participant), data=df_week)

effects.fitdensitytheta_tonic <- effect("densitytheta_tonic_z", fit.densitytheta_tonic, partial.residuals=T) 
plot(effects.fitdensitytheta_tonic, main = NULL, smooth.residuals=F, lwd="5" , residuals.cex=0.5, residuals.color=c("#FF7a11", "#FF9038","#FFa65F","#FFbc87","#FFddc1","#FFF2e9"), 
     col.line = "black",
     confint=list(col="grey", alpha=.3), 
     xlab="tonic theta density", ylab="General Positive Affect", 
     ylim = c(-3, 3),  yaxt = "i")

fit.snralpha_tonic <- lmer(PANAS_score_z ~ snralpha_tonic_z + scale(snralpha_tonic_baseline) + PANAS_score_z_baseline + condition:night + night + test_no + scale(tst) + channel + order + (1|participant), data=df_week)

effects.fitsnralpha_tonic <- effect("snralpha_tonic_z", fit.snralpha_tonic, partial.residuals=T) 
plot(effects.fitsnralpha_tonic,main = NULL, smooth.residuals=F, lwd="5" , residuals.cex=0.5, residuals.color=c("#FF7a11", "#FF9038","#FFa65F","#FFbc87","#FFddc1","#FFF2e9"),
      col.line = "black",
     confint=list(col="grey", alpha=.3), 
     xlab="tonic alpha amplitude", ylab="General Positive Affect",
     ylim = c(-3, 3),  yaxt = "i")
```
